---
title: "Male Data Cleaning"
editor: visual
---

1.  **Male, White-alone, Across all U.S. States + Puerto Rico (Status: Cleaned)**

```{r}
library(readxl)
library(tidyverse)

acs_data <- read.csv('dataset/ACS_data_rendered.csv')
```

```{r "White Alone"}
# Alabama
us_whitealone_data <- filter(acs_data, Label == "Bachelor's degree or higher*")
bdh_whitealone_alabama <- tibble(
  Years = us_whitealone_data$Years,
  Percentage_men = us_whitealone_data$`Alabama...9`,
  Race = "White Alone")

# Alaska
bdh_whitealone_alaska <- tibble(
  Years = us_whitealone_data$Years,
  Percentage_men = us_whitealone_data$`...21`,
  Race = "White Alone"
)


# Arizona
bdh_whitealone_arizona <- tibble(
  Years = us_whitealone_data$Years,
  Percentage_men = us_whitealone_data$`...33`,
  Race = "White Alone"
)

# Arkansas
bdh_whitealone_arkansas <- tibble(
  Years = us_whitealone_data$Years,
  Percentage_men = us_whitealone_data$`...45`,
  Race = "White Alone"
)

# California
bdh_whitealone_california <- tibble(
  Years = us_whitealone_data$Years,
  Percentage_men = us_whitealone_data$`...57`,
  Race = "White Alone"
)

# Colorado
bdh_whitealone_colorado <- tibble(
  Years = us_whitealone_data$Years,
  Percentage_men = us_whitealone_data$`...69`,
  Race = "White Alone"
)

# Connecticut
bdh_whitealone_connecticut <- tibble(
  Years = us_whitealone_data$Years,
  Percentage_men = us_whitealone_data$`...81`,
  Race = "White Alone"
)

# Delaware
bdh_whitealone_delaware <- tibble(
  Years = us_whitealone_data$Years,
  Percentage_men = us_whitealone_data$`...93`,
  Race = "White Alone"
)

# Florida
bdh_whitealone_florida <- tibble(
  Years = us_whitealone_data$Years,
  Percentage_men = us_whitealone_data$`...105`,
  Race = "White Alone"
)

# Georgia
bdh_whitealone_georgia <- tibble(
  Years = us_whitealone_data$Years,
  Percentage_men = us_whitealone_data$`...117`,
  Race = "White Alone"
)

# Hawaii
bdh_whitealone_hawaii <- tibble(
  Years = us_whitealone_data$Years,
  Percentage_men = us_whitealone_data$`...129`,
  Race = "White Alone"
)

# Idaho
bdh_whitealone_idaho <- tibble(
  Years = us_whitealone_data$Years,
  Percentage_men = us_whitealone_data$`...141`,
  Race = "White Alone"
)

# Illinois
bdh_whitealone_illinois <- tibble(
  Years = us_whitealone_data$Years,
  Percentage_men = us_whitealone_data$`...153`,
  Race = "White Alone"
)

# Indiana
bdh_whitealone_indiana <- tibble(
  Years = us_whitealone_data$Years,
  Percentage_men = us_whitealone_data$`...165`,
  Race = "White Alone"
)

# Iowa
bdh_whitealone_iowa <- tibble(
  Years = us_whitealone_data$Years,
  Percentage_men = us_whitealone_data$`...177`,
  Race = "White Alone"
)

# Kansas
bdh_whitealone_kansas <- tibble(
  Years = us_whitealone_data$Years,
  Percentage_men = us_whitealone_data$`...189`,
  Race = "White Alone"
)

# Kentucky
bdh_whitealone_kentucky <- tibble(
  Years = us_whitealone_data$Years,
  Percentage_men = us_whitealone_data$`...201`,
  Race = "White Alone"
)

# Louisiana
bdh_whitealone_louisiana <- tibble(
  Years = us_whitealone_data$Years,
  Percentage_men = us_whitealone_data$`...213`,
  Race = "White Alone"
)

# Maine
bdh_whitealone_maine <- tibble(
  Years = us_whitealone_data$Years,
  Percentage_men = us_whitealone_data$`...225`,
  Race = "White Alone"
)

# Maryland
bdh_whitealone_maryland <- tibble(
  Years = us_whitealone_data$Years,
  Percentage_men = us_whitealone_data$`...237`,
  Race = "White Alone"
)

# Massachusetts
bdh_whitealone_massachusetts <- tibble(
  Years = us_whitealone_data$Years,
  Percentage_men = us_whitealone_data$`...249`,
  Race = "White Alone"
)

# Michigan
bdh_whitealone_michigan <- tibble(
  Years = us_whitealone_data$Years,
  Percentage_men = us_whitealone_data$`...261`,
  Race = "White Alone"
)

# Minnesota
bdh_whitealone_minnesota <- tibble(
  Years = us_whitealone_data$Years,
  Percentage_men = us_whitealone_data$`...273`,
  Race = "White Alone"
)

# Mississippi
bdh_whitealone_mississippi <- tibble(
  Years = us_whitealone_data$Years,
  Percentage_men = us_whitealone_data$`...285`,
  Race = "White Alone"
)

# Missouri
bdh_whitealone_missouri <- tibble(
  Years = us_whitealone_data$Years,
  Percentage_men = us_whitealone_data$`...397`,
  Race = "White Alone"
)

# Montana
bdh_whitealone_montana <- tibble(
  Years = us_whitealone_data$Years,
  Percentage_men = us_whitealone_data$`...309`,
  Race = "White Alone"
)

# Nebraska
bdh_whitealone_nebraska <- tibble(
  Years = us_whitealone_data$Years,
  Percentage_men = us_whitealone_data$`...321`,
  Race = "White Alone"
)

# Nevada
bdh_whitealone_nevada <- tibble(
  Years = us_whitealone_data$Years,
  Percentage_men = us_whitealone_data$`...333`,
  Race = "White Alone"
)

# New Hampshire
bdh_whitealone_newhampshire <- tibble(
  Years = us_whitealone_data$Years,
  Percentage_men = us_whitealone_data$`...345`,
  Race = "White Alone"
)

# New Jersey
bdh_whitealone_newjersey <- tibble(
  Years = us_whitealone_data$Years,
  Percentage_men = us_whitealone_data$`...357`,
  Race = "White Alone"
)

# New Mexico
bdh_whitealone_newmexico <- tibble(
  Years = us_whitealone_data$Years,
  Percentage_men = us_whitealone_data$`...369`,
  Race = "White Alone"
)

# New York
bdh_whitealone_newyork <- tibble(
  Years = us_whitealone_data$Years,
  Percentage_men = us_whitealone_data$`...381`,
  Race = "White Alone"
)

# North Carolina
bdh_whitealone_northcarolina <- tibble(
  Years = us_whitealone_data$Years,
  Percentage_men = us_whitealone_data$`...393`,
  Race = "White Alone"
)

# North Dakota
bdh_whitealone_northdakota <- tibble(
  Years = us_whitealone_data$Years,
  Percentage_men = us_whitealone_data$`...405`,
  Race = "White Alone"
)

# Ohio
bdh_whitealone_ohio <- tibble(
  Years = us_whitealone_data$Years,
  Percentage_men = us_whitealone_data$`...417`,
  Race = "White Alone"
)

# Oklahoma
bdh_whitealone_oklahoma <- tibble(
  Years = us_whitealone_data$Years,
  Percentage_men = us_whitealone_data$`...429`,
  Race = "White Alone"
)

# Oregon
bdh_whitealone_oregon <- tibble(
  Years = us_whitealone_data$Years,
  Percentage_men = us_whitealone_data$`...441`,
  Race = "White Alone"
)

# Pennsylvania
bdh_whitealone_pennsylvania <- tibble(
  Years = us_whitealone_data$Years,
  Percentage_men = us_whitealone_data$`...453`,
  Race = "White Alone"
)

# Rhode Island
bdh_whitealone_rhodeisland <- tibble(
  Years = us_whitealone_data$Years,
  Percentage_men = us_whitealone_data$`...465`,
  Race = "White Alone"
)

# South Carolina
bdh_whitealone_southcarolina <- tibble(
  Years = us_whitealone_data$Years,
  Percentage_men = us_whitealone_data$`...477`,
  Race = "White Alone"
)

# South Dakota
bdh_whitealone_southdakota <- tibble(
  Years = us_whitealone_data$Years,
  Percentage_men = us_whitealone_data$`...489`,
  Race = "White Alone"
)

# Tennessee
bdh_whitealone_tennessee <- tibble(
  Years = us_whitealone_data$Years,
  Percentage_men = us_whitealone_data$`...501`,
  Race = "White Alone"
)

# Texas
bdh_whitealone_texas <- tibble(
  Years = us_whitealone_data$Years,
  Percentage_men = us_whitealone_data$`...513`,
  Race = "White Alone"
)

# Utah
bdh_whitealone_utah <- tibble(
  Years = us_whitealone_data$Years,
  Percentage_men = us_whitealone_data$`...525`,
  Race = "White Alone"
)

# Vermont
bdh_whitealone_vermont <- tibble(
  Years = us_whitealone_data$Years,
  Percentage_men = us_whitealone_data$`...537`,
  Race = "White Alone"
)

# Virginia
bdh_whitealone_virginia <- tibble(
  Years = us_whitealone_data$Years,
  Percentage_men = us_whitealone_data$`...549`,
  Race = "White Alone"
)

# Washington
bdh_whitealone_washington <- tibble(
  Years = us_whitealone_data$Years,
  Percentage_men = us_whitealone_data$`...561`,
  Race = "White Alone"
)

# West Virginia
bdh_whitealone_westvirginia <- tibble(
  Years = us_whitealone_data$Years,
  Percentage_men = us_whitealone_data$`...573`,
  Race = "White Alone"
)

# Wisconsin
bdh_whitealone_wisconsin <- tibble(
  Years = us_whitealone_data$Years,
  Percentage_men = us_whitealone_data$`...585`,
 Race = "White Alone"
)

# Wyoming
bdh_whitealone_wyoming <- tibble(
  Years = us_whitealone_data$Years,
  Percentage_men = us_whitealone_data$`...597`,
  Race = "White Alone"
)

# Puerto Rico
bdh_whitealone_puertorico <- tibble(
  Years = us_whitealone_data$Years,
  Percentage_men = us_whitealone_data$`...597`,
  Race = "White Alone"
)

# Combine all tibbles into one
combined_data_malewhitealone <- bind_rows(
  bdh_whitealone_alabama,
  bdh_whitealone_alaska,
  bdh_whitealone_arizona,
  bdh_whitealone_arkansas,
  bdh_whitealone_california,
  bdh_whitealone_colorado,
  bdh_whitealone_connecticut,
  bdh_whitealone_delaware,
  bdh_whitealone_florida,
  bdh_whitealone_georgia,
  bdh_whitealone_hawaii,
  bdh_whitealone_idaho,
  bdh_whitealone_illinois,
  bdh_whitealone_indiana,
  bdh_whitealone_iowa,
  bdh_whitealone_kansas,
  bdh_whitealone_kentucky,
  bdh_whitealone_louisiana,
  bdh_whitealone_maine,
  bdh_whitealone_maryland,
  bdh_whitealone_massachusetts,
  bdh_whitealone_michigan,
  bdh_whitealone_minnesota,
  bdh_whitealone_mississippi,
  bdh_whitealone_missouri,
  bdh_whitealone_montana,
  bdh_whitealone_nebraska,
  bdh_whitealone_nevada,
  bdh_whitealone_newhampshire,
  bdh_whitealone_newjersey,
  bdh_whitealone_newmexico,
  bdh_whitealone_newyork,
  bdh_whitealone_northcarolina,
  bdh_whitealone_northdakota,
  bdh_whitealone_ohio,
  bdh_whitealone_oklahoma,
  bdh_whitealone_oregon,
  bdh_whitealone_pennsylvania,
  bdh_whitealone_rhodeisland,
  bdh_whitealone_southcarolina,
  bdh_whitealone_southdakota,
  bdh_whitealone_tennessee,
  bdh_whitealone_texas,
  bdh_whitealone_utah,
  bdh_whitealone_vermont,
  bdh_whitealone_virginia,
  bdh_whitealone_washington,
  bdh_whitealone_westvirginia,
  bdh_whitealone_wisconsin,
  bdh_whitealone_wyoming,
  bdh_whitealone_puertorico
)

print(combined_data_malewhitealone)
```

2.  **Male, White-alone, not Hispanic or Latino, Across all U.S. States + Puerto Rico (Status: Cleaned)**

```{r "White alone, not Hispanic or Latino"}

# Alabama
us_whitealone_data <- filter(acs_data, Label == "Bachelor's degree or higher**")
us_WhitealonenotHispanicorLatino_data <- filter(acs_data, Label == "Bachelor's degree or higher**")
bdh_wnhp_alabama <- tibble(
  Years =  us_WhitealonenotHispanicorLatino_data$Years,
  Percentage_wnhp_men = us_WhitealonenotHispanicorLatino_data$`...9`,
  Race = "White alone, not Hispanic or Latino"
)

# Alaska
bdh_wnhp_alaska <- tibble(
  Years = us_WhitealonenotHispanicorLatino_data$Years,
  Percentage_wnhp_men = us_WhitealonenotHispanicorLatino_data$`...21`,
  Race = "White alone, not Hispanic or Latino"
)

# Arizona
bdh_wnhp_arizona <- tibble(
  Years = us_WhitealonenotHispanicorLatino_data$Years,
  Percentage_wnhp_men = us_WhitealonenotHispanicorLatino_data$`...33`,
  Race = "White alone, not Hispanic or Latino"
)

# Arkansas
bdh_wnhp_arkansas <- tibble(
  Years = us_WhitealonenotHispanicorLatino_data$Years,
  Percentage_wnhp_men = us_WhitealonenotHispanicorLatino_data$`...45`,
  Race = "White alone, not Hispanic or Latino"
)

# California
bdh_wnhp_california <- tibble(
  Years = us_WhitealonenotHispanicorLatino_data$Years,
  Percentage_wnhp_men = us_WhitealonenotHispanicorLatino_data$`...53`,
  Race = "White alone, not Hispanic or Latino"
)

# Colorado
bdh_wnhp_colorado <- tibble(
  Years = us_WhitealonenotHispanicorLatino_data$Years,
  Percentage_wnhp_men = us_WhitealonenotHispanicorLatino_data$`...65`,
  Race = "White alone, not Hispanic or Latino"
)

# Connecticut
bdh_wnhp_connecticut <- tibble(
  Years = us_WhitealonenotHispanicorLatino_data$Years,
  Percentage_wnhp_men = us_WhitealonenotHispanicorLatino_data$`...77`,
  Race = "White alone, not Hispanic or Latino"
)

# Delaware
bdh_wnhp_delaware <- tibble(
  Years = us_WhitealonenotHispanicorLatino_data$Years,
  Percentage_wnhp_men = us_WhitealonenotHispanicorLatino_data$`...89`,
  Race = "White alone, not Hispanic or Latino"
)

# Florida
bdh_wnhp_florida <- tibble(
  Years = us_WhitealonenotHispanicorLatino_data$Years,
  Percentage_wnhp_men = us_WhitealonenotHispanicorLatino_data$`...101`,
  Race = "White alone, not Hispanic or Latino"
)

# Georgia
bdh_wnhp_georgia <- tibble(
  Years = us_WhitealonenotHispanicorLatino_data$Years,
  Percentage_wnhp_men = us_WhitealonenotHispanicorLatino_data$`...113`,
  Race = "White alone, not Hispanic or Latino"
)

# Hawaii
bdh_wnhp_hawaii <- tibble(
  Years = us_WhitealonenotHispanicorLatino_data$Years,
  Percentage_wnhp_men = us_WhitealonenotHispanicorLatino_data$`...125`,
  Race = "White alone, not Hispanic or Latino"
)

# Idaho
bdh_wnhp_idaho <- tibble(
  Years = us_WhitealonenotHispanicorLatino_data$Years,
  Percentage_wnhp_men = us_WhitealonenotHispanicorLatino_data$`...137`,
  Race = "White alone, not Hispanic or Latino"
)

# Illinois
bdh_wnhp_illinois <- tibble(
  Years = us_WhitealonenotHispanicorLatino_data$Years,
  Percentage_wnhp_men = us_WhitealonenotHispanicorLatino_data$`...149`,
  Race = "White alone, not Hispanic or Latino"
)

# Indiana
bdh_wnhp_indiana <- tibble(
  Years = us_WhitealonenotHispanicorLatino_data$Years,
  Percentage_wnhp_men = us_WhitealonenotHispanicorLatino_data$`...161`,
  Race = "White alone, not Hispanic or Latino"
)

# Iowa
bdh_wnhp_iowa <- tibble(
  Years = us_WhitealonenotHispanicorLatino_data$Years,
  Percentage_wnhp_men = us_WhitealonenotHispanicorLatino_data$`...173`,
  Race = "White alone, not Hispanic or Latino"
)

# Kansas
bdh_wnhp_kansas <- tibble(
  Years = us_WhitealonenotHispanicorLatino_data$Years,
  Percentage_wnhp_men = us_WhitealonenotHispanicorLatino_data$`...185`,
  Race = "White alone, not Hispanic or Latino"
)

# Kentucky
bdh_wnhp_kentucky <- tibble(
  Years = us_WhitealonenotHispanicorLatino_data$Years,
  Percentage_wnhp_men = us_WhitealonenotHispanicorLatino_data$`...197`,
  Race = "White alone, not Hispanic or Latino"
)

# Louisiana
bdh_wnhp_louisiana <- tibble(
  Years = us_WhitealonenotHispanicorLatino_data$Years,
  Percentage_wnhp_men = us_WhitealonenotHispanicorLatino_data$`...209`,
  Race = "White alone, not Hispanic or Latino"
)

# Maine
bdh_wnhp_maine <- tibble(
  Years = us_WhitealonenotHispanicorLatino_data$Years,
  Percentage_wnhp_men = us_WhitealonenotHispanicorLatino_data$`...221`,
  Race = "White alone, not Hispanic or Latino"
)

# Maryland
bdh_wnhp_maryland <- tibble(
  Years = us_WhitealonenotHispanicorLatino_data$Years,
  Percentage_wnhp_men = us_WhitealonenotHispanicorLatino_data$`...233`,
  Race = "White alone, not Hispanic or Latino"
)

# Massachusetts
bdh_wnhp_massachusetts <- tibble(
  Years = us_WhitealonenotHispanicorLatino_data$Years,
  Percentage_wnhp_men = us_WhitealonenotHispanicorLatino_data$`...245`,
  Race = "White alone, not Hispanic or Latino"
)

# Michigan
bdh_wnhp_michigan <- tibble(
  Years = us_WhitealonenotHispanicorLatino_data$Years,
  Percentage_wnhp_men = us_WhitealonenotHispanicorLatino_data$`...257`,
  Race = "White alone, not Hispanic or Latino"
)

# Minnesota
bdh_wnhp_minnesota <- tibble(
  Years = us_WhitealonenotHispanicorLatino_data$Years,
  Percentage_wnhp_men = us_WhitealonenotHispanicorLatino_data$`...269`,
  Race = "White alone, not Hispanic or Latino"
)

# Mississippi
bdh_wnhp_mississippi <- tibble(
  Years = us_WhitealonenotHispanicorLatino_data$Years,
  Percentage_wnhp_men = us_WhitealonenotHispanicorLatino_data$`...281`,
  Race = "White alone, not Hispanic or Latino"
)

# Missouri
bdh_wnhp_missouri <- tibble(
  Years = us_WhitealonenotHispanicorLatino_data$Years,
  Percentage_wnhp_men = us_WhitealonenotHispanicorLatino_data$`...293`,
  Race = "White alone, not Hispanic or Latino"
)

# Montana
bdh_wnhp_montana <- tibble(
  Years = us_WhitealonenotHispanicorLatino_data$Years,
  Percentage_wnhp_men = us_WhitealonenotHispanicorLatino_data$`...305`,
  Race = "White alone, not Hispanic or Latino"
)

# Nebraska
bdh_wnhp_nebraska <- tibble(
  Years = us_WhitealonenotHispanicorLatino_data$Years,
  Percentage_wnhp_men = us_WhitealonenotHispanicorLatino_data$`...317`,
  Race = "White alone, not Hispanic or Latino"
)

# Nevada
bdh_wnhp_nevada <- tibble(
  Years = us_WhitealonenotHispanicorLatino_data$Years,
  Percentage_wnhp_men = us_WhitealonenotHispanicorLatino_data$`...329`,
  Race = "White alone, not Hispanic or Latino"
)

# New Hampshire
bdh_wnhp_newhampshire <- tibble(
  Years = us_WhitealonenotHispanicorLatino_data$Years,
  Percentage_wnhp_men = us_WhitealonenotHispanicorLatino_data$`...341`,
  Race = "White alone, not Hispanic or Latino"
)

# New Jersey
bdh_wnhp_newjersey <- tibble(
  Years = us_WhitealonenotHispanicorLatino_data$Years,
  Percentage_wnhp_men = us_WhitealonenotHispanicorLatino_data$`...353`,
  Race = "White alone, not Hispanic or Latino"
)

# New Mexico
bdh_wnhp_newmexico <- tibble(
  Years = us_WhitealonenotHispanicorLatino_data$Years,
  Percentage_wnhp_men = us_WhitealonenotHispanicorLatino_data$`...365`,
  Race = "White alone, not Hispanic or Latino"
)

# New York
bdh_wnhp_newyork <- tibble(
  Years = us_WhitealonenotHispanicorLatino_data$Years,
  Percentage_wnhp_men = us_WhitealonenotHispanicorLatino_data$`...377`,
  Race = "White alone, not Hispanic or Latino"
)

# North Carolina
bdh_wnhp_northcarolina <- tibble(
  Years = us_WhitealonenotHispanicorLatino_data$Years,
  Percentage_wnhp_men = us_WhitealonenotHispanicorLatino_data$`...389`,
  Race = "White alone, not Hispanic or Latino"
)

# North Dakota
bdh_wnhp_northdakota <- tibble(
  Years = us_WhitealonenotHispanicorLatino_data$Years,
  Percentage_wnhp_men = us_WhitealonenotHispanicorLatino_data$`...401`,
  Race = "White alone, not Hispanic or Latino"
)

# Ohio
bdh_wnhp_ohio <- tibble(
  Years = us_WhitealonenotHispanicorLatino_data$Years,
  Percentage_wnhp_men = us_WhitealonenotHispanicorLatino_data$`...413`,
  Race = "White alone, not Hispanic or Latino"
)

# Oklahoma
bdh_wnhp_oklahoma <- tibble(
  Years = us_WhitealonenotHispanicorLatino_data$Years,
  Percentage_wnhp_men = us_WhitealonenotHispanicorLatino_data$`...425`,
  Race = "White alone, not Hispanic or Latino"
)

# Oregon
bdh_wnhp_oregon <- tibble(
  Years = us_WhitealonenotHispanicorLatino_data$Years,
  Percentage_wnhp_men = us_WhitealonenotHispanicorLatino_data$`...437`,
  Race = "White alone, not Hispanic or Latino"
)

# Pennsylvania
bdh_wnhp_pennsylvania <- tibble(
  Years = us_WhitealonenotHispanicorLatino_data$Years,
  Percentage_wnhp_men = us_WhitealonenotHispanicorLatino_data$`...449`,
  Race = "White alone, not Hispanic or Latino"
)

# Rhode Island
bdh_wnhp_rhodeisland <- tibble(
  Years = us_WhitealonenotHispanicorLatino_data$Years,
  Percentage_wnhp_men = us_WhitealonenotHispanicorLatino_data$`...461`,
  Race = "White alone, not Hispanic or Latino"
)

# South Carolina
bdh_wnhp_southcarolina <- tibble(
  Years = us_WhitealonenotHispanicorLatino_data$Years,
  Percentage_wnhp_men = us_WhitealonenotHispanicorLatino_data$`...473`,
  Race = "White alone, not Hispanic or Latino"
)

# South Dakota
bdh_wnhp_southdakota <- tibble(
  Years = us_WhitealonenotHispanicorLatino_data$Years,
  Percentage_wnhp_men = us_WhitealonenotHispanicorLatino_data$`...485`,
  Race = "White alone, not Hispanic or Latino"
)

# Tennessee
bdh_wnhp_tennessee <- tibble(
  Years = us_WhitealonenotHispanicorLatino_data$Years,
  Percentage_wnhp_men = us_WhitealonenotHispanicorLatino_data$`...497`,
  Race = "White alone, not Hispanic or Latino"
)

# Texas
bdh_wnhp_texas <- tibble(
  Years = us_WhitealonenotHispanicorLatino_data$Years,
  Percentage_wnhp_men = us_WhitealonenotHispanicorLatino_data$`...509`,
  Race = "White alone, not Hispanic or Latino"
)

# Utah
bdh_wnhp_utah <- tibble(
  Years = us_WhitealonenotHispanicorLatino_data$Years,
  Percentage_wnhp_men = us_WhitealonenotHispanicorLatino_data$`...521`,
  Race = "White alone, not Hispanic or Latino"
)

# Vermont
bdh_wnhp_vermont <- tibble(
  Years = us_WhitealonenotHispanicorLatino_data$Years,
  Percentage_wnhp_men = us_WhitealonenotHispanicorLatino_data$`...533`,
  Race = "White alone, not Hispanic or Latino"
)

# Virginia
bdh_wnhp_virginia <- tibble(
  Years = us_WhitealonenotHispanicorLatino_data$Years,
  Percentage_wnhp_men = us_WhitealonenotHispanicorLatino_data$`...545`,
  Race = "White alone, not Hispanic or Latino"
)

# Washington
bdh_wnhp_washington <- tibble(
  Years = us_WhitealonenotHispanicorLatino_data$Years,
  Percentage_wnhp_men = us_WhitealonenotHispanicorLatino_data$`...557`,
  Race = "White alone, not Hispanic or Latino"
)

# West Virginia
bdh_wnhp_westvirginia <- tibble(
  Years =us_WhitealonenotHispanicorLatino_data$Years,
  Percentage_wnhp_men = us_WhitealonenotHispanicorLatino_data$`...569`,
  Race = "White alone, not Hispanic or Latino"
)

# Wisconsin
bdh_wnhp_wisconsin <- tibble(
  Years = us_WhitealonenotHispanicorLatino_data$Years,
  Percentage_wnhp_men = us_WhitealonenotHispanicorLatino_data$`...581`,
  Race = "White alone, not Hispanic or Latino"
)

# Wyoming
bdh_wnhp_wyoming <- tibble(
  Years = us_WhitealonenotHispanicorLatino_data$Years,
  Percentage_wnhp_men = us_WhitealonenotHispanicorLatino_data$`...593`,
  Race = "White alone, not Hispanic or Latino"
)

# Puerto Rico
bdh_wnhp_puertorico <- tibble(
  Years = us_WhitealonenotHispanicorLatino_data$Years,
  Percentage_wnhp_men = us_WhitealonenotHispanicorLatino_data$`...605`,
  Race = "White alone, not Hispanic or Latino"
)

# Combine all states
combined_data_wnhp <- bind_rows(
  bdh_wnhp_alabama,
  bdh_wnhp_alaska,
  bdh_wnhp_arizona,
  bdh_wnhp_arkansas,
  bdh_wnhp_california,
  bdh_wnhp_colorado,
  bdh_wnhp_connecticut,
  bdh_wnhp_delaware,
  bdh_wnhp_florida,
  bdh_wnhp_georgia,
  bdh_wnhp_hawaii,
  bdh_wnhp_idaho,
  bdh_wnhp_illinois,
  bdh_wnhp_indiana,
  bdh_wnhp_iowa,
  bdh_wnhp_kansas,
  bdh_wnhp_kentucky,
  bdh_wnhp_louisiana,
  bdh_wnhp_maine,
  bdh_wnhp_maryland,
  bdh_wnhp_massachusetts,
  bdh_wnhp_michigan,
  bdh_wnhp_minnesota,
  bdh_wnhp_mississippi,
  bdh_wnhp_missouri,
  bdh_wnhp_montana,
  bdh_wnhp_nebraska,
  bdh_wnhp_nevada,
  bdh_wnhp_newhampshire,
  bdh_wnhp_newjersey,
  bdh_wnhp_newmexico,
  bdh_wnhp_newyork,
  bdh_wnhp_northcarolina,
  bdh_wnhp_northdakota,
  bdh_wnhp_ohio,
  bdh_wnhp_oklahoma,
  bdh_wnhp_oregon,
  bdh_wnhp_pennsylvania,
  bdh_wnhp_rhodeisland,
  bdh_wnhp_southcarolina,
  bdh_wnhp_southdakota,
  bdh_wnhp_tennessee,
  bdh_wnhp_texas,
  bdh_wnhp_utah,
  bdh_wnhp_vermont,
  bdh_wnhp_virginia,
  bdh_wnhp_washington,
  bdh_wnhp_westvirginia,
  bdh_wnhp_wisconsin,
  bdh_wnhp_wyoming,
  bdh_wnhp_puertorico
)

print(combined_data_wnhp)

```

3.  **Male, Black Alone, Across all U.S. States + Puerto Rico (Status: Cleaned)**

```{r "Black Alone"}

# Alabama
us_blackalone_data <- filter(acs_data, Label == "Bachelor's degree or higher***")
bdh_wnhp_alabama <- tibble(
  Years =  us_blackalone_data$Years,
  Percentage_wnhp_men = us_blackalone_data$`...9`,
  Race = "Black Alone"
)

# Alaska
bdh_wnhp_alaska <- tibble(
  Years = us_blackalone_data$Years,
  Percentage_wnhp_men = us_blackalone_data$`...21`,
  Race = "Black Alone"
)

# Arizona
bdh_wnhp_arizona <- tibble(
  Years = us_blackalone_data$Years,
  Percentage_wnhp_men = us_blackalone_data$`...33`,
  Race = "Black Alone"
)

# Arkansas
bdh_wnhp_arkansas <- tibble(
  Years = us_blackalone_data$Years,
  Percentage_wnhp_men = us_blackalone_data$`...45`,
  Race = "Black Alone"
)

# California
bdh_wnhp_california <- tibble(
  Years = us_blackalone_data$Years,
  Percentage_wnhp_men = us_blackalone_data$`...53`,
  Race = "Black Alone"
)

# Colorado
bdh_wnhp_colorado <- tibble(
  Years = us_blackalone_data$Years,
  Percentage_wnhp_men = us_blackalone_data$`...65`,
  Race = "Black Alone"
)

# Connecticut
bdh_wnhp_connecticut <- tibble(
  Years = us_blackalone_data$Years,
  Percentage_wnhp_men = us_blackalone_data$`...77`,
  Race = "Black Alone"
)

# Delaware
bdh_wnhp_delaware <- tibble(
  Years = us_blackalone_data$Years,
  Percentage_wnhp_men = us_blackalone_data$`...89`,
  Race = "Black Alone"
)

# Florida
bdh_wnhp_florida <- tibble(
  Years = us_blackalone_data$Years,
  Percentage_wnhp_men = us_blackalone_data$`...101`,
  Race = "Black Alone"
)

# Georgia
bdh_wnhp_georgia <- tibble(
  Years = us_blackalone_data$Years,
  Percentage_wnhp_men = us_blackalone_data$`...113`,
  Race = "Black Alone"
)

# Hawaii
bdh_wnhp_hawaii <- tibble(
  Years = us_blackalone_data$Years,
  Percentage_wnhp_men = us_blackalone_data$`...125`,
  Race = "Black Alone"
)

# Idaho
bdh_wnhp_idaho <- tibble(
  Years = us_blackalone_data$Years,
  Percentage_wnhp_men = us_blackalone_data$`...137`,
  Race = "Black Alone"
)

# Illinois
bdh_wnhp_illinois <- tibble(
  Years = us_blackalone_data$Years,
  Percentage_wnhp_men = us_blackalone_data$`...149`,
  Race = "Black Alone"
)

# Indiana
bdh_wnhp_indiana <- tibble(
  Years = us_blackalone_data$Years,
  Percentage_wnhp_men = us_blackalone_data$`...161`,
  Race = "Black Alone"
)

# Iowa
bdh_wnhp_iowa <- tibble(
  Years = us_blackalone_data$Years,
  Percentage_wnhp_men = us_blackalone_data$`...173`,
  Race = "Black Alone"
)

# Kansas
bdh_wnhp_kansas <- tibble(
  Years = us_blackalone_data$Years,
  Percentage_wnhp_men = us_blackalone_data$`...185`,
  Race = "Black Alone"
)

# Kentucky
bdh_wnhp_kentucky <- tibble(
  Years = us_blackalone_data$Years,
  Percentage_wnhp_men = us_blackalone_data$`...197`,
  Race = "Black Alone"
)

# Louisiana
bdh_wnhp_louisiana <- tibble(
  Years = us_blackalone_data$Years,
  Percentage_wnhp_men = us_blackalone_data$`...209`,
  Race = "Black Alone"
)

# Maine
bdh_wnhp_maine <- tibble(
  Years = us_blackalone_data$Years,
  Percentage_wnhp_men = us_blackalone_data$`...221`,
  Race = "Black Alone"
)

# Maryland
bdh_wnhp_maryland <- tibble(
  Years = us_blackalone_data$Years,
  Percentage_wnhp_men = us_blackalone_data$`...233`,
  Race = "Black Alone"
)

# Massachusetts
bdh_wnhp_massachusetts <- tibble(
  Years = us_blackalone_data$Years,
  Percentage_wnhp_men = us_blackalone_data$`...245`,
  Race = "Black Alone"
)

# Michigan
bdh_wnhp_michigan <- tibble(
  Years = us_blackalone_data$Years,
  Percentage_wnhp_men = us_blackalone_data$`...257`,
  Race = "Black Alone"
)

# Minnesota
bdh_wnhp_minnesota <- tibble(
  Years = us_blackalone_data$Years,
  Percentage_wnhp_men = us_blackalone_data$`...269`,
  Race = "Black Alone"
)

# Mississippi
bdh_wnhp_mississippi <- tibble(
  Years = us_blackalone_data$Years,
  Percentage_wnhp_men = us_blackalone_data$`...281`,
  Race = "Black Alone"
)

# Missouri
bdh_wnhp_missouri <- tibble(
  Years = us_blackalone_data$Years,
  Percentage_wnhp_men = us_blackalone_data$`...293`,
  Race = "Black Alone"
)

# Montana
bdh_wnhp_montana <- tibble(
  Years = us_blackalone_data$Years,
  Percentage_wnhp_men = us_blackalone_data$`...305`,
  Race = "Black Alone"
)

# Nebraska
bdh_wnhp_nebraska <- tibble(
  Years = us_blackalone_data$Years,
  Percentage_wnhp_men = us_blackalone_data$`...317`,
  Race = "Black Alone"
)

# Nevada
bdh_wnhp_nevada <- tibble(
  Years = us_blackalone_data$Years,
  Percentage_wnhp_men = us_blackalone_data$`...329`,
  Race = "Black Alone"
)

# New Hampshire
bdh_wnhp_newhampshire <- tibble(
  Years = us_blackalone_data$Years,
  Percentage_wnhp_men = us_blackalone_data$`...341`,
  Race = "Black Alone"
)

# New Jersey
bdh_wnhp_newjersey <- tibble(
  Years = us_blackalone_data$Years,
  Percentage_wnhp_men = us_blackalone_data$`...353`,
  Race = "Black Alone"
)

# New Mexico
bdh_wnhp_newmexico <- tibble(
  Years = us_blackalone_data$Years,
  Percentage_wnhp_men = us_blackalone_data$`...365`,
  Race = "Black Alone"
)

# New York
bdh_wnhp_newyork <- tibble(
  Years = us_blackalone_data$Years,
  Percentage_wnhp_men = us_blackalone_data$`...377`,
  Race = "Black Alone"
)

# North Carolina
bdh_wnhp_northcarolina <- tibble(
  Years = us_blackalone_data$Years,
  Percentage_wnhp_men = us_blackalone_data$`...389`,
  Race = "Black Alone"
)

# North Dakota
bdh_wnhp_northdakota <- tibble(
  Years = us_blackalone_data$Years,
  Percentage_wnhp_men = us_blackalone_data$`...401`,
  Race = "Black Alone"
)

# Ohio
bdh_wnhp_ohio <- tibble(
  Years = us_blackalone_data$Years,
  Percentage_wnhp_men = us_blackalone_data$`...413`,
  Race = "Black Alone"
)

# Oklahoma
bdh_wnhp_oklahoma <- tibble(
  Years = us_blackalone_data$Years,
  Percentage_wnhp_men = us_blackalone_data$`...425`,
  Race = "Black Alone"
)

# Oregon
bdh_wnhp_oregon <- tibble(
  Years = us_blackalone_data$Years,
  Percentage_wnhp_men = us_blackalone_data$`...437`,
  Race = "Black Alone"
)

# Pennsylvania
bdh_wnhp_pennsylvania <- tibble(
  Years = us_blackalone_data$Years,
  Percentage_wnhp_men = us_blackalone_data$`...449`,
  Race = "Black Alone"
)

# Rhode Island
bdh_wnhp_rhodeisland <- tibble(
  Years = us_blackalone_data$Years,
  Percentage_wnhp_men = us_blackalone_data$`...461`,
  Race = "Black Alone"
)

# South Carolina
bdh_wnhp_southcarolina <- tibble(
  Years = us_blackalone_data$Years,
  Percentage_wnhp_men = us_blackalone_data$`...473`,
  Race = "Black Alone"
)

# South Dakota
bdh_wnhp_southdakota <- tibble(
  Years = us_blackalone_data$Years,
  Percentage_wnhp_men = us_blackalone_data$`...485`,
  Race = "Black Alone"
)

# Tennessee
bdh_wnhp_tennessee <- tibble(
  Years = us_blackalone_data$Years,
  Percentage_wnhp_men = us_blackalone_data$`...497`,
  Race = "Black Alone"
)

# Texas
bdh_wnhp_texas <- tibble(
  Years = us_blackalone_data$Years,
  Percentage_wnhp_men = us_blackalone_data$`...509`,
  Race = "Black Alone"
)

# Utah
bdh_wnhp_utah <- tibble(
  Years = us_blackalone_data$Years,
  Percentage_wnhp_men = us_blackalone_data$`...521`,
  Race = "Black Alone"
)

# Vermont
bdh_wnhp_vermont <- tibble(
  Years = us_blackalone_data$Years,
  Percentage_wnhp_men = us_blackalone_data$`...533`,
  Race = "Black Alone"
)

# Virginia
bdh_wnhp_virginia <- tibble(
  Years = us_blackalone_data$Years,
  Percentage_wnhp_men = us_blackalone_data$`...545`,
  Race = "Black Alone"
)

# Washington
bdh_wnhp_washington <- tibble(
  Years = us_blackalone_data$Years,
  Percentage_wnhp_men = us_blackalone_data$`...557`,
  Race = "Black Alone"
)

# West Virginia
bdh_wnhp_westvirginia <- tibble(
  Years =us_blackalone_data$Years,
  Percentage_wnhp_men = us_blackalone_data$`...569`,
  Race = "Black Alone"
)

# Wisconsin
bdh_wnhp_wisconsin <- tibble(
  Years = us_blackalone_data$Years,
  Percentage_wnhp_men = us_blackalone_data$`...581`,
  Race = "Black Alone"
)

# Wyoming
bdh_wnhp_wyoming <- tibble(
  Years = us_blackalone_data$Years,
  Percentage_wnhp_men = us_blackalone_data$`...593`,
  Race = "Black Alone"
)

# Puerto Rico
bdh_wnhp_puertorico <- tibble(
  Years = us_blackalone_data$Years,
  Percentage_wnhp_men = us_blackalone_data$`...605`,
  Race = "Black Alone"
)

# Combine all states
combined_data_wnhp <- bind_rows(
  bdh_wnhp_alabama,
  bdh_wnhp_alaska,
  bdh_wnhp_arizona,
  bdh_wnhp_arkansas,
  bdh_wnhp_california,
  bdh_wnhp_colorado,
  bdh_wnhp_connecticut,
  bdh_wnhp_delaware,
  bdh_wnhp_florida,
  bdh_wnhp_georgia,
  bdh_wnhp_hawaii,
  bdh_wnhp_idaho,
  bdh_wnhp_illinois,
  bdh_wnhp_indiana,
  bdh_wnhp_iowa,
  bdh_wnhp_kansas,
  bdh_wnhp_kentucky,
  bdh_wnhp_louisiana,
  bdh_wnhp_maine,
  bdh_wnhp_maryland,
  bdh_wnhp_massachusetts,
  bdh_wnhp_michigan,
  bdh_wnhp_minnesota,
  bdh_wnhp_mississippi,
  bdh_wnhp_missouri,
  bdh_wnhp_montana,
  bdh_wnhp_nebraska,
  bdh_wnhp_nevada,
  bdh_wnhp_newhampshire,
  bdh_wnhp_newjersey,
  bdh_wnhp_newmexico,
  bdh_wnhp_newyork,
  bdh_wnhp_northcarolina,
  bdh_wnhp_northdakota,
  bdh_wnhp_ohio,
  bdh_wnhp_oklahoma,
  bdh_wnhp_oregon,
  bdh_wnhp_pennsylvania,
  bdh_wnhp_rhodeisland,
  bdh_wnhp_southcarolina,
  bdh_wnhp_southdakota,
  bdh_wnhp_tennessee,
  bdh_wnhp_texas,
  bdh_wnhp_utah,
  bdh_wnhp_vermont,
  bdh_wnhp_virginia,
  bdh_wnhp_washington,
  bdh_wnhp_westvirginia,
  bdh_wnhp_wisconsin,
  bdh_wnhp_wyoming,
  bdh_wnhp_puertorico
)

print(combined_data_wnhp)

```

4.  **Male, American Indian or Alaska Native Alone, Across all U.S. States + Puerto Rico (Status: Cleaned)**

```{r "American Indian or Alaska Native Alone"}

# Alabama
us_AmericanIndianorAlaskaNativeAlone_data <- filter(acs_data, Label == "Bachelor's degree or higher****")
bdh_wnhp_alabama <- tibble(
  Years =  us_AmericanIndianorAlaskaNativeAlone_data$Years,
  Percentage_wnhp_men = us_AmericanIndianorAlaskaNativeAlone_data$`...9`,
  Race = "American Indian or Alaska Native Alone"
)

# Alaska
bdh_wnhp_alaska <- tibble(
  Years = us_AmericanIndianorAlaskaNativeAlone_data$Years,
  Percentage_wnhp_men = us_AmericanIndianorAlaskaNativeAlone_data$`...21`,
  Race = "American Indian or Alaska Native Alone"
)

# Arizona
bdh_wnhp_arizona <- tibble(
  Years = us_AmericanIndianorAlaskaNativeAlone_data$Years,
  Percentage_wnhp_men = us_AmericanIndianorAlaskaNativeAlone_data$`...33`,
  Race = "American Indian or Alaska Native Alone"
)

# Arkansas
bdh_wnhp_arkansas <- tibble(
  Years = us_AmericanIndianorAlaskaNativeAlone_data$Years,
  Percentage_wnhp_men = us_AmericanIndianorAlaskaNativeAlone_data$`...45`,
  Race = "American Indian or Alaska Native Alone"
)

# California
bdh_wnhp_california <- tibble(
  Years = us_AmericanIndianorAlaskaNativeAlone_data$Years,
  Percentage_wnhp_men = us_AmericanIndianorAlaskaNativeAlone_data$`...53`,
  Race = "American Indian or Alaska Native Alone"
)

# Colorado
bdh_wnhp_colorado <- tibble(
  Years = us_AmericanIndianorAlaskaNativeAlone_data$Years,
  Percentage_wnhp_men = us_AmericanIndianorAlaskaNativeAlone_data$`...65`,
  Race = "American Indian or Alaska Native Alone"
)

# Connecticut
bdh_wnhp_connecticut <- tibble(
  Years = us_AmericanIndianorAlaskaNativeAlone_data$Years,
  Percentage_wnhp_men = us_AmericanIndianorAlaskaNativeAlone_data$`...77`,
  Race = "American Indian or Alaska Native Alone"
)

# Delaware
bdh_wnhp_delaware <- tibble(
  Years = us_AmericanIndianorAlaskaNativeAlone_data$Years,
  Percentage_wnhp_men = us_AmericanIndianorAlaskaNativeAlone_data$`...89`,
  Race = "American Indian or Alaska Native Alone"
)

# Florida
bdh_wnhp_florida <- tibble(
  Years = us_AmericanIndianorAlaskaNativeAlone_data$Years,
  Percentage_wnhp_men = us_AmericanIndianorAlaskaNativeAlone_data$`...101`,
  Race = "American Indian or Alaska Native Alone"
)

# Georgia
bdh_wnhp_georgia <- tibble(
  Years = us_AmericanIndianorAlaskaNativeAlone_data$Years,
  Percentage_wnhp_men = us_AmericanIndianorAlaskaNativeAlone_data$`...113`,
  Race = "American Indian or Alaska Native Alone"
)

# Hawaii
bdh_wnhp_hawaii <- tibble(
  Years = us_AmericanIndianorAlaskaNativeAlone_data$Years,
  Percentage_wnhp_men = us_AmericanIndianorAlaskaNativeAlone_data$`...125`,
  Race = "American Indian or Alaska Native Alone"
)

# Idaho
bdh_wnhp_idaho <- tibble(
  Years = us_AmericanIndianorAlaskaNativeAlone_data$Years,
  Percentage_wnhp_men = us_AmericanIndianorAlaskaNativeAlone_data$`...137`,
  Race = "American Indian or Alaska Native Alone"
)

# Illinois
bdh_wnhp_illinois <- tibble(
  Years = us_AmericanIndianorAlaskaNativeAlone_data$Years,
  Percentage_wnhp_men = us_AmericanIndianorAlaskaNativeAlone_data$`...149`,
  Race = "American Indian or Alaska Native Alone"
)

# Indiana
bdh_wnhp_indiana <- tibble(
  Years = us_AmericanIndianorAlaskaNativeAlone_data$Years,
  Percentage_wnhp_men = us_AmericanIndianorAlaskaNativeAlone_data$`...161`,
  Race = "American Indian or Alaska Native Alone"
)

# Iowa
bdh_wnhp_iowa <- tibble(
  Years = us_AmericanIndianorAlaskaNativeAlone_data$Years,
  Percentage_wnhp_men = us_AmericanIndianorAlaskaNativeAlone_data$`...173`,
  Race = "American Indian or Alaska Native Alone"
)

# Kansas
bdh_wnhp_kansas <- tibble(
  Years = us_AmericanIndianorAlaskaNativeAlone_data$Years,
  Percentage_wnhp_men = us_AmericanIndianorAlaskaNativeAlone_data$`...185`,
  Race = "American Indian or Alaska Native Alone"
)

# Kentucky
bdh_wnhp_kentucky <- tibble(
  Years = us_AmericanIndianorAlaskaNativeAlone_data$Years,
  Percentage_wnhp_men = us_AmericanIndianorAlaskaNativeAlone_data$`...197`,
  Race = "American Indian or Alaska Native Alone"
)

# Louisiana
bdh_wnhp_louisiana <- tibble(
  Years = us_AmericanIndianorAlaskaNativeAlone_data$Years,
  Percentage_wnhp_men = us_AmericanIndianorAlaskaNativeAlone_data$`...209`,
  Race = "American Indian or Alaska Native Alone"
)

# Maine
bdh_wnhp_maine <- tibble(
  Years = us_AmericanIndianorAlaskaNativeAlone_data$Years,
  Percentage_wnhp_men = us_AmericanIndianorAlaskaNativeAlone_data$`...221`,
  Race = "American Indian or Alaska Native Alone"
)

# Maryland
bdh_wnhp_maryland <- tibble(
  Years = us_AmericanIndianorAlaskaNativeAlone_data$Years,
  Percentage_wnhp_men = us_AmericanIndianorAlaskaNativeAlone_data$`...233`,
  Race = "American Indian or Alaska Native Alone"
)

# Massachusetts
bdh_wnhp_massachusetts <- tibble(
  Years = us_AmericanIndianorAlaskaNativeAlone_data$Years,
  Percentage_wnhp_men = us_AmericanIndianorAlaskaNativeAlone_data$`...245`,
  Race = "American Indian or Alaska Native Alone"
)

# Michigan
bdh_wnhp_michigan <- tibble(
  Years = us_AmericanIndianorAlaskaNativeAlone_data$Years,
  Percentage_wnhp_men = us_AmericanIndianorAlaskaNativeAlone_data$`...257`,
  Race = "American Indian or Alaska Native Alone"
)

# Minnesota
bdh_wnhp_minnesota <- tibble(
  Years = us_AmericanIndianorAlaskaNativeAlone_data$Years,
  Percentage_wnhp_men = us_AmericanIndianorAlaskaNativeAlone_data$`...269`,
  Race = "American Indian or Alaska Native Alone"
)

# Mississippi
bdh_wnhp_mississippi <- tibble(
  Years = us_AmericanIndianorAlaskaNativeAlone_data$Years,
  Percentage_wnhp_men = us_AmericanIndianorAlaskaNativeAlone_data$`...281`,
  Race = "American Indian or Alaska Native Alone"
)

# Missouri
bdh_wnhp_missouri <- tibble(
  Years = us_AmericanIndianorAlaskaNativeAlone_data$Years,
  Percentage_wnhp_men = us_AmericanIndianorAlaskaNativeAlone_data$`...293`,
  Race = "American Indian or Alaska Native Alone"
)

# Montana
bdh_wnhp_montana <- tibble(
  Years = us_AmericanIndianorAlaskaNativeAlone_data$Years,
  Percentage_wnhp_men = us_AmericanIndianorAlaskaNativeAlone_data$`...305`,
  Race = "American Indian or Alaska Native Alone"
)

# Nebraska
bdh_wnhp_nebraska <- tibble(
  Years = us_AmericanIndianorAlaskaNativeAlone_data$Years,
  Percentage_wnhp_men = us_AmericanIndianorAlaskaNativeAlone_data$`...317`,
  Race = "American Indian or Alaska Native Alone"
)

# Nevada
bdh_wnhp_nevada <- tibble(
  Years = us_AmericanIndianorAlaskaNativeAlone_data$Years,
  Percentage_wnhp_men = us_AmericanIndianorAlaskaNativeAlone_data$`...329`,
  Race = "American Indian or Alaska Native Alone"
)

# New Hampshire
bdh_wnhp_newhampshire <- tibble(
  Years = us_AmericanIndianorAlaskaNativeAlone_data$Years,
  Percentage_wnhp_men = us_AmericanIndianorAlaskaNativeAlone_data$`...341`,
  Race = "American Indian or Alaska Native Alone"
)

# New Jersey
bdh_wnhp_newjersey <- tibble(
  Years = us_AmericanIndianorAlaskaNativeAlone_data$Years,
  Percentage_wnhp_men = us_AmericanIndianorAlaskaNativeAlone_data$`...353`,
  Race = "American Indian or Alaska Native Alone"
)

# New Mexico
bdh_wnhp_newmexico <- tibble(
  Years = us_AmericanIndianorAlaskaNativeAlone_data$Years,
  Percentage_wnhp_men = us_AmericanIndianorAlaskaNativeAlone_data$`...365`,
  Race = "American Indian or Alaska Native Alone"
)

# New York
bdh_wnhp_newyork <- tibble(
  Years = us_AmericanIndianorAlaskaNativeAlone_data$Years,
  Percentage_wnhp_men = us_AmericanIndianorAlaskaNativeAlone_data$`...377`,
  Race = "American Indian or Alaska Native Alone"
)

# North Carolina
bdh_wnhp_northcarolina <- tibble(
  Years = us_AmericanIndianorAlaskaNativeAlone_data$Years,
  Percentage_wnhp_men = us_AmericanIndianorAlaskaNativeAlone_data$`...389`,
  Race = "American Indian or Alaska Native Alone"
)

# North Dakota
bdh_wnhp_northdakota <- tibble(
  Years = us_AmericanIndianorAlaskaNativeAlone_data$Years,
  Percentage_wnhp_men = us_AmericanIndianorAlaskaNativeAlone_data$`...401`,
  Race = "American Indian or Alaska Native Alone"
)

# Ohio
bdh_wnhp_ohio <- tibble(
  Years = us_AmericanIndianorAlaskaNativeAlone_data$Years,
  Percentage_wnhp_men = us_AmericanIndianorAlaskaNativeAlone_data$`...413`,
  Race = "American Indian or Alaska Native Alone"
)

# Oklahoma
bdh_wnhp_oklahoma <- tibble(
  Years = us_AmericanIndianorAlaskaNativeAlone_data$Years,
  Percentage_wnhp_men = us_AmericanIndianorAlaskaNativeAlone_data$`...425`,
  Race = "American Indian or Alaska Native Alone"
)

# Oregon
bdh_wnhp_oregon <- tibble(
  Years = us_AmericanIndianorAlaskaNativeAlone_data$Years,
  Percentage_wnhp_men = us_AmericanIndianorAlaskaNativeAlone_data$`...437`,
  Race = "American Indian or Alaska Native Alone"
)

# Pennsylvania
bdh_wnhp_pennsylvania <- tibble(
  Years = us_AmericanIndianorAlaskaNativeAlone_data$Years,
  Percentage_wnhp_men = us_AmericanIndianorAlaskaNativeAlone_data$`...449`,
  Race = "American Indian or Alaska Native Alone"
)

# Rhode Island
bdh_wnhp_rhodeisland <- tibble(
  Years = us_AmericanIndianorAlaskaNativeAlone_data$Years,
  Percentage_wnhp_men = us_AmericanIndianorAlaskaNativeAlone_data$`...461`,
  Race = "American Indian or Alaska Native Alone"
)

# South Carolina
bdh_wnhp_southcarolina <- tibble(
  Years = us_AmericanIndianorAlaskaNativeAlone_data$Years,
  Percentage_wnhp_men = us_AmericanIndianorAlaskaNativeAlone_data$`...473`,
  Race = "American Indian or Alaska Native Alone"
)

# South Dakota
bdh_wnhp_southdakota <- tibble(
  Years = us_AmericanIndianorAlaskaNativeAlone_data$Years,
  Percentage_wnhp_men = us_AmericanIndianorAlaskaNativeAlone_data$`...485`,
  Race = "American Indian or Alaska Native Alone"
)

# Tennessee
bdh_wnhp_tennessee <- tibble(
  Years = us_AmericanIndianorAlaskaNativeAlone_data$Years,
  Percentage_wnhp_men = us_AmericanIndianorAlaskaNativeAlone_data$`...497`,
  Race = "American Indian or Alaska Native Alone"
)

# Texas
bdh_wnhp_texas <- tibble(
  Years = us_AmericanIndianorAlaskaNativeAlone_data$Years,
  Percentage_wnhp_men = us_AmericanIndianorAlaskaNativeAlone_data$`...509`,
  Race = "American Indian or Alaska Native Alone"
)

# Utah
bdh_wnhp_utah <- tibble(
  Years = us_AmericanIndianorAlaskaNativeAlone_data$Years,
  Percentage_wnhp_men = us_AmericanIndianorAlaskaNativeAlone_data$`...521`,
  Race = "American Indian or Alaska Native Alone"
)

# Vermont
bdh_wnhp_vermont <- tibble(
  Years = us_AmericanIndianorAlaskaNativeAlone_data$Years,
  Percentage_wnhp_men = us_AmericanIndianorAlaskaNativeAlone_data$`...533`,
  Race = "American Indian or Alaska Native Alone"
)

# Virginia
bdh_wnhp_virginia <- tibble(
  Years = us_AmericanIndianorAlaskaNativeAlone_data$Years,
  Percentage_wnhp_men = us_AmericanIndianorAlaskaNativeAlone_data$`...545`,
  Race = "American Indian or Alaska Native Alone"
)

# Washington
bdh_wnhp_washington <- tibble(
  Years = us_AmericanIndianorAlaskaNativeAlone_data$Years,
  Percentage_wnhp_men = us_AmericanIndianorAlaskaNativeAlone_data$`...557`,
  Race = "American Indian or Alaska Native Alone"
)

# West Virginia
bdh_wnhp_westvirginia <- tibble(
  Years =us_AmericanIndianorAlaskaNativeAlone_data$Years,
  Percentage_wnhp_men = us_AmericanIndianorAlaskaNativeAlone_data$`...569`,
  Race = "American Indian or Alaska Native Alone"
)

# Wisconsin
bdh_wnhp_wisconsin <- tibble(
  Years = us_AmericanIndianorAlaskaNativeAlone_data$Years,
  Percentage_wnhp_men = us_AmericanIndianorAlaskaNativeAlone_data$`...581`,
  Race = "American Indian or Alaska Native Alone"
)

# Wyoming
bdh_wnhp_wyoming <- tibble(
  Years = us_AmericanIndianorAlaskaNativeAlone_data$Years,
  Percentage_wnhp_men = us_AmericanIndianorAlaskaNativeAlone_data$`...593`,
  Race = "American Indian or Alaska Native Alone"
)

# Puerto Rico
bdh_wnhp_puertorico <- tibble(
  Years = us_AmericanIndianorAlaskaNativeAlone_data$Years,
  Percentage_wnhp_men = us_AmericanIndianorAlaskaNativeAlone_data$`...605`,
  Race = "American Indian or Alaska Native Alone"
)

# Combine all states
combined_data_wnhp <- bind_rows(
  bdh_wnhp_alabama,
  bdh_wnhp_alaska,
  bdh_wnhp_arizona,
  bdh_wnhp_arkansas,
  bdh_wnhp_california,
  bdh_wnhp_colorado,
  bdh_wnhp_connecticut,
  bdh_wnhp_delaware,
  bdh_wnhp_florida,
  bdh_wnhp_georgia,
  bdh_wnhp_hawaii,
  bdh_wnhp_idaho,
  bdh_wnhp_illinois,
  bdh_wnhp_indiana,
  bdh_wnhp_iowa,
  bdh_wnhp_kansas,
  bdh_wnhp_kentucky,
  bdh_wnhp_louisiana,
  bdh_wnhp_maine,
  bdh_wnhp_maryland,
  bdh_wnhp_massachusetts,
  bdh_wnhp_michigan,
  bdh_wnhp_minnesota,
  bdh_wnhp_mississippi,
  bdh_wnhp_missouri,
  bdh_wnhp_montana,
  bdh_wnhp_nebraska,
  bdh_wnhp_nevada,
  bdh_wnhp_newhampshire,
  bdh_wnhp_newjersey,
  bdh_wnhp_newmexico,
  bdh_wnhp_newyork,
  bdh_wnhp_northcarolina,
  bdh_wnhp_northdakota,
  bdh_wnhp_ohio,
  bdh_wnhp_oklahoma,
  bdh_wnhp_oregon,
  bdh_wnhp_pennsylvania,
  bdh_wnhp_rhodeisland,
  bdh_wnhp_southcarolina,
  bdh_wnhp_southdakota,
  bdh_wnhp_tennessee,
  bdh_wnhp_texas,
  bdh_wnhp_utah,
  bdh_wnhp_vermont,
  bdh_wnhp_virginia,
  bdh_wnhp_washington,
  bdh_wnhp_westvirginia,
  bdh_wnhp_wisconsin,
  bdh_wnhp_wyoming,
  bdh_wnhp_puertorico
)

print(combined_data_wnhp)

```

5.  **Male, Asian Alone, Across all U.S. States + Puerto Rico (Status: Cleaned)**

```{r}

# Alabama
us_Asianalone_data <- filter(acs_data, Label == "Bachelor's degree or higher*****")
bdh_wnhp_alabama <- tibble(
  Years =  us_Asianalone_data$Years,
  Percentage_wnhp_men = us_Asianalone_data$`...9`,
  Race = "Asian Alone"
)

# Alaska
bdh_wnhp_alaska <- tibble(
  Years = us_Asianalone_data$Years,
  Percentage_wnhp_men = us_Asianalone_data$`...21`,
  Race = "Asian Alone"
)

# Arizona
bdh_wnhp_arizona <- tibble(
  Years = us_Asianalone_data$Years,
  Percentage_wnhp_men = us_Asianalone_data$`...33`,
  Race = "Asian Alone"
)

# Arkansas
bdh_wnhp_arkansas <- tibble(
  Years = us_Asianalone_data$Years,
  Percentage_wnhp_men = us_Asianalone_data$`...45`,
  Race = "Asian Alone"
)

# California
bdh_wnhp_california <- tibble(
  Years = us_Asianalone_data$Years,
  Percentage_wnhp_men = us_Asianalone_data$`...53`,
  Race = "Asian Alone"
)

# Colorado
bdh_wnhp_colorado <- tibble(
  Years = us_Asianalone_data$Years,
  Percentage_wnhp_men = us_Asianalone_data$`...65`,
  Race = "Asian Alone"
)

# Connecticut
bdh_wnhp_connecticut <- tibble(
  Years = us_Asianalone_data$Years,
  Percentage_wnhp_men = us_Asianalone_data$`...77`,
  Race = "Asian Alone"
)

# Delaware
bdh_wnhp_delaware <- tibble(
  Years = us_Asianalone_data$Years,
  Percentage_wnhp_men = us_Asianalone_data$`...89`,
  Race = "Asian Alone"
)

# Florida
bdh_wnhp_florida <- tibble(
  Years = us_Asianalone_data$Years,
  Percentage_wnhp_men = us_Asianalone_data$`...101`,
  Race = "Asian Alone"
)

# Georgia
bdh_wnhp_georgia <- tibble(
  Years = us_Asianalone_data$Years,
  Percentage_wnhp_men = us_Asianalone_data$`...113`,
  Race = "Asian Alone"
)

# Hawaii
bdh_wnhp_hawaii <- tibble(
  Years = us_Asianalone_data$Years,
  Percentage_wnhp_men = us_Asianalone_data$`...125`,
  Race = "Asian Alone"
)

# Idaho
bdh_wnhp_idaho <- tibble(
  Years = us_Asianalone_data$Years,
  Percentage_wnhp_men = us_Asianalone_data$`...137`,
  Race = "Asian Alone"
)

# Illinois
bdh_wnhp_illinois <- tibble(
  Years = us_Asianalone_data$Years,
  Percentage_wnhp_men = us_Asianalone_data$`...149`,
  Race = "Asian Alone"
)

# Indiana
bdh_wnhp_indiana <- tibble(
  Years = us_Asianalone_data$Years,
  Percentage_wnhp_men = us_Asianalone_data$`...161`,
  Race = "Asian Alone"
)

# Iowa
bdh_wnhp_iowa <- tibble(
  Years = us_Asianalone_data$Years,
  Percentage_wnhp_men = us_Asianalone_data$`...173`,
  Race = "Asian Alone"
)

# Kansas
bdh_wnhp_kansas <- tibble(
  Years = us_Asianalone_data$Years,
  Percentage_wnhp_men = us_Asianalone_data$`...185`,
  Race = "Asian Alone"
)

# Kentucky
bdh_wnhp_kentucky <- tibble(
  Years = us_Asianalone_data$Years,
  Percentage_wnhp_men = us_Asianalone_data$`...197`,
  Race = "Asian Alone"
)

# Louisiana
bdh_wnhp_louisiana <- tibble(
  Years = us_Asianalone_data$Years,
  Percentage_wnhp_men = us_Asianalone_data$`...209`,
  Race = "Asian Alone"
)

# Maine
bdh_wnhp_maine <- tibble(
  Years = us_Asianalone_data$Years,
  Percentage_wnhp_men = us_Asianalone_data$`...221`,
  Race = "Asian Alone"
)

# Maryland
bdh_wnhp_maryland <- tibble(
  Years = us_Asianalone_data$Years,
  Percentage_wnhp_men = us_Asianalone_data$`...233`,
  Race = "Asian Alone"
)

# Massachusetts
bdh_wnhp_massachusetts <- tibble(
  Years = us_Asianalone_data$Years,
  Percentage_wnhp_men = us_Asianalone_data$`...245`,
  Race = "Asian Alone"
)

# Michigan
bdh_wnhp_michigan <- tibble(
  Years = us_Asianalone_data$Years,
  Percentage_wnhp_men = us_Asianalone_data$`...257`,
  Race = "Asian Alone"
)

# Minnesota
bdh_wnhp_minnesota <- tibble(
  Years = us_Asianalone_data$Years,
  Percentage_wnhp_men = us_Asianalone_data$`...269`,
  Race = "Asian Alone"
)

# Mississippi
bdh_wnhp_mississippi <- tibble(
  Years = us_Asianalone_data$Years,
  Percentage_wnhp_men = us_Asianalone_data$`...281`,
  Race = "Asian Alone"
)

# Missouri
bdh_wnhp_missouri <- tibble(
  Years = us_Asianalone_data$Years,
  Percentage_wnhp_men = us_Asianalone_data$`...293`,
  Race = "Asian Alone"
)

# Montana
bdh_wnhp_montana <- tibble(
  Years = us_Asianalone_data$Years,
  Percentage_wnhp_men = us_Asianalone_data$`...305`,
  Race = "Asian Alone"
)

# Nebraska
bdh_wnhp_nebraska <- tibble(
  Years = us_Asianalone_data$Years,
  Percentage_wnhp_men = us_Asianalone_data$`...317`,
  Race = "Asian Alone"
)

# Nevada
bdh_wnhp_nevada <- tibble(
  Years = us_Asianalone_data$Years,
  Percentage_wnhp_men = us_Asianalone_data$`...329`,
  Race = "Asian Alone"
)

# New Hampshire
bdh_wnhp_newhampshire <- tibble(
  Years = us_Asianalone_data$Years,
  Percentage_wnhp_men = us_Asianalone_data$`...341`,
  Race = "Asian Alone"
)

# New Jersey
bdh_wnhp_newjersey <- tibble(
  Years = us_Asianalone_data$Years,
  Percentage_wnhp_men = us_Asianalone_data$`...353`,
  Race = "Asian Alone"
)

# New Mexico
bdh_wnhp_newmexico <- tibble(
  Years = us_Asianalone_data$Years,
  Percentage_wnhp_men = us_Asianalone_data$`...365`,
  Race = "Asian Alone"
)

# New York
bdh_wnhp_newyork <- tibble(
  Years = us_Asianalone_data$Years,
  Percentage_wnhp_men = us_Asianalone_data$`...377`,
  Race = "Asian Alone"
)

# North Carolina
bdh_wnhp_northcarolina <- tibble(
  Years = us_Asianalone_data$Years,
  Percentage_wnhp_men = us_Asianalone_data$`...389`,
  Race = "Asian Alone"
)

# North Dakota
bdh_wnhp_northdakota <- tibble(
  Years = us_Asianalone_data$Years,
  Percentage_wnhp_men = us_Asianalone_data$`...401`,
  Race = "Asian Alone"
)

# Ohio
bdh_wnhp_ohio <- tibble(
  Years = us_Asianalone_data$Years,
  Percentage_wnhp_men = us_Asianalone_data$`...413`,
  Race = "Asian Alone"
)

# Oklahoma
bdh_wnhp_oklahoma <- tibble(
  Years = us_Asianalone_data$Years,
  Percentage_wnhp_men = us_Asianalone_data$`...425`,
  Race = "Asian Alone"
)

# Oregon
bdh_wnhp_oregon <- tibble(
  Years = us_Asianalone_data$Years,
  Percentage_wnhp_men = us_Asianalone_data$`...437`,
  Race = "Asian Alone"
)

# Pennsylvania
bdh_wnhp_pennsylvania <- tibble(
  Years = us_Asianalone_data$Years,
  Percentage_wnhp_men = us_Asianalone_data$`...449`,
  Race = "Asian Alone"
)

# Rhode Island
bdh_wnhp_rhodeisland <- tibble(
  Years = us_Asianalone_data$Years,
  Percentage_wnhp_men = us_Asianalone_data$`...461`,
  Race = "Asian Alone"
)

# South Carolina
bdh_wnhp_southcarolina <- tibble(
  Years = us_Asianalone_data$Years,
  Percentage_wnhp_men = us_Asianalone_data$`...473`,
  Race = "Asian Alone"
)

# South Dakota
bdh_wnhp_southdakota <- tibble(
  Years = us_Asianalone_data$Years,
  Percentage_wnhp_men = us_Asianalone_data$`...485`,
  Race = "Asian Alone"
)

# Tennessee
bdh_wnhp_tennessee <- tibble(
  Years = us_Asianalone_data$Years,
  Percentage_wnhp_men = us_Asianalone_data$`...497`,
  Race = "Asian Alone"
)

# Texas
bdh_wnhp_texas <- tibble(
  Years = us_Asianalone_data$Years,
  Percentage_wnhp_men = us_Asianalone_data$`...509`,
  Race = "Asian Alone"
)

# Utah
bdh_wnhp_utah <- tibble(
  Years = us_Asianalone_data$Years,
  Percentage_wnhp_men = us_Asianalone_data$`...521`,
  Race = "Asian Alone"
)

# Vermont
bdh_wnhp_vermont <- tibble(
  Years = us_Asianalone_data$Years,
  Percentage_wnhp_men = us_Asianalone_data$`...533`,
  Race = "Asian Alone"
)

# Virginia
bdh_wnhp_virginia <- tibble(
  Years = us_Asianalone_data$Years,
  Percentage_wnhp_men = us_Asianalone_data$`...545`,
  Race = "Asian Alone"
)

# Washington
bdh_wnhp_washington <- tibble(
  Years = us_Asianalone_data$Years,
  Percentage_wnhp_men = us_Asianalone_data$`...557`,
  Race = "Asian Alone"
)

# West Virginia
bdh_wnhp_westvirginia <- tibble(
  Years =us_Asianalone_data$Years,
  Percentage_wnhp_men = us_Asianalone_data$`...569`,
  Race = "Asian Alone"
)

# Wisconsin
bdh_wnhp_wisconsin <- tibble(
  Years = us_Asianalone_data$Years,
  Percentage_wnhp_men = us_Asianalone_data$`...581`,
  Race = "Asian Alone"
)

# Wyoming
bdh_wnhp_wyoming <- tibble(
  Years = us_Asianalone_data$Years,
  Percentage_wnhp_men = us_Asianalone_data$`...593`,
  Race = "Asian Alone"
)

# Puerto Rico
bdh_wnhp_puertorico <- tibble(
  Years = us_Asianalone_data$Years,
  Percentage_wnhp_men = us_Asianalone_data$`...605`,
  Race = "Asian Alone"
)

# Combine all states
combined_data_wnhp <- bind_rows(
  bdh_wnhp_alabama,
  bdh_wnhp_alaska,
  bdh_wnhp_arizona,
  bdh_wnhp_arkansas,
  bdh_wnhp_california,
  bdh_wnhp_colorado,
  bdh_wnhp_connecticut,
  bdh_wnhp_delaware,
  bdh_wnhp_florida,
  bdh_wnhp_georgia,
  bdh_wnhp_hawaii,
  bdh_wnhp_idaho,
  bdh_wnhp_illinois,
  bdh_wnhp_indiana,
  bdh_wnhp_iowa,
  bdh_wnhp_kansas,
  bdh_wnhp_kentucky,
  bdh_wnhp_louisiana,
  bdh_wnhp_maine,
  bdh_wnhp_maryland,
  bdh_wnhp_massachusetts,
  bdh_wnhp_michigan,
  bdh_wnhp_minnesota,
  bdh_wnhp_mississippi,
  bdh_wnhp_missouri,
  bdh_wnhp_montana,
  bdh_wnhp_nebraska,
  bdh_wnhp_nevada,
  bdh_wnhp_newhampshire,
  bdh_wnhp_newjersey,
  bdh_wnhp_newmexico,
  bdh_wnhp_newyork,
  bdh_wnhp_northcarolina,
  bdh_wnhp_northdakota,
  bdh_wnhp_ohio,
  bdh_wnhp_oklahoma,
  bdh_wnhp_oregon,
  bdh_wnhp_pennsylvania,
  bdh_wnhp_rhodeisland,
  bdh_wnhp_southcarolina,
  bdh_wnhp_southdakota,
  bdh_wnhp_tennessee,
  bdh_wnhp_texas,
  bdh_wnhp_utah,
  bdh_wnhp_vermont,
  bdh_wnhp_virginia,
  bdh_wnhp_washington,
  bdh_wnhp_westvirginia,
  bdh_wnhp_wisconsin,
  bdh_wnhp_wyoming,
  bdh_wnhp_puertorico
)

print(combined_data_wnhp)

```

6.  **Male, Native Hawaiian and Other Pacific Islander Alone, Across all U.S. States + Puerto Rico (Status: Cleaned)**

```{r}

# Alabama
us_NativeHawaiianAlone_data <- filter(acs_data, Label == "Bachelor's degree or higher******")
bdh_wnhp_alabama <- tibble(
  Years =  us_NativeHawaiianAlone_data$Years,
  Percentage_wnhp_men = us_NativeHawaiianAlone_data$`...9`,
  Race = "Native Hawaiian and Other Pacific Islander Alone"
)

# Alaska
bdh_wnhp_alaska <- tibble(
  Years = us_NativeHawaiianAlone_data$Years,
  Percentage_wnhp_men = us_NativeHawaiianAlone_data$`...21`,
  Race = "Native Hawaiian and Other Pacific Islander Alone"
)

# Arizona
bdh_wnhp_arizona <- tibble(
  Years = us_NativeHawaiianAlone_data$Years,
  Percentage_wnhp_men = us_NativeHawaiianAlone_data$`...33`,
  Race = "Native Hawaiian and Other Pacific Islander Alone"
)

# Arkansas
bdh_wnhp_arkansas <- tibble(
  Years = us_NativeHawaiianAlone_data$Years,
  Percentage_wnhp_men = us_NativeHawaiianAlone_data$`...45`,
  Race = "Native Hawaiian and Other Pacific Islander Alone"
)

# California
bdh_wnhp_california <- tibble(
  Years = us_NativeHawaiianAlone_data$Years,
  Percentage_wnhp_men = us_NativeHawaiianAlone_data$`...53`,
  Race = "Native Hawaiian and Other Pacific Islander Alone"
)

# Colorado
bdh_wnhp_colorado <- tibble(
  Years = us_NativeHawaiianAlone_data$Years,
  Percentage_wnhp_men = us_NativeHawaiianAlone_data$`...65`,
  Race = "Native Hawaiian and Other Pacific Islander Alone"
)

# Connecticut
bdh_wnhp_connecticut <- tibble(
  Years = us_NativeHawaiianAlone_data$Years,
  Percentage_wnhp_men = us_NativeHawaiianAlone_data$`...77`,
  Race = "Native Hawaiian and Other Pacific Islander Alone"
)

# Delaware
bdh_wnhp_delaware <- tibble(
  Years = us_NativeHawaiianAlone_data$Years,
  Percentage_wnhp_men = us_NativeHawaiianAlone_data$`...89`,
  Race = "Native Hawaiian and Other Pacific Islander Alone"
)

# Florida
bdh_wnhp_florida <- tibble(
  Years = us_NativeHawaiianAlone_data$Years,
  Percentage_wnhp_men = us_NativeHawaiianAlone_data$`...101`,
  Race = "Native Hawaiian and Other Pacific Islander Alone"
)

# Georgia
bdh_wnhp_georgia <- tibble(
  Years = us_NativeHawaiianAlone_data$Years,
  Percentage_wnhp_men = us_NativeHawaiianAlone_data$`...113`,
  Race = "Native Hawaiian and Other Pacific Islander Alone"
)

# Hawaii
bdh_wnhp_hawaii <- tibble(
  Years = us_NativeHawaiianAlone_data$Years,
  Percentage_wnhp_men = us_NativeHawaiianAlone_data$`...125`,
  Race = "Native Hawaiian and Other Pacific Islander Alone"
)

# Idaho
bdh_wnhp_idaho <- tibble(
  Years = us_NativeHawaiianAlone_data$Years,
  Percentage_wnhp_men = us_NativeHawaiianAlone_data$`...137`,
  Race = "Native Hawaiian and Other Pacific Islander Alone"
)

# Illinois
bdh_wnhp_illinois <- tibble(
  Years = us_NativeHawaiianAlone_data$Years,
  Percentage_wnhp_men = us_NativeHawaiianAlone_data$`...149`,
  Race = "Native Hawaiian and Other Pacific Islander Alone"
)

# Indiana
bdh_wnhp_indiana <- tibble(
  Years = us_NativeHawaiianAlone_data$Years,
  Percentage_wnhp_men = us_NativeHawaiianAlone_data$`...161`,
  Race = "Native Hawaiian and Other Pacific Islander Alone"
)

# Iowa
bdh_wnhp_iowa <- tibble(
  Years = us_NativeHawaiianAlone_data$Years,
  Percentage_wnhp_men = us_NativeHawaiianAlone_data$`...173`,
  Race = "Native Hawaiian and Other Pacific Islander Alone"
)

# Kansas
bdh_wnhp_kansas <- tibble(
  Years = us_NativeHawaiianAlone_data$Years,
  Percentage_wnhp_men = us_NativeHawaiianAlone_data$`...185`,
  Race = "Native Hawaiian and Other Pacific Islander Alone"
)

# Kentucky
bdh_wnhp_kentucky <- tibble(
  Years = us_NativeHawaiianAlone_data$Years,
  Percentage_wnhp_men = us_NativeHawaiianAlone_data$`...197`,
  Race = "Native Hawaiian and Other Pacific Islander Alone"
)

# Louisiana
bdh_wnhp_louisiana <- tibble(
  Years = us_NativeHawaiianAlone_data$Years,
  Percentage_wnhp_men = us_NativeHawaiianAlone_data$`...209`,
  Race = "Native Hawaiian and Other Pacific Islander Alone"
)

# Maine
bdh_wnhp_maine <- tibble(
  Years = us_NativeHawaiianAlone_data$Years,
  Percentage_wnhp_men = us_NativeHawaiianAlone_data$`...221`,
  Race = "Native Hawaiian and Other Pacific Islander Alone"
)

# Maryland
bdh_wnhp_maryland <- tibble(
  Years = us_NativeHawaiianAlone_data$Years,
  Percentage_wnhp_men = us_NativeHawaiianAlone_data$`...233`,
  Race = "Native Hawaiian and Other Pacific Islander Alone"
)

# Massachusetts
bdh_wnhp_massachusetts <- tibble(
  Years = us_NativeHawaiianAlone_data$Years,
  Percentage_wnhp_men = us_NativeHawaiianAlone_data$`...245`,
  Race = "Native Hawaiian and Other Pacific Islander Alone"
)

# Michigan
bdh_wnhp_michigan <- tibble(
  Years = us_NativeHawaiianAlone_data$Years,
  Percentage_wnhp_men = us_NativeHawaiianAlone_data$`...257`,
  Race = "Native Hawaiian and Other Pacific Islander Alone"
)

# Minnesota
bdh_wnhp_minnesota <- tibble(
  Years = us_NativeHawaiianAlone_data$Years,
  Percentage_wnhp_men = us_NativeHawaiianAlone_data$`...269`,
  Race = "Native Hawaiian and Other Pacific Islander Alone"
)

# Mississippi
bdh_wnhp_mississippi <- tibble(
  Years = us_NativeHawaiianAlone_data$Years,
  Percentage_wnhp_men = us_NativeHawaiianAlone_data$`...281`,
  Race = "Native Hawaiian and Other Pacific Islander Alone"
)

# Missouri
bdh_wnhp_missouri <- tibble(
  Years = us_NativeHawaiianAlone_data$Years,
  Percentage_wnhp_men = us_NativeHawaiianAlone_data$`...293`,
  Race = "Native Hawaiian and Other Pacific Islander Alone"
)

# Montana
bdh_wnhp_montana <- tibble(
  Years = us_NativeHawaiianAlone_data$Years,
  Percentage_wnhp_men = us_NativeHawaiianAlone_data$`...305`,
  Race = "Native Hawaiian and Other Pacific Islander Alone"
)

# Nebraska
bdh_wnhp_nebraska <- tibble(
  Years = us_NativeHawaiianAlone_data$Years,
  Percentage_wnhp_men = us_NativeHawaiianAlone_data$`...317`,
  Race = "Native Hawaiian and Other Pacific Islander Alone"
)

# Nevada
bdh_wnhp_nevada <- tibble(
  Years = us_NativeHawaiianAlone_data$Years,
  Percentage_wnhp_men = us_NativeHawaiianAlone_data$`...329`,
  Race = "Native Hawaiian and Other Pacific Islander Alone"
)

# New Hampshire
bdh_wnhp_newhampshire <- tibble(
  Years = us_NativeHawaiianAlone_data$Years,
  Percentage_wnhp_men = us_NativeHawaiianAlone_data$`...341`,
  Race = "Native Hawaiian and Other Pacific Islander Alone"
)

# New Jersey
bdh_wnhp_newjersey <- tibble(
  Years = us_NativeHawaiianAlone_data$Years,
  Percentage_wnhp_men = us_NativeHawaiianAlone_data$`...353`,
  Race = "Native Hawaiian and Other Pacific Islander Alone"
)

# New Mexico
bdh_wnhp_newmexico <- tibble(
  Years = us_NativeHawaiianAlone_data$Years,
  Percentage_wnhp_men = us_NativeHawaiianAlone_data$`...365`,
  Race = "Native Hawaiian and Other Pacific Islander Alone"
)

# New York
bdh_wnhp_newyork <- tibble(
  Years = us_NativeHawaiianAlone_data$Years,
  Percentage_wnhp_men = us_NativeHawaiianAlone_data$`...377`,
  Race = "Native Hawaiian and Other Pacific Islander Alone"
)

# North Carolina
bdh_wnhp_northcarolina <- tibble(
  Years = us_NativeHawaiianAlone_data$Years,
  Percentage_wnhp_men = us_NativeHawaiianAlone_data$`...389`,
  Race = "Native Hawaiian and Other Pacific Islander Alone"
)

# North Dakota
bdh_wnhp_northdakota <- tibble(
  Years = us_NativeHawaiianAlone_data$Years,
  Percentage_wnhp_men = us_NativeHawaiianAlone_data$`...401`,
  Race = "Native Hawaiian and Other Pacific Islander Alone"
)

# Ohio
bdh_wnhp_ohio <- tibble(
  Years = us_NativeHawaiianAlone_data$Years,
  Percentage_wnhp_men = us_NativeHawaiianAlone_data$`...413`,
  Race = "Native Hawaiian and Other Pacific Islander Alone"
)

# Oklahoma
bdh_wnhp_oklahoma <- tibble(
  Years = us_NativeHawaiianAlone_data$Years,
  Percentage_wnhp_men = us_NativeHawaiianAlone_data$`...425`,
  Race = "Native Hawaiian and Other Pacific Islander Alone"
)

# Oregon
bdh_wnhp_oregon <- tibble(
  Years = us_NativeHawaiianAlone_data$Years,
  Percentage_wnhp_men = us_NativeHawaiianAlone_data$`...437`,
  Race = "Native Hawaiian and Other Pacific Islander Alone"
)

# Pennsylvania
bdh_wnhp_pennsylvania <- tibble(
  Years = us_NativeHawaiianAlone_data$Years,
  Percentage_wnhp_men = us_NativeHawaiianAlone_data$`...449`,
  Race = "Native Hawaiian and Other Pacific Islander Alone"
)

# Rhode Island
bdh_wnhp_rhodeisland <- tibble(
  Years = us_NativeHawaiianAlone_data$Years,
  Percentage_wnhp_men = us_NativeHawaiianAlone_data$`...461`,
  Race = "Native Hawaiian and Other Pacific Islander Alone"
)

# South Carolina
bdh_wnhp_southcarolina <- tibble(
  Years = us_NativeHawaiianAlone_data$Years,
  Percentage_wnhp_men = us_NativeHawaiianAlone_data$`...473`,
  Race = "Native Hawaiian and Other Pacific Islander Alone"
)

# South Dakota
bdh_wnhp_southdakota <- tibble(
  Years = us_NativeHawaiianAlone_data$Years,
  Percentage_wnhp_men = us_NativeHawaiianAlone_data$`...485`,
  Race = "Native Hawaiian and Other Pacific Islander Alone"
)

# Tennessee
bdh_wnhp_tennessee <- tibble(
  Years = us_NativeHawaiianAlone_data$Years,
  Percentage_wnhp_men = us_NativeHawaiianAlone_data$`...497`,
  Race = "Native Hawaiian and Other Pacific Islander Alone"
)

# Texas
bdh_wnhp_texas <- tibble(
  Years = us_NativeHawaiianAlone_data$Years,
  Percentage_wnhp_men = us_NativeHawaiianAlone_data$`...509`,
  Race = "Native Hawaiian and Other Pacific Islander Alone"
)

# Utah
bdh_wnhp_utah <- tibble(
  Years = us_NativeHawaiianAlone_data$Years,
  Percentage_wnhp_men = us_NativeHawaiianAlone_data$`...521`,
  Race = "Native Hawaiian and Other Pacific Islander Alone"
)

# Vermont
bdh_wnhp_vermont <- tibble(
  Years = us_NativeHawaiianAlone_data$Years,
  Percentage_wnhp_men = us_NativeHawaiianAlone_data$`...533`,
  Race = "Native Hawaiian and Other Pacific Islander Alone"
)

# Virginia
bdh_wnhp_virginia <- tibble(
  Years = us_NativeHawaiianAlone_data$Years,
  Percentage_wnhp_men = us_NativeHawaiianAlone_data$`...545`,
  Race = "Native Hawaiian and Other Pacific Islander Alone"
)

# Washington
bdh_wnhp_washington <- tibble(
  Years = us_NativeHawaiianAlone_data$Years,
  Percentage_wnhp_men = us_NativeHawaiianAlone_data$`...557`,
  Race = "Native Hawaiian and Other Pacific Islander Alone"
)

# West Virginia
bdh_wnhp_westvirginia <- tibble(
  Years = us_NativeHawaiianAlone_data$Years,
  Percentage_wnhp_men = us_NativeHawaiianAlone_data$`...569`,
  Race = "Native Hawaiian and Other Pacific Islander Alone"
)

# Wisconsin
bdh_wnhp_wisconsin <- tibble(
  Years = us_NativeHawaiianAlone_data$Years,
  Percentage_wnhp_men = us_NativeHawaiianAlone_data$`...581`,
  Race = "Native Hawaiian and Other Pacific Islander Alone"
)

# Wyoming
bdh_wnhp_wyoming <- tibble(
  Years = us_NativeHawaiianAlone_data$Years,
  Percentage_wnhp_men = us_NativeHawaiianAlone_data$`...593`,
  Race = "Native Hawaiian and Other Pacific Islander Alone"
)

# Puerto Rico
bdh_wnhp_puertorico <- tibble(
  Years = us_NativeHawaiianAlone_data$Years,
  Percentage_wnhp_men = us_NativeHawaiianAlone_data$`...605`,
  Race = "Native Hawaiian and Other Pacific Islander Alone"
)

# Combine all states
combined_data_wnhp <- bind_rows(
  bdh_wnhp_alabama,
  bdh_wnhp_alaska,
  bdh_wnhp_arizona,
  bdh_wnhp_arkansas,
  bdh_wnhp_california,
  bdh_wnhp_colorado,
  bdh_wnhp_connecticut,
  bdh_wnhp_delaware,
  bdh_wnhp_florida,
  bdh_wnhp_georgia,
  bdh_wnhp_hawaii,
  bdh_wnhp_idaho,
  bdh_wnhp_illinois,
  bdh_wnhp_indiana,
  bdh_wnhp_iowa,
  bdh_wnhp_kansas,
  bdh_wnhp_kentucky,
  bdh_wnhp_louisiana,
  bdh_wnhp_maine,
  bdh_wnhp_maryland,
  bdh_wnhp_massachusetts,
  bdh_wnhp_michigan,
  bdh_wnhp_minnesota,
  bdh_wnhp_mississippi,
  bdh_wnhp_missouri,
  bdh_wnhp_montana,
  bdh_wnhp_nebraska,
  bdh_wnhp_nevada,
  bdh_wnhp_newhampshire,
  bdh_wnhp_newjersey,
  bdh_wnhp_newmexico,
  bdh_wnhp_newyork,
  bdh_wnhp_northcarolina,
  bdh_wnhp_northdakota,
  bdh_wnhp_ohio,
  bdh_wnhp_oklahoma,
  bdh_wnhp_oregon,
  bdh_wnhp_pennsylvania,
  bdh_wnhp_rhodeisland,
  bdh_wnhp_southcarolina,
  bdh_wnhp_southdakota,
  bdh_wnhp_tennessee,
  bdh_wnhp_texas,
  bdh_wnhp_utah,
  bdh_wnhp_vermont,
  bdh_wnhp_virginia,
  bdh_wnhp_washington,
  bdh_wnhp_westvirginia,
  bdh_wnhp_wisconsin,
  bdh_wnhp_wyoming,
  bdh_wnhp_puertorico
)

print(combined_data_wnhp)

```

7.  **Male, Some other race Alone, Across all U.S. States + Puerto Rico (Status: Cleaned)**

```{r}

# Alabama
us_SomeotherraceAlone_data <- filter(acs_data, Label == "Bachelor's degree or higher*******")
bdh_wnhp_alabama <- tibble(
  Years =  us_SomeotherraceAlone_data$Years,
  Percentage_wnhp_men = us_SomeotherraceAlone_data$`...9`,
  Race = "Some other race Alone"
)

# Alaska
bdh_wnhp_alaska <- tibble(
  Years = us_SomeotherraceAlone_data$Years,
  Percentage_wnhp_men = us_SomeotherraceAlone_data$`...21`,
  Race = "Some other race Alone"
)

# Arizona
bdh_wnhp_arizona <- tibble(
  Years = us_SomeotherraceAlone_data$Years,
  Percentage_wnhp_men = us_SomeotherraceAlone_data$`...33`,
  Race = "Some other race Alone"
)

# Arkansas
bdh_wnhp_arkansas <- tibble(
  Years = us_SomeotherraceAlone_data$Years,
  Percentage_wnhp_men = us_SomeotherraceAlone_data$`...45`,
  Race = "Some other race Alone"
)

# California
bdh_wnhp_california <- tibble(
  Years = us_SomeotherraceAlone_data$Years,
  Percentage_wnhp_men = us_SomeotherraceAlone_data$`...53`,
  Race = "Some other race Alone"
)

# Colorado
bdh_wnhp_colorado <- tibble(
  Years = us_SomeotherraceAlone_data$Years,
  Percentage_wnhp_men = us_SomeotherraceAlone_data$`...65`,
  Race = "Some other race Alone"
)

# Connecticut
bdh_wnhp_connecticut <- tibble(
  Years = us_SomeotherraceAlone_data$Years,
  Percentage_wnhp_men = us_SomeotherraceAlone_data$`...77`,
  Race = "Some other race Alone"
)

# Delaware
bdh_wnhp_delaware <- tibble(
  Years = us_SomeotherraceAlone_data$Years,
  Percentage_wnhp_men = us_SomeotherraceAlone_data$`...89`,
  Race = "Some other race Alone"
)

# Florida
bdh_wnhp_florida <- tibble(
  Years = us_SomeotherraceAlone_data$Years,
  Percentage_wnhp_men = us_SomeotherraceAlone_data$`...101`,
  Race = "Some other race Alone"
)

# Georgia
bdh_wnhp_georgia <- tibble(
  Years = us_SomeotherraceAlone_data$Years,
  Percentage_wnhp_men = us_SomeotherraceAlone_data$`...113`,
  Race = "Some other race Alone"
)

# Hawaii
bdh_wnhp_hawaii <- tibble(
  Years = us_SomeotherraceAlone_data$Years,
  Percentage_wnhp_men = us_SomeotherraceAlone_data$`...125`,
  Race = "Some other race Alone"
)

# Idaho
bdh_wnhp_idaho <- tibble(
  Years = us_SomeotherraceAlone_data$Years,
  Percentage_wnhp_men = us_SomeotherraceAlone_data$`...137`,
  Race = "Some other race Alone"
)

# Illinois
bdh_wnhp_illinois <- tibble(
  Years = us_SomeotherraceAlone_data$Years,
  Percentage_wnhp_men = us_SomeotherraceAlone_data$`...149`,
  Race = "Some other race Alone"
)

# Indiana
bdh_wnhp_indiana <- tibble(
  Years = us_SomeotherraceAlone_data$Years,
  Percentage_wnhp_men = us_SomeotherraceAlone_data$`...161`,
  Race = "Some other race Alone"
)

# Iowa
bdh_wnhp_iowa <- tibble(
  Years = us_SomeotherraceAlone_data$Years,
  Percentage_wnhp_men = us_SomeotherraceAlone_data$`...173`,
  Race = "Some other race Alone"
)

# Kansas
bdh_wnhp_kansas <- tibble(
  Years = us_SomeotherraceAlone_data$Years,
  Percentage_wnhp_men = us_SomeotherraceAlone_data$`...185`,
  Race = "Some other race Alone"
)

# Kentucky
bdh_wnhp_kentucky <- tibble(
  Years = us_SomeotherraceAlone_data$Years,
  Percentage_wnhp_men = us_SomeotherraceAlone_data$`...197`,
  Race = "Some other race Alone"
)

# Louisiana
bdh_wnhp_louisiana <- tibble(
  Years = us_SomeotherraceAlone_data$Years,
  Percentage_wnhp_men = us_SomeotherraceAlone_data$`...209`,
  Race = "Some other race Alone"
)

# Maine
bdh_wnhp_maine <- tibble(
  Years = us_SomeotherraceAlone_data$Years,
  Percentage_wnhp_men = us_SomeotherraceAlone_data$`...221`,
  Race = "Some other race Alone"
)

# Maryland
bdh_wnhp_maryland <- tibble(
  Years = us_SomeotherraceAlone_data$Years,
  Percentage_wnhp_men = us_SomeotherraceAlone_data$`...233`,
  Race = "Some other race Alone"
)

# Massachusetts
bdh_wnhp_massachusetts <- tibble(
  Years = us_SomeotherraceAlone_data$Years,
  Percentage_wnhp_men = us_SomeotherraceAlone_data$`...245`,
  Race = "Some other race Alone"
)

# Michigan
bdh_wnhp_michigan <- tibble(
  Years = us_SomeotherraceAlone_data$Years,
  Percentage_wnhp_men = us_SomeotherraceAlone_data$`...257`,
  Race = "Some other race Alone"
)

# Minnesota
bdh_wnhp_minnesota <- tibble(
  Years = us_SomeotherraceAlone_data$Years,
  Percentage_wnhp_men = us_SomeotherraceAlone_data$`...269`,
  Race = "Some other race Alone"
)

# Mississippi
bdh_wnhp_mississippi <- tibble(
  Years = us_SomeotherraceAlone_data$Years,
  Percentage_wnhp_men = us_SomeotherraceAlone_data$`...281`,
  Race = "Some other race Alone"
)

# Missouri
bdh_wnhp_missouri <- tibble(
  Years = us_SomeotherraceAlone_data$Years,
  Percentage_wnhp_men = us_SomeotherraceAlone_data$`...293`,
  Race = "Some other race Alone"
)

# Montana
bdh_wnhp_montana <- tibble(
  Years = us_SomeotherraceAlone_data$Years,
  Percentage_wnhp_men = us_SomeotherraceAlone_data$`...305`,
  Race = "Some other race Alone"
)

# Nebraska
bdh_wnhp_nebraska <- tibble(
  Years = us_SomeotherraceAlone_data$Years,
  Percentage_wnhp_men = us_SomeotherraceAlone_data$`...317`,
  Race = "Some other race Alone"
)

# Nevada
bdh_wnhp_nevada <- tibble(
  Years = us_SomeotherraceAlone_data$Years,
  Percentage_wnhp_men = us_SomeotherraceAlone_data$`...329`,
  Race = "Some other race Alone"
)

# New Hampshire
bdh_wnhp_newhampshire <- tibble(
  Years = us_SomeotherraceAlone_data$Years,
  Percentage_wnhp_men = us_SomeotherraceAlone_data$`...341`,
  Race = "Some other race Alone"
)

# New Jersey
bdh_wnhp_newjersey <- tibble(
  Years = us_SomeotherraceAlone_data$Years,
  Percentage_wnhp_men = us_SomeotherraceAlone_data$`...353`,
  Race = "Some other race Alone"
)

# New Mexico
bdh_wnhp_newmexico <- tibble(
  Years = us_SomeotherraceAlone_data$Years,
  Percentage_wnhp_men = us_SomeotherraceAlone_data$`...365`,
  Race = "Some other race Alone"
)

# New York
bdh_wnhp_newyork <- tibble(
  Years = us_SomeotherraceAlone_data$Years,
  Percentage_wnhp_men = us_SomeotherraceAlone_data$`...377`,
  Race = "Some other race Alone"
)

# North Carolina
bdh_wnhp_northcarolina <- tibble(
  Years = us_SomeotherraceAlone_data$Years,
  Percentage_wnhp_men = us_SomeotherraceAlone_data$`...389`,
  Race = "Some other race Alone"
)

# North Dakota
bdh_wnhp_northdakota <- tibble(
  Years = us_SomeotherraceAlone_data$Years,
  Percentage_wnhp_men = us_SomeotherraceAlone_data$`...401`,
  Race = "Some other race Alone"
)

# Ohio
bdh_wnhp_ohio <- tibble(
  Years = us_SomeotherraceAlone_data$Years,
  Percentage_wnhp_men = us_SomeotherraceAlone_data$`...413`,
  Race = "Some other race Alone"
)

# Oklahoma
bdh_wnhp_oklahoma <- tibble(
  Years = us_SomeotherraceAlone_data$Years,
  Percentage_wnhp_men = us_SomeotherraceAlone_data$`...425`,
  Race = "Some other race Alone"
)

# Oregon
bdh_wnhp_oregon <- tibble(
  Years = us_SomeotherraceAlone_data$Years,
  Percentage_wnhp_men = us_SomeotherraceAlone_data$`...437`,
  Race = "Some other race Alone"
)

# Pennsylvania
bdh_wnhp_pennsylvania <- tibble(
  Years = us_SomeotherraceAlone_data$Years,
  Percentage_wnhp_men = us_SomeotherraceAlone_data$`...449`,
  Race = "Some other race Alone"
)

# Rhode Island
bdh_wnhp_rhodeisland <- tibble(
  Years = us_SomeotherraceAlone_data$Years,
  Percentage_wnhp_men = us_SomeotherraceAlone_data$`...461`,
  Race = "Some other race Alone"
)

# South Carolina
bdh_wnhp_southcarolina <- tibble(
  Years = us_SomeotherraceAlone_data$Years,
  Percentage_wnhp_men = us_SomeotherraceAlone_data$`...473`,
  Race = "Some other race Alone"
)

# South Dakota
bdh_wnhp_southdakota <- tibble(
  Years = us_SomeotherraceAlone_data$Years,
  Percentage_wnhp_men = us_SomeotherraceAlone_data$`...485`,
  Race = "Some other race Alone"
)

# Tennessee
bdh_wnhp_tennessee <- tibble(
  Years = us_SomeotherraceAlone_data$Years,
  Percentage_wnhp_men = us_SomeotherraceAlone_data$`...497`,
  Race = "Some other race Alone"
)

# Texas
bdh_wnhp_texas <- tibble(
  Years = us_SomeotherraceAlone_data$Years,
  Percentage_wnhp_men = us_SomeotherraceAlone_data$`...509`,
  Race = "Some other race Alone"
)

# Utah
bdh_wnhp_utah <- tibble(
  Years = us_SomeotherraceAlone_data$Years,
  Percentage_wnhp_men = us_SomeotherraceAlone_data$`...521`,
  Race = "Some other race Alone"
)

# Vermont
bdh_wnhp_vermont <- tibble(
  Years = us_SomeotherraceAlone_data$Years,
  Percentage_wnhp_men = us_SomeotherraceAlone_data$`...533`,
  Race = "Some other race Alone"
)

# Virginia
bdh_wnhp_virginia <- tibble(
  Years = us_SomeotherraceAlone_data$Years,
  Percentage_wnhp_men = us_SomeotherraceAlone_data$`...545`,
  Race = "Some other race Alone"
)

# Washington
bdh_wnhp_washington <- tibble(
  Years = us_SomeotherraceAlone_data$Years,
  Percentage_wnhp_men = us_SomeotherraceAlone_data$`...557`,
  Race = "Some other race Alone"
)

# West Virginia
bdh_wnhp_westvirginia <- tibble(
  Years = us_SomeotherraceAlone_data$Years,
  Percentage_wnhp_men = us_SomeotherraceAlone_data$`...569`,
  Race = "Some other race Alone"
)

# Wisconsin
bdh_wnhp_wisconsin <- tibble(
  Years = us_SomeotherraceAlone_data$Years,
  Percentage_wnhp_men = us_SomeotherraceAlone_data$`...581`,
  Race = "Some other race Alone"
)

# Wyoming
bdh_wnhp_wyoming <- tibble(
  Years = us_SomeotherraceAlone_data$Years,
  Percentage_wnhp_men = us_SomeotherraceAlone_data$`...593`,
  Race = "Some other race Alone"
)

# Puerto Rico
bdh_wnhp_puertorico <- tibble(
  Years = us_SomeotherraceAlone_data$Years,
  Percentage_wnhp_men = us_SomeotherraceAlone_data$`...605`,
  Race = "Some other race Alone"
)

# Combine all states
combined_data_wnhp <- bind_rows(
  bdh_wnhp_alabama,
  bdh_wnhp_alaska,
  bdh_wnhp_arizona,
  bdh_wnhp_arkansas,
  bdh_wnhp_california,
  bdh_wnhp_colorado,
  bdh_wnhp_connecticut,
  bdh_wnhp_delaware,
  bdh_wnhp_florida,
  bdh_wnhp_georgia,
  bdh_wnhp_hawaii,
  bdh_wnhp_idaho,
  bdh_wnhp_illinois,
  bdh_wnhp_indiana,
  bdh_wnhp_iowa,
  bdh_wnhp_kansas,
  bdh_wnhp_kentucky,
  bdh_wnhp_louisiana,
  bdh_wnhp_maine,
  bdh_wnhp_maryland,
  bdh_wnhp_massachusetts,
  bdh_wnhp_michigan,
  bdh_wnhp_minnesota,
  bdh_wnhp_mississippi,
  bdh_wnhp_missouri,
  bdh_wnhp_montana,
  bdh_wnhp_nebraska,
  bdh_wnhp_nevada,
  bdh_wnhp_newhampshire,
  bdh_wnhp_newjersey,
  bdh_wnhp_newmexico,
  bdh_wnhp_newyork,
  bdh_wnhp_northcarolina,
  bdh_wnhp_northdakota,
  bdh_wnhp_ohio,
  bdh_wnhp_oklahoma,
  bdh_wnhp_oregon,
  bdh_wnhp_pennsylvania,
  bdh_wnhp_rhodeisland,
  bdh_wnhp_southcarolina,
  bdh_wnhp_southdakota,
  bdh_wnhp_tennessee,
  bdh_wnhp_texas,
  bdh_wnhp_utah,
  bdh_wnhp_vermont,
  bdh_wnhp_virginia,
  bdh_wnhp_washington,
  bdh_wnhp_westvirginia,
  bdh_wnhp_wisconsin,
  bdh_wnhp_wyoming,
  bdh_wnhp_puertorico
)

print(combined_data_wnhp)

```

8.  **Male, Two or more races, Across all U.S. States + Puerto Rico (Status: Cleaned)**

```{r}

# Alabama
us_Twoormoreraces_data <- filter(acs_data, Label == "Bachelor's degree or higher********")
bdh_wnhp_alabama <- tibble(
  Years =  us_Twoormoreraces_data$Years,
  Percentage_wnhp_men = us_Twoormoreraces_data$`...9`,
  Race = "Two or more races,"
)

# Alaska
bdh_wnhp_alaska <- tibble(
  Years = us_Twoormoreraces_data$Years,
  Percentage_wnhp_men = us_Twoormoreraces_data$`...21`,
  Race = "Two or more races,"
)

# Arizona
bdh_wnhp_arizona <- tibble(
  Years = us_Twoormoreraces_data$Years,
  Percentage_wnhp_men = us_Twoormoreraces_data$`...33`,
  Race = "Two or more races,"
)

# Arkansas
bdh_wnhp_arkansas <- tibble(
  Years = us_Twoormoreraces_data$Years,
  Percentage_wnhp_men = us_Twoormoreraces_data$`...45`,
  Race = "Two or more races,"
)

# California
bdh_wnhp_california <- tibble(
  Years = us_Twoormoreraces_data$Years,
  Percentage_wnhp_men = us_Twoormoreraces_data$`...53`,
  Race = "Two or more races,"
)

# Colorado
bdh_wnhp_colorado <- tibble(
  Years = us_Twoormoreraces_data$Years,
  Percentage_wnhp_men = us_Twoormoreraces_data$`...65`,
  Race = "Two or more races,"
)

# Connecticut
bdh_wnhp_connecticut <- tibble(
  Years = us_Twoormoreraces_data$Years,
  Percentage_wnhp_men = us_Twoormoreraces_data$`...77`,
  Race = "Two or more races,"
)

# Delaware
bdh_wnhp_delaware <- tibble(
  Years = us_Twoormoreraces_data$Years,
  Percentage_wnhp_men = us_Twoormoreraces_data$`...89`,
  Race = "Two or more races,"
)

# Florida
bdh_wnhp_florida <- tibble(
  Years = us_Twoormoreraces_data$Years,
  Percentage_wnhp_men = us_Twoormoreraces_data$`...101`,
  Race = "Two or more races,"
)

# Georgia
bdh_wnhp_georgia <- tibble(
  Years = us_Twoormoreraces_data$Years,
  Percentage_wnhp_men = us_Twoormoreraces_data$`...113`,
  Race = "Two or more races,"
)

# Hawaii
bdh_wnhp_hawaii <- tibble(
  Years = us_Twoormoreraces_data$Years,
  Percentage_wnhp_men = us_Twoormoreraces_data$`...125`,
  Race = "Two or more races,"
)

# Idaho
bdh_wnhp_idaho <- tibble(
  Years = us_Twoormoreraces_data$Years,
  Percentage_wnhp_men = us_Twoormoreraces_data$`...137`,
  Race = "Two or more races,"
)

# Illinois
bdh_wnhp_illinois <- tibble(
  Years = us_Twoormoreraces_data$Years,
  Percentage_wnhp_men = us_Twoormoreraces_data$`...149`,
  Race = "Two or more races,"
)

# Indiana
bdh_wnhp_indiana <- tibble(
  Years = us_Twoormoreraces_data$Years,
  Percentage_wnhp_men = us_Twoormoreraces_data$`...161`,
  Race = "Two or more races,"
)

# Iowa
bdh_wnhp_iowa <- tibble(
  Years = us_Twoormoreraces_data$Years,
  Percentage_wnhp_men = us_Twoormoreraces_data$`...173`,
  Race = "Two or more races,"
)

# Kansas
bdh_wnhp_kansas <- tibble(
  Years = us_Twoormoreraces_data$Years,
  Percentage_wnhp_men = us_Twoormoreraces_data$`...185`,
  Race = "Two or more races,"
)

# Kentucky
bdh_wnhp_kentucky <- tibble(
  Years = us_Twoormoreraces_data$Years,
  Percentage_wnhp_men = us_Twoormoreraces_data$`...197`,
  Race = "Two or more races,"
)

# Louisiana
bdh_wnhp_louisiana <- tibble(
  Years = us_Twoormoreraces_data$Years,
  Percentage_wnhp_men = us_Twoormoreraces_data$`...209`,
  Race = "Two or more races,"
)

# Maine
bdh_wnhp_maine <- tibble(
  Years = us_Twoormoreraces_data$Years,
  Percentage_wnhp_men = us_Twoormoreraces_data$`...221`,
  Race = "Two or more races,"
)

# Maryland
bdh_wnhp_maryland <- tibble(
  Years = us_Twoormoreraces_data$Years,
  Percentage_wnhp_men = us_Twoormoreraces_data$`...233`,
  Race = "Two or more races,"
)

# Massachusetts
bdh_wnhp_massachusetts <- tibble(
  Years = us_Twoormoreraces_data$Years,
  Percentage_wnhp_men = us_Twoormoreraces_data$`...245`,
  Race = "Two or more races,"
)

# Michigan
bdh_wnhp_michigan <- tibble(
  Years = us_Twoormoreraces_data$Years,
  Percentage_wnhp_men = us_Twoormoreraces_data$`...257`,
  Race = "Two or more races,"
)

# Minnesota
bdh_wnhp_minnesota <- tibble(
  Years = us_Twoormoreraces_data$Years,
  Percentage_wnhp_men = us_Twoormoreraces_data$`...269`,
  Race = "Two or more races,"
)

# Mississippi
bdh_wnhp_mississippi <- tibble(
  Years = us_Twoormoreraces_data$Years,
  Percentage_wnhp_men = us_Twoormoreraces_data$`...281`,
  Race = "Two or more races,"
)

# Missouri
bdh_wnhp_missouri <- tibble(
  Years = us_Twoormoreraces_data$Years,
  Percentage_wnhp_men = us_Twoormoreraces_data$`...293`,
  Race = "Two or more races,"
)

# Montana
bdh_wnhp_montana <- tibble(
  Years = us_Twoormoreraces_data$Years,
  Percentage_wnhp_men = us_Twoormoreraces_data$`...305`,
  Race = "Two or more races,"
)

# Nebraska
bdh_wnhp_nebraska <- tibble(
  Years = us_Twoormoreraces_data$Years,
  Percentage_wnhp_men = us_Twoormoreraces_data$`...317`,
  Race = "Two or more races,"
)

# Nevada
bdh_wnhp_nevada <- tibble(
  Years = us_Twoormoreraces_data$Years,
  Percentage_wnhp_men = us_Twoormoreraces_data$`...329`,
  Race = "Two or more races,"
)

# New Hampshire
bdh_wnhp_newhampshire <- tibble(
  Years = us_Twoormoreraces_data$Years,
  Percentage_wnhp_men = us_Twoormoreraces_data$`...341`,
  Race = "Two or more races,"
)

# New Jersey
bdh_wnhp_newjersey <- tibble(
  Years = us_Twoormoreraces_data$Years,
  Percentage_wnhp_men = us_Twoormoreraces_data$`...353`,
  Race = "Two or more races,"
)

# New Mexico
bdh_wnhp_newmexico <- tibble(
  Years = us_Twoormoreraces_data$Years,
  Percentage_wnhp_men = us_Twoormoreraces_data$`...365`,
  Race = "Two or more races,"
)

# New York
bdh_wnhp_newyork <- tibble(
  Years = us_Twoormoreraces_data$Years,
  Percentage_wnhp_men = us_Twoormoreraces_data$`...377`,
  Race = "Two or more races,"
)

# North Carolina
bdh_wnhp_northcarolina <- tibble(
  Years = us_Twoormoreraces_data$Years,
  Percentage_wnhp_men = us_Twoormoreraces_data$`...389`,
  Race = "Two or more races,"
)

# North Dakota
bdh_wnhp_northdakota <- tibble(
  Years = us_Twoormoreraces_data$Years,
  Percentage_wnhp_men = us_Twoormoreraces_data$`...401`,
  Race = "Two or more races,"
)

# Ohio
bdh_wnhp_ohio <- tibble(
  Years = us_Twoormoreraces_data$Years,
  Percentage_wnhp_men = us_Twoormoreraces_data$`...413`,
  Race = "Two or more races,"
)

# Oklahoma
bdh_wnhp_oklahoma <- tibble(
  Years = us_Twoormoreraces_data$Years,
  Percentage_wnhp_men = us_Twoormoreraces_data$`...425`,
  Race = "Two or more races,"
)

# Oregon
bdh_wnhp_oregon <- tibble(
  Years = us_Twoormoreraces_data$Years,
  Percentage_wnhp_men = us_Twoormoreraces_data$`...437`,
  Race = "Two or more races,"
)

# Pennsylvania
bdh_wnhp_pennsylvania <- tibble(
  Years = us_Twoormoreraces_data$Years,
  Percentage_wnhp_men = us_Twoormoreraces_data$`...449`,
  Race = "Two or more races,"
)

# Rhode Island
bdh_wnhp_rhodeisland <- tibble(
  Years = us_Twoormoreraces_data$Years,
  Percentage_wnhp_men = us_Twoormoreraces_data$`...461`,
  Race = "Two or more races,"
)

# South Carolina
bdh_wnhp_southcarolina <- tibble(
  Years = us_Twoormoreraces_data$Years,
  Percentage_wnhp_men = us_Twoormoreraces_data$`...473`,
  Race = "Two or more races,"
)

# South Dakota
bdh_wnhp_southdakota <- tibble(
  Years = us_Twoormoreraces_data$Years,
  Percentage_wnhp_men = us_Twoormoreraces_data$`...485`,
  Race = "Two or more races,"
)

# Tennessee
bdh_wnhp_tennessee <- tibble(
  Years = us_Twoormoreraces_data$Years,
  Percentage_wnhp_men = us_Twoormoreraces_data$`...497`,
  Race = "Two or more races,"
)

# Texas
bdh_wnhp_texas <- tibble(
  Years = us_Twoormoreraces_data$Years,
  Percentage_wnhp_men = us_Twoormoreraces_data$`...509`,
  Race = "Two or more races,"
)

# Utah
bdh_wnhp_utah <- tibble(
  Years = us_Twoormoreraces_data$Years,
  Percentage_wnhp_men = us_Twoormoreraces_data$`...521`,
  Race = "Two or more races,"
)

# Vermont
bdh_wnhp_vermont <- tibble(
  Years = us_Twoormoreraces_data$Years,
  Percentage_wnhp_men = us_Twoormoreraces_data$`...533`,
  Race = "Two or more races,"
)

# Virginia
bdh_wnhp_virginia <- tibble(
  Years = us_Twoormoreraces_data$Years,
  Percentage_wnhp_men = us_Twoormoreraces_data$`...545`,
  Race = "Two or more races,"
)

# Washington
bdh_wnhp_washington <- tibble(
  Years = us_Twoormoreraces_data$Years,
  Percentage_wnhp_men = us_Twoormoreraces_data$`...557`,
  Race = "Two or more races,"
)

# West Virginia
bdh_wnhp_westvirginia <- tibble(
  Years = us_Twoormoreraces_data$Years,
  Percentage_wnhp_men = us_Twoormoreraces_data$`...569`,
  Race = "Two or more races,"
)

# Wisconsin
bdh_wnhp_wisconsin <- tibble(
  Years = us_Twoormoreraces_data$Years,
  Percentage_wnhp_men = us_Twoormoreraces_data$`...581`,
  Race = "Two or more races,"
)

# Wyoming
bdh_wnhp_wyoming <- tibble(
  Years = us_Twoormoreraces_data$Years,
  Percentage_wnhp_men = us_Twoormoreraces_data$`...593`,
  Race = "Two or more races,"
)

# Puerto Rico
bdh_wnhp_puertorico <- tibble(
  Years = us_Twoormoreraces_data$Years,
  Percentage_wnhp_men = us_Twoormoreraces_data$`...605`,
  Race = "Two or more races,"
)

# Combine all states
combined_data_wnhp <- bind_rows(
  bdh_wnhp_alabama,
  bdh_wnhp_alaska,
  bdh_wnhp_arizona,
  bdh_wnhp_arkansas,
  bdh_wnhp_california,
  bdh_wnhp_colorado,
  bdh_wnhp_connecticut,
  bdh_wnhp_delaware,
  bdh_wnhp_florida,
  bdh_wnhp_georgia,
  bdh_wnhp_hawaii,
  bdh_wnhp_idaho,
  bdh_wnhp_illinois,
  bdh_wnhp_indiana,
  bdh_wnhp_iowa,
  bdh_wnhp_kansas,
  bdh_wnhp_kentucky,
  bdh_wnhp_louisiana,
  bdh_wnhp_maine,
  bdh_wnhp_maryland,
  bdh_wnhp_massachusetts,
  bdh_wnhp_michigan,
  bdh_wnhp_minnesota,
  bdh_wnhp_mississippi,
  bdh_wnhp_missouri,
  bdh_wnhp_montana,
  bdh_wnhp_nebraska,
  bdh_wnhp_nevada,
  bdh_wnhp_newhampshire,
  bdh_wnhp_newjersey,
  bdh_wnhp_newmexico,
  bdh_wnhp_newyork,
  bdh_wnhp_northcarolina,
  bdh_wnhp_northdakota,
  bdh_wnhp_ohio,
  bdh_wnhp_oklahoma,
  bdh_wnhp_oregon,
  bdh_wnhp_pennsylvania,
  bdh_wnhp_rhodeisland,
  bdh_wnhp_southcarolina,
  bdh_wnhp_southdakota,
  bdh_wnhp_tennessee,
  bdh_wnhp_texas,
  bdh_wnhp_utah,
  bdh_wnhp_vermont,
  bdh_wnhp_virginia,
  bdh_wnhp_washington,
  bdh_wnhp_westvirginia,
  bdh_wnhp_wisconsin,
  bdh_wnhp_wyoming,
  bdh_wnhp_puertorico
)

print(combined_data_wnhp)

```

9.  **Male, Hispanic or Latino Origin, Across all U.S. States + Puerto Rico (Status: Cleaned)**

```{r}
# Alabama
us_HispanicorLatinoOrigin_data <- filter(acs_data, Label == "Bachelor's degree or higher*********")
bdh_wnhp_alabama <- tibble(
  Years =  us_HispanicorLatinoOrigin_data$Years,
  Percentage_wnhp_men = us_HispanicorLatinoOrigin_data$`...9`,
  Race = "Hispanic or Latino Origin"
)

# Alaska
bdh_wnhp_alaska <- tibble(
  Years = us_HispanicorLatinoOrigin_data$Years,
  Percentage_wnhp_men = us_HispanicorLatinoOrigin_data$`...21`,
  Race = "Hispanic or Latino Origin"
)

# Arizona
bdh_wnhp_arizona <- tibble(
  Years = us_HispanicorLatinoOrigin_data$Years,
  Percentage_wnhp_men = us_HispanicorLatinoOrigin_data$`...33`,
  Race = "Hispanic or Latino Origin"
)

# Arkansas
bdh_wnhp_arkansas <- tibble(
  Years = us_HispanicorLatinoOrigin_data$Years,
  Percentage_wnhp_men = us_HispanicorLatinoOrigin_data$`...45`,
  Race = "Hispanic or Latino Origin"
)

# California
bdh_wnhp_california <- tibble(
  Years = us_HispanicorLatinoOrigin_data$Years,
  Percentage_wnhp_men = us_HispanicorLatinoOrigin_data$`...53`,
  Race = "Hispanic or Latino Origin"
)

# Colorado
bdh_wnhp_colorado <- tibble(
  Years = us_HispanicorLatinoOrigin_data$Years,
  Percentage_wnhp_men = us_HispanicorLatinoOrigin_data$`...65`,
  Race = "Hispanic or Latino Origin"
)

# Connecticut
bdh_wnhp_connecticut <- tibble(
  Years = us_HispanicorLatinoOrigin_data$Years,
  Percentage_wnhp_men = us_HispanicorLatinoOrigin_data$`...77`,
  Race = "Hispanic or Latino Origin"
)

# Delaware
bdh_wnhp_delaware <- tibble(
  Years = us_HispanicorLatinoOrigin_data$Years,
  Percentage_wnhp_men = us_HispanicorLatinoOrigin_data$`...89`,
  Race = "Hispanic or Latino Origin"
)

# Florida
bdh_wnhp_florida <- tibble(
  Years = us_HispanicorLatinoOrigin_data$Years,
  Percentage_wnhp_men = us_HispanicorLatinoOrigin_data$`...101`,
  Race = "Hispanic or Latino Origin"
)

# Georgia
bdh_wnhp_georgia <- tibble(
  Years = us_HispanicorLatinoOrigin_data$Years,
  Percentage_wnhp_men = us_HispanicorLatinoOrigin_data$`...113`,
  Race = "Hispanic or Latino Origin"
)

# Hawaii
bdh_wnhp_hawaii <- tibble(
  Years = us_HispanicorLatinoOrigin_data$Years,
  Percentage_wnhp_men = us_HispanicorLatinoOrigin_data$`...125`,
  Race = "Hispanic or Latino Origin"
)

# Idaho
bdh_wnhp_idaho <- tibble(
  Years = us_HispanicorLatinoOrigin_data$Years,
  Percentage_wnhp_men = us_HispanicorLatinoOrigin_data$`...137`,
  Race = "Hispanic or Latino Origin"
)

# Illinois
bdh_wnhp_illinois <- tibble(
  Years = us_HispanicorLatinoOrigin_data$Years,
  Percentage_wnhp_men = us_HispanicorLatinoOrigin_data$`...149`,
  Race = "Hispanic or Latino Origin"
)

# Indiana
bdh_wnhp_indiana <- tibble(
  Years = us_HispanicorLatinoOrigin_data$Years,
  Percentage_wnhp_men = us_HispanicorLatinoOrigin_data$`...161`,
  Race = "Hispanic or Latino Origin"
)

# Iowa
bdh_wnhp_iowa <- tibble(
  Years = us_HispanicorLatinoOrigin_data$Years,
  Percentage_wnhp_men = us_HispanicorLatinoOrigin_data$`...173`,
  Race = "Hispanic or Latino Origin"
)

# Kansas
bdh_wnhp_kansas <- tibble(
  Years = us_HispanicorLatinoOrigin_data$Years,
  Percentage_wnhp_men = us_HispanicorLatinoOrigin_data$`...185`,
  Race = "Hispanic or Latino Origin"
)

# Kentucky
bdh_wnhp_kentucky <- tibble(
  Years = us_HispanicorLatinoOrigin_data$Years,
  Percentage_wnhp_men = us_HispanicorLatinoOrigin_data$`...197`,
  Race = "Hispanic or Latino Origin"
)

# Louisiana
bdh_wnhp_louisiana <- tibble(
  Years = us_HispanicorLatinoOrigin_data$Years,
  Percentage_wnhp_men = us_HispanicorLatinoOrigin_data$`...209`,
  Race = "Hispanic or Latino Origin"
)

# Maine
bdh_wnhp_maine <- tibble(
  Years = us_HispanicorLatinoOrigin_data$Years,
  Percentage_wnhp_men = us_HispanicorLatinoOrigin_data$`...221`,
  Race = "Hispanic or Latino Origin"
)

# Maryland
bdh_wnhp_maryland <- tibble(
  Years = us_HispanicorLatinoOrigin_data$Years,
  Percentage_wnhp_men = us_HispanicorLatinoOrigin_data$`...233`,
  Race = "Hispanic or Latino Origin"
)

# Massachusetts
bdh_wnhp_massachusetts <- tibble(
  Years = us_HispanicorLatinoOrigin_data$Years,
  Percentage_wnhp_men = us_HispanicorLatinoOrigin_data$`...245`,
  Race = "Hispanic or Latino Origin"
)

# Michigan
bdh_wnhp_michigan <- tibble(
  Years = us_HispanicorLatinoOrigin_data$Years,
  Percentage_wnhp_men = us_HispanicorLatinoOrigin_data$`...257`,
  Race = "Hispanic or Latino Origin"
)

# Minnesota
bdh_wnhp_minnesota <- tibble(
  Years = us_HispanicorLatinoOrigin_data$Years,
  Percentage_wnhp_men = us_HispanicorLatinoOrigin_data$`...269`,
  Race = "Hispanic or Latino Origin"
)

# Mississippi
bdh_wnhp_mississippi <- tibble(
  Years = us_HispanicorLatinoOrigin_data$Years,
  Percentage_wnhp_men = us_HispanicorLatinoOrigin_data$`...281`,
  Race = "Hispanic or Latino Origin"
)

# Missouri
bdh_wnhp_missouri <- tibble(
  Years = us_HispanicorLatinoOrigin_data$Years,
  Percentage_wnhp_men = us_HispanicorLatinoOrigin_data$`...293`,
  Race = "Hispanic or Latino Origin"
)

# Montana
bdh_wnhp_montana <- tibble(
  Years = us_HispanicorLatinoOrigin_data$Years,
  Percentage_wnhp_men = us_HispanicorLatinoOrigin_data$`...305`,
  Race = "Hispanic or Latino Origin"
)

# Nebraska
bdh_wnhp_nebraska <- tibble(
  Years = us_HispanicorLatinoOrigin_data$Years,
  Percentage_wnhp_men = us_HispanicorLatinoOrigin_data$`...317`,
  Race = "Hispanic or Latino Origin"
)

# Nevada
bdh_wnhp_nevada <- tibble(
  Years = us_HispanicorLatinoOrigin_data$Years,
  Percentage_wnhp_men = us_HispanicorLatinoOrigin_data$`...329`,
  Race = "Hispanic or Latino Origin"
)

# New Hampshire
bdh_wnhp_newhampshire <- tibble(
  Years = us_HispanicorLatinoOrigin_data$Years,
  Percentage_wnhp_men = us_HispanicorLatinoOrigin_data$`...341`,
  Race = "Hispanic or Latino Origin"
)

# New Jersey
bdh_wnhp_newjersey <- tibble(
  Years = us_HispanicorLatinoOrigin_data$Years,
  Percentage_wnhp_men = us_HispanicorLatinoOrigin_data$`...353`,
  Race = "Hispanic or Latino Origin"
)

# New Mexico
bdh_wnhp_newmexico <- tibble(
  Years = us_HispanicorLatinoOrigin_data$Years,
  Percentage_wnhp_men = us_HispanicorLatinoOrigin_data$`...365`,
  Race = "Hispanic or Latino Origin"
)

# New York
bdh_wnhp_newyork <- tibble(
  Years = us_HispanicorLatinoOrigin_data$Years,
  Percentage_wnhp_men = us_HispanicorLatinoOrigin_data$`...377`,
  Race = "Hispanic or Latino Origin"
)

# North Carolina
bdh_wnhp_northcarolina <- tibble(
  Years = us_HispanicorLatinoOrigin_data$Years,
  Percentage_wnhp_men = us_HispanicorLatinoOrigin_data$`...389`,
  Race = "Hispanic or Latino Origin"
)

# North Dakota
bdh_wnhp_northdakota <- tibble(
  Years = us_HispanicorLatinoOrigin_data$Years,
  Percentage_wnhp_men = us_HispanicorLatinoOrigin_data$`...401`,
  Race = "Hispanic or Latino Origin"
)

# Ohio
bdh_wnhp_ohio <- tibble(
  Years = us_HispanicorLatinoOrigin_data$Years,
  Percentage_wnhp_men = us_HispanicorLatinoOrigin_data$`...413`,
  Race = "Hispanic or Latino Origin"
)

# Oklahoma
bdh_wnhp_oklahoma <- tibble(
  Years = us_HispanicorLatinoOrigin_data$Years,
  Percentage_wnhp_men = us_HispanicorLatinoOrigin_data$`...425`,
  Race = "Hispanic or Latino Origin"
)

# Oregon
bdh_wnhp_oregon <- tibble(
  Years = us_HispanicorLatinoOrigin_data$Years,
  Percentage_wnhp_men = us_HispanicorLatinoOrigin_data$`...437`,
  Race = "Hispanic or Latino Origin"
)

# Pennsylvania
bdh_wnhp_pennsylvania <- tibble(
  Years = us_HispanicorLatinoOrigin_data$Years,
  Percentage_wnhp_men = us_HispanicorLatinoOrigin_data$`...449`,
  Race = "Hispanic or Latino Origin"
)

# Rhode Island
bdh_wnhp_rhodeisland <- tibble(
  Years = us_HispanicorLatinoOrigin_data$Years,
  Percentage_wnhp_men = us_HispanicorLatinoOrigin_data$`...461`,
  Race = "Hispanic or Latino Origin"
)

# South Carolina
bdh_wnhp_southcarolina <- tibble(
  Years = us_HispanicorLatinoOrigin_data$Years,
  Percentage_wnhp_men = us_HispanicorLatinoOrigin_data$`...473`,
  Race = "Hispanic or Latino Origin"
)

# South Dakota
bdh_wnhp_southdakota <- tibble(
  Years = us_HispanicorLatinoOrigin_data$Years,
  Percentage_wnhp_men = us_HispanicorLatinoOrigin_data$`...485`,
  Race = "Hispanic or Latino Origin"
)

# Tennessee
bdh_wnhp_tennessee <- tibble(
  Years = us_HispanicorLatinoOrigin_data$Years,
  Percentage_wnhp_men = us_HispanicorLatinoOrigin_data$`...497`,
  Race = "Hispanic or Latino Origin"
)

# Texas
bdh_wnhp_texas <- tibble(
  Years = us_HispanicorLatinoOrigin_data$Years,
  Percentage_wnhp_men = us_HispanicorLatinoOrigin_data$`...509`,
  Race = "Hispanic or Latino Origin"
)

# Utah
bdh_wnhp_utah <- tibble(
  Years = us_HispanicorLatinoOrigin_data$Years,
  Percentage_wnhp_men = us_HispanicorLatinoOrigin_data$`...521`,
  Race = "Hispanic or Latino Origin"
)

# Vermont
bdh_wnhp_vermont <- tibble(
  Years = us_HispanicorLatinoOrigin_data$Years,
  Percentage_wnhp_men = us_HispanicorLatinoOrigin_data$`...533`,
  Race = "Hispanic or Latino Origin"
)

# Virginia
bdh_wnhp_virginia <- tibble(
  Years = us_HispanicorLatinoOrigin_data$Years,
  Percentage_wnhp_men = us_HispanicorLatinoOrigin_data$`...545`,
  Race = "Hispanic or Latino Origin"
)

# Washington
bdh_wnhp_washington <- tibble(
  Years = us_HispanicorLatinoOrigin_data$Years,
  Percentage_wnhp_men = us_HispanicorLatinoOrigin_data$`...557`,
  Race = "Hispanic or Latino Origin"
)

# West Virginia
bdh_wnhp_westvirginia <- tibble(
  Years = us_HispanicorLatinoOrigin_data$Years,
  Percentage_wnhp_men = us_HispanicorLatinoOrigin_data$`...569`,
  Race = "Hispanic or Latino Origin"
)

# Wisconsin
bdh_wnhp_wisconsin <- tibble(
  Years = us_HispanicorLatinoOrigin_data$Years,
  Percentage_wnhp_men = us_HispanicorLatinoOrigin_data$`...581`,
  Race = "Hispanic or Latino Origin"
)

# Wyoming
bdh_wnhp_wyoming <- tibble(
  Years = us_HispanicorLatinoOrigin_data$Years,
  Percentage_wnhp_men = us_HispanicorLatinoOrigin_data$`...593`,
  Race = "Hispanic or Latino Origin"
)

# Puerto Rico
bdh_wnhp_puertorico <- tibble(
  Years = us_HispanicorLatinoOrigin_data$Years,
  Percentage_wnhp_men = us_HispanicorLatinoOrigin_data$`...605`,
  Race = "Hispanic or Latino Origin"
)

# Combine all states
combined_data_wnhp <- bind_rows(
  bdh_wnhp_alabama,
  bdh_wnhp_alaska,
  bdh_wnhp_arizona,
  bdh_wnhp_arkansas,
  bdh_wnhp_california,
  bdh_wnhp_colorado,
  bdh_wnhp_connecticut,
  bdh_wnhp_delaware,
  bdh_wnhp_florida,
  bdh_wnhp_georgia,
  bdh_wnhp_hawaii,
  bdh_wnhp_idaho,
  bdh_wnhp_illinois,
  bdh_wnhp_indiana,
  bdh_wnhp_iowa,
  bdh_wnhp_kansas,
  bdh_wnhp_kentucky,
  bdh_wnhp_louisiana,
  bdh_wnhp_maine,
  bdh_wnhp_maryland,
  bdh_wnhp_massachusetts,
  bdh_wnhp_michigan,
  bdh_wnhp_minnesota,
  bdh_wnhp_mississippi,
  bdh_wnhp_missouri,
  bdh_wnhp_montana,
  bdh_wnhp_nebraska,
  bdh_wnhp_nevada,
  bdh_wnhp_newhampshire,
  bdh_wnhp_newjersey,
  bdh_wnhp_newmexico,
  bdh_wnhp_newyork,
  bdh_wnhp_northcarolina,
  bdh_wnhp_northdakota,
  bdh_wnhp_ohio,
  bdh_wnhp_oklahoma,
  bdh_wnhp_oregon,
  bdh_wnhp_pennsylvania,
  bdh_wnhp_rhodeisland,
  bdh_wnhp_southcarolina,
  bdh_wnhp_southdakota,
  bdh_wnhp_tennessee,
  bdh_wnhp_texas,
  bdh_wnhp_utah,
  bdh_wnhp_vermont,
  bdh_wnhp_virginia,
  bdh_wnhp_washington,
  bdh_wnhp_westvirginia,
  bdh_wnhp_wisconsin,
  bdh_wnhp_wyoming,
  bdh_wnhp_puertorico
)

print(combined_data_wnhp)

```
