---
title: "Male Data Cleaning"
editor: visual
---

```{r "Reading Data and Initializing Packages"}
suppressMessages(library(readxl))
suppressMessages(library(tidyverse))

# Uncomment the following two commands if you have not run this file previously after Dylan made the changes

# acs_data_test <- read_excel("dataset/acsfinale.xlsx")
# write_csv(acs_data, file = here::here('dataset', 'ACS_data_rendered.csv'))

acs_data <- read.csv('dataset/ACS_data_rendered.csv')

state_names <- c("Alabama", "Alaska", "Arizona", "Arkansas", "California", "Colorado", "Connecticut", "Delaware", "Florida", "Georgia", "Hawaii", "Idaho", "Illinois", "Indiana", "Iowa", "Kansas", "Kentucky", "Louisiana", "Maine", "Maryland", "Massachusetts", "Michigan", "Minnesota", "Mississippi", "Missouri", "Montana", "Nebraska", "Nevada", "New Hampshire", "New Jersey", "New Mexico", "New York", "North Carolina", "North Dakota", "Ohio", "Oklahoma", "Oregon", "Pennsylvania", "Rhode Island", "South Carolina", "South Dakota", "Tennessee", "Texas", "Utah", "Vermont", "Virginia", "Washington", "West Virginia", "Wisconsin", "Wyoming", "Puerto Rico")

race_names <- c("White Alone", "White alone, not Hispanic or Latino", "Black Alone", "American   
                Indian or Alaska Native Alone", "Asian Alone", "Native Hawaiian and Other Pacific 
                Islander Alone", "Some other race Alone", "Two or more races", "Hispanic or Latino 
                Origin")
```

```{r}
create_dataframe <- function(race_names, state_names, acs_data) {
  race_data <- list()
  for (race in race_names) {
    state_data <- list()
    for (index in 1:51) {
      state = state_names[index]
      multiplier <- which(race_names == race) 
      string2 <- rep("*", multiplier)
      label <- paste("Bachelor's degree or higher", paste(string2, collapse = ""), 
                     sep = "")
      filtered_data <- filter(acs_data, Label == label)
      number <- 9 + 12 * (index - 1)
      state_data[[state]] <- tibble(
        State = state,
        Years = filtered_data$Years,
        Percentage = filtered_data[[paste0("...", number)]],
        Race = race
      )
    }
    combined_state <- bind_rows(state_data)
    race_data[[race]] <- combined_state
  }
  # if you want separate tables for each race, comment out this line of data
  race_data <- bind_rows(race_data)

  return(race_data)
}

create_dataframe(race_names, state_names, acs_data)
```

## **Male, White-alone, Across all U.S. States + Puerto Rico (Status: Cleaned)**

```{r "White Alone"}

create_white_data <- function(state_names, acs_data) {
  state_data <- list()
  for (index in 1:51) {
    state = state_names[index]
    filtered_data <- filter(acs_data, Label == "Bachelor's degree or higher*")
    number <- 9 + 12 * (index - 1)
    state_data[[state]] <- tibble(
      State = state,
      Years = filtered_data$Years,
      Percentage_white_men = filtered_data[[paste0("...", number)]],
      Race = "White alone, not Hispanic or Latino"
    )
  }
  combined_data <- bind_rows(state_data)
  return(combined_data)
}

create_white_data(state_names, acs_data)
```

## **Male, White-alone, not Hispanic or Latino, Across all U.S. States + Puerto Rico (Status: Cleaned)**

```{r "White alone, not Hispanic or Latino"}
create_wnhp_data <- function(state_names, acs_data) {
  state_data <- list()
  for (index in 1:51) {
    state = state_names[index]
    filtered_data <- filter(acs_data, Label == "Bachelor's degree or higher**")
    number <- 9 + 12 * (index - 1)
    state_data[[state]] <- tibble(
      State = state,
      Years = filtered_data$Years,
      Percentage_wnhp_men = filtered_data[[paste0("...", number)]],
      Race = "White alone, not Hispanic or Latino"
    )
  }
  combined_data <- bind_rows(state_data)
  return(combined_data)
}

create_wnhp_data(state_names, acs_data)
```

## **Male, Black Alone, Across all U.S. States + Puerto Rico (Status: Cleaned)**

```{r "Black Alone"}
create_black_data <- function(state_names, acs_data) {
  state_data <- list()
  for (index in 1:51) {
    state = state_names[index]
    filtered_data <- filter(acs_data, Label == "Bachelor's degree or higher***")
    number <- 9 + 12 * (index - 1)
    state_data[[state]] <- tibble(
      State = state,
      Years = filtered_data$Years,
      Percentage_black_men = filtered_data[[paste0("...", number)]],
      Race = "White alone, not Hispanic or Latino"
    )
  }
  combined_data <- bind_rows(state_data)
  return(combined_data)
}

create_black_data(state_names, acs_data)
```

## **Male, American Indian or Alaska Native Alone, Across all U.S. States + Puerto Rico (Status: Cleaned)**

```{r "American Indian or Alaska Native Alone"}
create_wnhp_data <- function(state_names, acs_data) {
  state_data <- list()
  for (index in 1:51) {
    state = state_names[index]
    filtered_data <- filter(acs_data, Label == "Bachelor's degree or higher****")
    number <- 9 + 12 * (index - 1)
    print(state)
    state_data[[state]] <- tibble(
      State = state,
      Years = filtered_data$Years,
      Percentage_wnhp_men = filtered_data[[paste0("...", number)]],
      Race = "White alone, not Hispanic or Latino"
    )
  }
  combined_data <- bind_rows(state_data)
  return(combined_data)
}
```

## **Male, Asian Alone, Across all U.S. States + Puerto Rico (Status: Cleaned)**

```{r "Asian Alone"}
create_wnhp_data <- function(state_names, acs_data) {
  state_data <- list()
  for (index in 1:51) {
    state = state_names[index]
    filtered_data <- filter(acs_data, Label == "Bachelor's degree or higher*****")
    number <- 9 + 12 * (index - 1)
    print(state)
    state_data[[state]] <- tibble(
      State = state,
      Years = filtered_data$Years,
      Percentage_wnhp_men = filtered_data[[paste0("...", number)]],
      Race = "White alone, not Hispanic or Latino"
    )
  }
  combined_data <- bind_rows(state_data)
  return(combined_data)
}
```

## **Male, Native Hawaiian and Other Pacific Islander Alone, Across all U.S. States + Puerto Rico (Status: Cleaned)**

```{r}
create_wnhp_data <- function(state_names, acs_data) {
  state_data <- list()
  for (index in 1:51) {
    state = state_names[index]
    filtered_data <- filter(acs_data, Label == "Bachelor's degree or higher*******")
    number <- 9 + 12 * (index - 1)
    print(state)
    state_data[[state]] <- tibble(
      State = state,
      Years = filtered_data$Years,
      Percentage_wnhp_men = filtered_data[[paste0("...", number)]],
      Race = "White alone, not Hispanic or Latino"
    )
  }
  combined_data <- bind_rows(state_data)
  return(combined_data)
}
```

## **Male, Some other race Alone, Across all U.S. States + Puerto Rico (Status: Cleaned)**

```{r}
create_wnhp_data <- function(state_names, acs_data) {
  state_data <- list()
  for (index in 1:51) {
    state = state_names[index]
    filtered_data <- filter(acs_data, Label == "Bachelor's degree or higher*******")
    number <- 9 + 12 * (index - 1)
    print(state)
    state_data[[state]] <- tibble(
      State = state,
      Years = filtered_data$Years,
      Percentage_wnhp_men = filtered_data[[paste0("...", number)]],
      Race = "White alone, not Hispanic or Latino"
    )
  }
  combined_data <- bind_rows(state_data)
  return(combined_data)
}
```

## **Male, Two or more races, Across all U.S. States + Puerto Rico (Status: Cleaned)**

```{r}

# Alabama
us_Twoormoreraces_data <- filter(acs_data, Label == "Bachelor's degree or higher********")
bdh_wnhp_alabama <- tibble(
  Years =  us_Twoormoreraces_data$Years,
  Percentage_wnhp_men = us_Twoormoreraces_data$`...9`,
  Race = "Two or more races,"
)

# Alaska
bdh_wnhp_alaska <- tibble(
  Years = us_Twoormoreraces_data$Years,
  Percentage_wnhp_men = us_Twoormoreraces_data$`...21`,
  Race = "Two or more races,"
)

# Arizona
bdh_wnhp_arizona <- tibble(
  Years = us_Twoormoreraces_data$Years,
  Percentage_wnhp_men = us_Twoormoreraces_data$`...33`,
  Race = "Two or more races,"
)

# Arkansas
bdh_wnhp_arkansas <- tibble(
  Years = us_Twoormoreraces_data$Years,
  Percentage_wnhp_men = us_Twoormoreraces_data$`...45`,
  Race = "Two or more races,"
)

# California
bdh_wnhp_california <- tibble(
  Years = us_Twoormoreraces_data$Years,
  Percentage_wnhp_men = us_Twoormoreraces_data$`...53`,
  Race = "Two or more races,"
)

# Colorado
bdh_wnhp_colorado <- tibble(
  Years = us_Twoormoreraces_data$Years,
  Percentage_wnhp_men = us_Twoormoreraces_data$`...65`,
  Race = "Two or more races,"
)

# Connecticut
bdh_wnhp_connecticut <- tibble(
  Years = us_Twoormoreraces_data$Years,
  Percentage_wnhp_men = us_Twoormoreraces_data$`...77`,
  Race = "Two or more races,"
)

# Delaware
bdh_wnhp_delaware <- tibble(
  Years = us_Twoormoreraces_data$Years,
  Percentage_wnhp_men = us_Twoormoreraces_data$`...89`,
  Race = "Two or more races,"
)

# Florida
bdh_wnhp_florida <- tibble(
  Years = us_Twoormoreraces_data$Years,
  Percentage_wnhp_men = us_Twoormoreraces_data$`...101`,
  Race = "Two or more races,"
)

# Georgia
bdh_wnhp_georgia <- tibble(
  Years = us_Twoormoreraces_data$Years,
  Percentage_wnhp_men = us_Twoormoreraces_data$`...113`,
  Race = "Two or more races,"
)

# Hawaii
bdh_wnhp_hawaii <- tibble(
  Years = us_Twoormoreraces_data$Years,
  Percentage_wnhp_men = us_Twoormoreraces_data$`...125`,
  Race = "Two or more races,"
)

# Idaho
bdh_wnhp_idaho <- tibble(
  Years = us_Twoormoreraces_data$Years,
  Percentage_wnhp_men = us_Twoormoreraces_data$`...137`,
  Race = "Two or more races,"
)

# Illinois
bdh_wnhp_illinois <- tibble(
  Years = us_Twoormoreraces_data$Years,
  Percentage_wnhp_men = us_Twoormoreraces_data$`...149`,
  Race = "Two or more races,"
)

# Indiana
bdh_wnhp_indiana <- tibble(
  Years = us_Twoormoreraces_data$Years,
  Percentage_wnhp_men = us_Twoormoreraces_data$`...161`,
  Race = "Two or more races,"
)

# Iowa
bdh_wnhp_iowa <- tibble(
  Years = us_Twoormoreraces_data$Years,
  Percentage_wnhp_men = us_Twoormoreraces_data$`...173`,
  Race = "Two or more races,"
)

# Kansas
bdh_wnhp_kansas <- tibble(
  Years = us_Twoormoreraces_data$Years,
  Percentage_wnhp_men = us_Twoormoreraces_data$`...185`,
  Race = "Two or more races,"
)

# Kentucky
bdh_wnhp_kentucky <- tibble(
  Years = us_Twoormoreraces_data$Years,
  Percentage_wnhp_men = us_Twoormoreraces_data$`...197`,
  Race = "Two or more races,"
)

# Louisiana
bdh_wnhp_louisiana <- tibble(
  Years = us_Twoormoreraces_data$Years,
  Percentage_wnhp_men = us_Twoormoreraces_data$`...209`,
  Race = "Two or more races,"
)

# Maine
bdh_wnhp_maine <- tibble(
  Years = us_Twoormoreraces_data$Years,
  Percentage_wnhp_men = us_Twoormoreraces_data$`...221`,
  Race = "Two or more races,"
)

# Maryland
bdh_wnhp_maryland <- tibble(
  Years = us_Twoormoreraces_data$Years,
  Percentage_wnhp_men = us_Twoormoreraces_data$`...233`,
  Race = "Two or more races,"
)

# Massachusetts
bdh_wnhp_massachusetts <- tibble(
  Years = us_Twoormoreraces_data$Years,
  Percentage_wnhp_men = us_Twoormoreraces_data$`...245`,
  Race = "Two or more races,"
)

# Michigan
bdh_wnhp_michigan <- tibble(
  Years = us_Twoormoreraces_data$Years,
  Percentage_wnhp_men = us_Twoormoreraces_data$`...257`,
  Race = "Two or more races,"
)

# Minnesota
bdh_wnhp_minnesota <- tibble(
  Years = us_Twoormoreraces_data$Years,
  Percentage_wnhp_men = us_Twoormoreraces_data$`...269`,
  Race = "Two or more races,"
)

# Mississippi
bdh_wnhp_mississippi <- tibble(
  Years = us_Twoormoreraces_data$Years,
  Percentage_wnhp_men = us_Twoormoreraces_data$`...281`,
  Race = "Two or more races,"
)

# Missouri
bdh_wnhp_missouri <- tibble(
  Years = us_Twoormoreraces_data$Years,
  Percentage_wnhp_men = us_Twoormoreraces_data$`...293`,
  Race = "Two or more races,"
)

# Montana
bdh_wnhp_montana <- tibble(
  Years = us_Twoormoreraces_data$Years,
  Percentage_wnhp_men = us_Twoormoreraces_data$`...305`,
  Race = "Two or more races,"
)

# Nebraska
bdh_wnhp_nebraska <- tibble(
  Years = us_Twoormoreraces_data$Years,
  Percentage_wnhp_men = us_Twoormoreraces_data$`...317`,
  Race = "Two or more races,"
)

# Nevada
bdh_wnhp_nevada <- tibble(
  Years = us_Twoormoreraces_data$Years,
  Percentage_wnhp_men = us_Twoormoreraces_data$`...329`,
  Race = "Two or more races,"
)

# New Hampshire
bdh_wnhp_newhampshire <- tibble(
  Years = us_Twoormoreraces_data$Years,
  Percentage_wnhp_men = us_Twoormoreraces_data$`...341`,
  Race = "Two or more races,"
)

# New Jersey
bdh_wnhp_newjersey <- tibble(
  Years = us_Twoormoreraces_data$Years,
  Percentage_wnhp_men = us_Twoormoreraces_data$`...353`,
  Race = "Two or more races,"
)

# New Mexico
bdh_wnhp_newmexico <- tibble(
  Years = us_Twoormoreraces_data$Years,
  Percentage_wnhp_men = us_Twoormoreraces_data$`...365`,
  Race = "Two or more races,"
)

# New York
bdh_wnhp_newyork <- tibble(
  Years = us_Twoormoreraces_data$Years,
  Percentage_wnhp_men = us_Twoormoreraces_data$`...377`,
  Race = "Two or more races,"
)

# North Carolina
bdh_wnhp_northcarolina <- tibble(
  Years = us_Twoormoreraces_data$Years,
  Percentage_wnhp_men = us_Twoormoreraces_data$`...389`,
  Race = "Two or more races,"
)

# North Dakota
bdh_wnhp_northdakota <- tibble(
  Years = us_Twoormoreraces_data$Years,
  Percentage_wnhp_men = us_Twoormoreraces_data$`...401`,
  Race = "Two or more races,"
)

# Ohio
bdh_wnhp_ohio <- tibble(
  Years = us_Twoormoreraces_data$Years,
  Percentage_wnhp_men = us_Twoormoreraces_data$`...413`,
  Race = "Two or more races,"
)

# Oklahoma
bdh_wnhp_oklahoma <- tibble(
  Years = us_Twoormoreraces_data$Years,
  Percentage_wnhp_men = us_Twoormoreraces_data$`...425`,
  Race = "Two or more races,"
)

# Oregon
bdh_wnhp_oregon <- tibble(
  Years = us_Twoormoreraces_data$Years,
  Percentage_wnhp_men = us_Twoormoreraces_data$`...437`,
  Race = "Two or more races,"
)

# Pennsylvania
bdh_wnhp_pennsylvania <- tibble(
  Years = us_Twoormoreraces_data$Years,
  Percentage_wnhp_men = us_Twoormoreraces_data$`...449`,
  Race = "Two or more races,"
)

# Rhode Island
bdh_wnhp_rhodeisland <- tibble(
  Years = us_Twoormoreraces_data$Years,
  Percentage_wnhp_men = us_Twoormoreraces_data$`...461`,
  Race = "Two or more races,"
)

# South Carolina
bdh_wnhp_southcarolina <- tibble(
  Years = us_Twoormoreraces_data$Years,
  Percentage_wnhp_men = us_Twoormoreraces_data$`...473`,
  Race = "Two or more races,"
)

# South Dakota
bdh_wnhp_southdakota <- tibble(
  Years = us_Twoormoreraces_data$Years,
  Percentage_wnhp_men = us_Twoormoreraces_data$`...485`,
  Race = "Two or more races,"
)

# Tennessee
bdh_wnhp_tennessee <- tibble(
  Years = us_Twoormoreraces_data$Years,
  Percentage_wnhp_men = us_Twoormoreraces_data$`...497`,
  Race = "Two or more races,"
)

# Texas
bdh_wnhp_texas <- tibble(
  Years = us_Twoormoreraces_data$Years,
  Percentage_wnhp_men = us_Twoormoreraces_data$`...509`,
  Race = "Two or more races,"
)

# Utah
bdh_wnhp_utah <- tibble(
  Years = us_Twoormoreraces_data$Years,
  Percentage_wnhp_men = us_Twoormoreraces_data$`...521`,
  Race = "Two or more races,"
)

# Vermont
bdh_wnhp_vermont <- tibble(
  Years = us_Twoormoreraces_data$Years,
  Percentage_wnhp_men = us_Twoormoreraces_data$`...533`,
  Race = "Two or more races,"
)

# Virginia
bdh_wnhp_virginia <- tibble(
  Years = us_Twoormoreraces_data$Years,
  Percentage_wnhp_men = us_Twoormoreraces_data$`...545`,
  Race = "Two or more races,"
)

# Washington
bdh_wnhp_washington <- tibble(
  Years = us_Twoormoreraces_data$Years,
  Percentage_wnhp_men = us_Twoormoreraces_data$`...557`,
  Race = "Two or more races,"
)

# West Virginia
bdh_wnhp_westvirginia <- tibble(
  Years = us_Twoormoreraces_data$Years,
  Percentage_wnhp_men = us_Twoormoreraces_data$`...569`,
  Race = "Two or more races,"
)

# Wisconsin
bdh_wnhp_wisconsin <- tibble(
  Years = us_Twoormoreraces_data$Years,
  Percentage_wnhp_men = us_Twoormoreraces_data$`...581`,
  Race = "Two or more races,"
)

# Wyoming
bdh_wnhp_wyoming <- tibble(
  Years = us_Twoormoreraces_data$Years,
  Percentage_wnhp_men = us_Twoormoreraces_data$`...593`,
  Race = "Two or more races,"
)

# Puerto Rico
bdh_wnhp_puertorico <- tibble(
  Years = us_Twoormoreraces_data$Years,
  Percentage_wnhp_men = us_Twoormoreraces_data$`...605`,
  Race = "Two or more races,"
)

# Combine all states
combined_data_wnhp <- bind_rows(
  bdh_wnhp_alabama,
  bdh_wnhp_alaska,
  bdh_wnhp_arizona,
  bdh_wnhp_arkansas,
  bdh_wnhp_california,
  bdh_wnhp_colorado,
  bdh_wnhp_connecticut,
  bdh_wnhp_delaware,
  bdh_wnhp_florida,
  bdh_wnhp_georgia,
  bdh_wnhp_hawaii,
  bdh_wnhp_idaho,
  bdh_wnhp_illinois,
  bdh_wnhp_indiana,
  bdh_wnhp_iowa,
  bdh_wnhp_kansas,
  bdh_wnhp_kentucky,
  bdh_wnhp_louisiana,
  bdh_wnhp_maine,
  bdh_wnhp_maryland,
  bdh_wnhp_massachusetts,
  bdh_wnhp_michigan,
  bdh_wnhp_minnesota,
  bdh_wnhp_mississippi,
  bdh_wnhp_missouri,
  bdh_wnhp_montana,
  bdh_wnhp_nebraska,
  bdh_wnhp_nevada,
  bdh_wnhp_newhampshire,
  bdh_wnhp_newjersey,
  bdh_wnhp_newmexico,
  bdh_wnhp_newyork,
  bdh_wnhp_northcarolina,
  bdh_wnhp_northdakota,
  bdh_wnhp_ohio,
  bdh_wnhp_oklahoma,
  bdh_wnhp_oregon,
  bdh_wnhp_pennsylvania,
  bdh_wnhp_rhodeisland,
  bdh_wnhp_southcarolina,
  bdh_wnhp_southdakota,
  bdh_wnhp_tennessee,
  bdh_wnhp_texas,
  bdh_wnhp_utah,
  bdh_wnhp_vermont,
  bdh_wnhp_virginia,
  bdh_wnhp_washington,
  bdh_wnhp_westvirginia,
  bdh_wnhp_wisconsin,
  bdh_wnhp_wyoming,
  bdh_wnhp_puertorico
)

print(combined_data_wnhp)

```

## **Male, Hispanic or Latino Origin, Across all U.S. States + Puerto Rico (Status: Cleaned)**

```{r}
# Alabama
us_HispanicorLatinoOrigin_data <- filter(acs_data, Label == "Bachelor's degree or higher*********")
bdh_wnhp_alabama <- tibble(
  Years =  us_HispanicorLatinoOrigin_data$Years,
  Percentage_wnhp_men = us_HispanicorLatinoOrigin_data$`...9`,
  Race = "Hispanic or Latino Origin"
)

# Alaska
bdh_wnhp_alaska <- tibble(
  Years = us_HispanicorLatinoOrigin_data$Years,
  Percentage_wnhp_men = us_HispanicorLatinoOrigin_data$`...21`,
  Race = "Hispanic or Latino Origin"
)

# Arizona
bdh_wnhp_arizona <- tibble(
  Years = us_HispanicorLatinoOrigin_data$Years,
  Percentage_wnhp_men = us_HispanicorLatinoOrigin_data$`...33`,
  Race = "Hispanic or Latino Origin"
)

# Arkansas
bdh_wnhp_arkansas <- tibble(
  Years = us_HispanicorLatinoOrigin_data$Years,
  Percentage_wnhp_men = us_HispanicorLatinoOrigin_data$`...45`,
  Race = "Hispanic or Latino Origin"
)

# California
bdh_wnhp_california <- tibble(
  Years = us_HispanicorLatinoOrigin_data$Years,
  Percentage_wnhp_men = us_HispanicorLatinoOrigin_data$`...53`,
  Race = "Hispanic or Latino Origin"
)

# Colorado
bdh_wnhp_colorado <- tibble(
  Years = us_HispanicorLatinoOrigin_data$Years,
  Percentage_wnhp_men = us_HispanicorLatinoOrigin_data$`...65`,
  Race = "Hispanic or Latino Origin"
)

# Connecticut
bdh_wnhp_connecticut <- tibble(
  Years = us_HispanicorLatinoOrigin_data$Years,
  Percentage_wnhp_men = us_HispanicorLatinoOrigin_data$`...77`,
  Race = "Hispanic or Latino Origin"
)

# Delaware
bdh_wnhp_delaware <- tibble(
  Years = us_HispanicorLatinoOrigin_data$Years,
  Percentage_wnhp_men = us_HispanicorLatinoOrigin_data$`...89`,
  Race = "Hispanic or Latino Origin"
)

# Florida
bdh_wnhp_florida <- tibble(
  Years = us_HispanicorLatinoOrigin_data$Years,
  Percentage_wnhp_men = us_HispanicorLatinoOrigin_data$`...101`,
  Race = "Hispanic or Latino Origin"
)

# Georgia
bdh_wnhp_georgia <- tibble(
  Years = us_HispanicorLatinoOrigin_data$Years,
  Percentage_wnhp_men = us_HispanicorLatinoOrigin_data$`...113`,
  Race = "Hispanic or Latino Origin"
)

# Hawaii
bdh_wnhp_hawaii <- tibble(
  Years = us_HispanicorLatinoOrigin_data$Years,
  Percentage_wnhp_men = us_HispanicorLatinoOrigin_data$`...125`,
  Race = "Hispanic or Latino Origin"
)

# Idaho
bdh_wnhp_idaho <- tibble(
  Years = us_HispanicorLatinoOrigin_data$Years,
  Percentage_wnhp_men = us_HispanicorLatinoOrigin_data$`...137`,
  Race = "Hispanic or Latino Origin"
)

# Illinois
bdh_wnhp_illinois <- tibble(
  Years = us_HispanicorLatinoOrigin_data$Years,
  Percentage_wnhp_men = us_HispanicorLatinoOrigin_data$`...149`,
  Race = "Hispanic or Latino Origin"
)

# Indiana
bdh_wnhp_indiana <- tibble(
  Years = us_HispanicorLatinoOrigin_data$Years,
  Percentage_wnhp_men = us_HispanicorLatinoOrigin_data$`...161`,
  Race = "Hispanic or Latino Origin"
)

# Iowa
bdh_wnhp_iowa <- tibble(
  Years = us_HispanicorLatinoOrigin_data$Years,
  Percentage_wnhp_men = us_HispanicorLatinoOrigin_data$`...173`,
  Race = "Hispanic or Latino Origin"
)

# Kansas
bdh_wnhp_kansas <- tibble(
  Years = us_HispanicorLatinoOrigin_data$Years,
  Percentage_wnhp_men = us_HispanicorLatinoOrigin_data$`...185`,
  Race = "Hispanic or Latino Origin"
)

# Kentucky
bdh_wnhp_kentucky <- tibble(
  Years = us_HispanicorLatinoOrigin_data$Years,
  Percentage_wnhp_men = us_HispanicorLatinoOrigin_data$`...197`,
  Race = "Hispanic or Latino Origin"
)

# Louisiana
bdh_wnhp_louisiana <- tibble(
  Years = us_HispanicorLatinoOrigin_data$Years,
  Percentage_wnhp_men = us_HispanicorLatinoOrigin_data$`...209`,
  Race = "Hispanic or Latino Origin"
)

# Maine
bdh_wnhp_maine <- tibble(
  Years = us_HispanicorLatinoOrigin_data$Years,
  Percentage_wnhp_men = us_HispanicorLatinoOrigin_data$`...221`,
  Race = "Hispanic or Latino Origin"
)

# Maryland
bdh_wnhp_maryland <- tibble(
  Years = us_HispanicorLatinoOrigin_data$Years,
  Percentage_wnhp_men = us_HispanicorLatinoOrigin_data$`...233`,
  Race = "Hispanic or Latino Origin"
)

# Massachusetts
bdh_wnhp_massachusetts <- tibble(
  Years = us_HispanicorLatinoOrigin_data$Years,
  Percentage_wnhp_men = us_HispanicorLatinoOrigin_data$`...245`,
  Race = "Hispanic or Latino Origin"
)

# Michigan
bdh_wnhp_michigan <- tibble(
  Years = us_HispanicorLatinoOrigin_data$Years,
  Percentage_wnhp_men = us_HispanicorLatinoOrigin_data$`...257`,
  Race = "Hispanic or Latino Origin"
)

# Minnesota
bdh_wnhp_minnesota <- tibble(
  Years = us_HispanicorLatinoOrigin_data$Years,
  Percentage_wnhp_men = us_HispanicorLatinoOrigin_data$`...269`,
  Race = "Hispanic or Latino Origin"
)

# Mississippi
bdh_wnhp_mississippi <- tibble(
  Years = us_HispanicorLatinoOrigin_data$Years,
  Percentage_wnhp_men = us_HispanicorLatinoOrigin_data$`...281`,
  Race = "Hispanic or Latino Origin"
)

# Missouri
bdh_wnhp_missouri <- tibble(
  Years = us_HispanicorLatinoOrigin_data$Years,
  Percentage_wnhp_men = us_HispanicorLatinoOrigin_data$`...293`,
  Race = "Hispanic or Latino Origin"
)

# Montana
bdh_wnhp_montana <- tibble(
  Years = us_HispanicorLatinoOrigin_data$Years,
  Percentage_wnhp_men = us_HispanicorLatinoOrigin_data$`...305`,
  Race = "Hispanic or Latino Origin"
)

# Nebraska
bdh_wnhp_nebraska <- tibble(
  Years = us_HispanicorLatinoOrigin_data$Years,
  Percentage_wnhp_men = us_HispanicorLatinoOrigin_data$`...317`,
  Race = "Hispanic or Latino Origin"
)

# Nevada
bdh_wnhp_nevada <- tibble(
  Years = us_HispanicorLatinoOrigin_data$Years,
  Percentage_wnhp_men = us_HispanicorLatinoOrigin_data$`...329`,
  Race = "Hispanic or Latino Origin"
)

# New Hampshire
bdh_wnhp_newhampshire <- tibble(
  Years = us_HispanicorLatinoOrigin_data$Years,
  Percentage_wnhp_men = us_HispanicorLatinoOrigin_data$`...341`,
  Race = "Hispanic or Latino Origin"
)

# New Jersey
bdh_wnhp_newjersey <- tibble(
  Years = us_HispanicorLatinoOrigin_data$Years,
  Percentage_wnhp_men = us_HispanicorLatinoOrigin_data$`...353`,
  Race = "Hispanic or Latino Origin"
)

# New Mexico
bdh_wnhp_newmexico <- tibble(
  Years = us_HispanicorLatinoOrigin_data$Years,
  Percentage_wnhp_men = us_HispanicorLatinoOrigin_data$`...365`,
  Race = "Hispanic or Latino Origin"
)

# New York
bdh_wnhp_newyork <- tibble(
  Years = us_HispanicorLatinoOrigin_data$Years,
  Percentage_wnhp_men = us_HispanicorLatinoOrigin_data$`...377`,
  Race = "Hispanic or Latino Origin"
)

# North Carolina
bdh_wnhp_northcarolina <- tibble(
  Years = us_HispanicorLatinoOrigin_data$Years,
  Percentage_wnhp_men = us_HispanicorLatinoOrigin_data$`...389`,
  Race = "Hispanic or Latino Origin"
)

# North Dakota
bdh_wnhp_northdakota <- tibble(
  Years = us_HispanicorLatinoOrigin_data$Years,
  Percentage_wnhp_men = us_HispanicorLatinoOrigin_data$`...401`,
  Race = "Hispanic or Latino Origin"
)

# Ohio
bdh_wnhp_ohio <- tibble(
  Years = us_HispanicorLatinoOrigin_data$Years,
  Percentage_wnhp_men = us_HispanicorLatinoOrigin_data$`...413`,
  Race = "Hispanic or Latino Origin"
)

# Oklahoma
bdh_wnhp_oklahoma <- tibble(
  Years = us_HispanicorLatinoOrigin_data$Years,
  Percentage_wnhp_men = us_HispanicorLatinoOrigin_data$`...425`,
  Race = "Hispanic or Latino Origin"
)

# Oregon
bdh_wnhp_oregon <- tibble(
  Years = us_HispanicorLatinoOrigin_data$Years,
  Percentage_wnhp_men = us_HispanicorLatinoOrigin_data$`...437`,
  Race = "Hispanic or Latino Origin"
)

# Pennsylvania
bdh_wnhp_pennsylvania <- tibble(
  Years = us_HispanicorLatinoOrigin_data$Years,
  Percentage_wnhp_men = us_HispanicorLatinoOrigin_data$`...449`,
  Race = "Hispanic or Latino Origin"
)

# Rhode Island
bdh_wnhp_rhodeisland <- tibble(
  Years = us_HispanicorLatinoOrigin_data$Years,
  Percentage_wnhp_men = us_HispanicorLatinoOrigin_data$`...461`,
  Race = "Hispanic or Latino Origin"
)

# South Carolina
bdh_wnhp_southcarolina <- tibble(
  Years = us_HispanicorLatinoOrigin_data$Years,
  Percentage_wnhp_men = us_HispanicorLatinoOrigin_data$`...473`,
  Race = "Hispanic or Latino Origin"
)

# South Dakota
bdh_wnhp_southdakota <- tibble(
  Years = us_HispanicorLatinoOrigin_data$Years,
  Percentage_wnhp_men = us_HispanicorLatinoOrigin_data$`...485`,
  Race = "Hispanic or Latino Origin"
)

# Tennessee
bdh_wnhp_tennessee <- tibble(
  Years = us_HispanicorLatinoOrigin_data$Years,
  Percentage_wnhp_men = us_HispanicorLatinoOrigin_data$`...497`,
  Race = "Hispanic or Latino Origin"
)

# Texas
bdh_wnhp_texas <- tibble(
  Years = us_HispanicorLatinoOrigin_data$Years,
  Percentage_wnhp_men = us_HispanicorLatinoOrigin_data$`...509`,
  Race = "Hispanic or Latino Origin"
)

# Utah
bdh_wnhp_utah <- tibble(
  Years = us_HispanicorLatinoOrigin_data$Years,
  Percentage_wnhp_men = us_HispanicorLatinoOrigin_data$`...521`,
  Race = "Hispanic or Latino Origin"
)

# Vermont
bdh_wnhp_vermont <- tibble(
  Years = us_HispanicorLatinoOrigin_data$Years,
  Percentage_wnhp_men = us_HispanicorLatinoOrigin_data$`...533`,
  Race = "Hispanic or Latino Origin"
)

# Virginia
bdh_wnhp_virginia <- tibble(
  Years = us_HispanicorLatinoOrigin_data$Years,
  Percentage_wnhp_men = us_HispanicorLatinoOrigin_data$`...545`,
  Race = "Hispanic or Latino Origin"
)

# Washington
bdh_wnhp_washington <- tibble(
  Years = us_HispanicorLatinoOrigin_data$Years,
  Percentage_wnhp_men = us_HispanicorLatinoOrigin_data$`...557`,
  Race = "Hispanic or Latino Origin"
)

# West Virginia
bdh_wnhp_westvirginia <- tibble(
  Years = us_HispanicorLatinoOrigin_data$Years,
  Percentage_wnhp_men = us_HispanicorLatinoOrigin_data$`...569`,
  Race = "Hispanic or Latino Origin"
)

# Wisconsin
bdh_wnhp_wisconsin <- tibble(
  Years = us_HispanicorLatinoOrigin_data$Years,
  Percentage_wnhp_men = us_HispanicorLatinoOrigin_data$`...581`,
  Race = "Hispanic or Latino Origin"
)

# Wyoming
bdh_wnhp_wyoming <- tibble(
  Years = us_HispanicorLatinoOrigin_data$Years,
  Percentage_wnhp_men = us_HispanicorLatinoOrigin_data$`...593`,
  Race = "Hispanic or Latino Origin"
)

# Puerto Rico
bdh_wnhp_puertorico <- tibble(
  Years = us_HispanicorLatinoOrigin_data$Years,
  Percentage_wnhp_men = us_HispanicorLatinoOrigin_data$`...605`,
  Race = "Hispanic or Latino Origin"
)

# Combine all states
combined_data_wnhp <- bind_rows(
  bdh_wnhp_alabama,
  bdh_wnhp_alaska,
  bdh_wnhp_arizona,
  bdh_wnhp_arkansas,
  bdh_wnhp_california,
  bdh_wnhp_colorado,
  bdh_wnhp_connecticut,
  bdh_wnhp_delaware,
  bdh_wnhp_florida,
  bdh_wnhp_georgia,
  bdh_wnhp_hawaii,
  bdh_wnhp_idaho,
  bdh_wnhp_illinois,
  bdh_wnhp_indiana,
  bdh_wnhp_iowa,
  bdh_wnhp_kansas,
  bdh_wnhp_kentucky,
  bdh_wnhp_louisiana,
  bdh_wnhp_maine,
  bdh_wnhp_maryland,
  bdh_wnhp_massachusetts,
  bdh_wnhp_michigan,
  bdh_wnhp_minnesota,
  bdh_wnhp_mississippi,
  bdh_wnhp_missouri,
  bdh_wnhp_montana,
  bdh_wnhp_nebraska,
  bdh_wnhp_nevada,
  bdh_wnhp_newhampshire,
  bdh_wnhp_newjersey,
  bdh_wnhp_newmexico,
  bdh_wnhp_newyork,
  bdh_wnhp_northcarolina,
  bdh_wnhp_northdakota,
  bdh_wnhp_ohio,
  bdh_wnhp_oklahoma,
  bdh_wnhp_oregon,
  bdh_wnhp_pennsylvania,
  bdh_wnhp_rhodeisland,
  bdh_wnhp_southcarolina,
  bdh_wnhp_southdakota,
  bdh_wnhp_tennessee,
  bdh_wnhp_texas,
  bdh_wnhp_utah,
  bdh_wnhp_vermont,
  bdh_wnhp_virginia,
  bdh_wnhp_washington,
  bdh_wnhp_westvirginia,
  bdh_wnhp_wisconsin,
  bdh_wnhp_wyoming,
  bdh_wnhp_puertorico
)

print(combined_data_wnhp)

```
