---
title: "Female Data Cleaning"
editor: visual
---

```{r}
# Analysis Approach:
# Dependent Variables:
# Percentage of Bachelor’s degrees earned by women of different racial backgrounds (White, Black, Asian, etc.)
# Independent Variable:
# Year

# Data Granularity:
# State-level data
# Segmented by female race

# Hypothesis:
# The percentage of Bachelor's degrees earned by women of different racial backgrounds has changed over time, influenced by various factors. 

```

Female, White-alone, Across all U.S. States + Puerto Rico (Status: Cleaned)

```{r}
## Separating data for Female, White-alone, Across all U.S. States + Puerto Rico (Status: Cleaned) 

library(readxl)
library(dplyr)
library(tibble)

acs_data <- read_excel("dataset/acsfinale.xlsx")

# Alabama
alabama_data <- filter(acs_data, Label == "Bachelor's degree or higher*")
bdh_whitealone_alabama <- tibble(
  Years = alabama_data$Years,
  Percentage_women = alabama_data$`Alabama...13`,
  Race = "White Alone"
)

# Alaska
alaska_data <- filter(acs_data, Label == "Bachelor's degree or higher*")
bdh_whitealone_alaska <- tibble(
  Years = alaska_data$Years,
  Percentage_women = alaska_data$`...25`,
  Race = "White Alone"
)


# Arizona
arizona_data <- filter(acs_data, Label == "Bachelor's degree or higher*")
bdh_whitealone_arizona <- tibble(
  Years = arizona_data$Years,
  Percentage_women = arizona_data$`...37`,
  Race = "White Alone"
)

# Arkansas
arkansas_data <- filter(acs_data, Label == "Bachelor's degree or higher*")
bdh_whitealone_arkansas <- tibble(
  Years = arkansas_data$Years,
  Percentage_women = arkansas_data$`...49`,
  Race = "White Alone"
)

# California
california_data <- filter(acs_data, Label == "Bachelor's degree or higher*")
bdh_whitealone_california <- tibble(
  Years = california_data$Years,
  Percentage_women = california_data$`...61`,
  Race = "White Alone"
)

# Colorado
colorado_data <- filter(acs_data, Label == "Bachelor's degree or higher*")
bdh_whitealone_colorado <- tibble(
  Years = colorado_data$Years,
  Percentage_women = colorado_data$`...73`,
  Race = "White Alone"
)

# Connecticut
connecticut_data <- filter(acs_data, Label == "Bachelor's degree or higher*")
bdh_whitealone_connecticut <- tibble(
  Years = connecticut_data$Years,
  Percentage_women = connecticut_data$`...85`,
  Race = "White Alone"
)

# Delaware
delaware_data <- filter(acs_data, Label == "Bachelor's degree or higher*")
bdh_whitealone_delaware <- tibble(
  Years = delaware_data$Years,
  Percentage_women = delaware_data$`...97`,
  Race = "White Alone"
)

# Florida
florida_data <- filter(acs_data, Label == "Bachelor's degree or higher*")
bdh_whitealone_florida <- tibble(
  Years = florida_data$Years,
  Percentage_women = florida_data$`...109`,
  Race = "White Alone"
)

# Georgia
georgia_data <- filter(acs_data, Label == "Bachelor's degree or higher*")
bdh_whitealone_georgia <- tibble(
  Years = georgia_data$Years,
  Percentage_women = georgia_data$`...121`,
  Race = "White Alone"
)

# Hawaii
hawaii_data <- filter(acs_data, Label == "Bachelor's degree or higher*")
bdh_whitealone_hawaii <- tibble(
  Years = hawaii_data$Years,
  Percentage_women = hawaii_data$`...133`,
  Race = "White Alone"
)

# Idaho
idaho_data <- filter(acs_data, Label == "Bachelor's degree or higher*")
bdh_whitealone_idaho <- tibble(
  Years = idaho_data$Years,
  Percentage_women = idaho_data$`...145`,
  Race = "White Alone"
)

# Illinois
illinois_data <- filter(acs_data, Label == "Bachelor's degree or higher*")
bdh_whitealone_illinois <- tibble(
  Years = illinois_data$Years,
  Percentage_women = illinois_data$`...157`,
  Race = "White Alone"
)

# Indiana
indiana_data <- filter(acs_data, Label == "Bachelor's degree or higher*")
bdh_whitealone_indiana <- tibble(
  Years = indiana_data$Years,
  Percentage_women = indiana_data$`...169`,
  Race = "White Alone"
)

# Iowa
iowa_data <- filter(acs_data, Label == "Bachelor's degree or higher*")
bdh_whitealone_iowa <- tibble(
  Years = iowa_data$Years,
  Percentage_women = iowa_data$`...181`,
  Race = "White Alone"
)

# Kansas
kansas_data <- filter(acs_data, Label == "Bachelor's degree or higher*")
bdh_whitealone_kansas <- tibble(
  Years = kansas_data$Years,
  Percentage_women = kansas_data$`...193`,
  Race = "White Alone"
)

# Kentucky
kentucky_data <- filter(acs_data, Label == "Bachelor's degree or higher*")
bdh_whitealone_kentucky <- tibble(
  Years = kentucky_data$Years,
  Percentage_women = kentucky_data$`...205`,
  Race = "White Alone"
)

# Louisiana
louisiana_data <- filter(acs_data, Label == "Bachelor's degree or higher*")
bdh_whitealone_louisiana <- tibble(
  Years = louisiana_data$Years,
  Percentage_women = louisiana_data$`...217`,
  Race = "White Alone"
)

# Maine
maine_data <- filter(acs_data, Label == "Bachelor's degree or higher*")
bdh_whitealone_maine <- tibble(
  Years = maine_data$Years,
  Percentage_women = maine_data$`...229`,
  Race = "White Alone"
)

# Maryland
maryland_data <- filter(acs_data, Label == "Bachelor's degree or higher*")
bdh_whitealone_maryland <- tibble(
  Years = maryland_data$Years,
  Percentage_women = maryland_data$`...241`,
  Race = "White Alone"
)

# Massachusetts
massachusetts_data <- filter(acs_data, Label == "Bachelor's degree or higher*")
bdh_whitealone_massachusetts <- tibble(
  Years = massachusetts_data$Years,
  Percentage_women = massachusetts_data$`...253`,
  Race = "White Alone"
)

# Michigan
michigan_data <- filter(acs_data, Label == "Bachelor's degree or higher*")
bdh_whitealone_michigan <- tibble(
  Years = michigan_data$Years,
  Percentage_women = michigan_data$`...265`,
  Race = "White Alone"
)

# Minnesota
minnesota_data <- filter(acs_data, Label == "Bachelor's degree or higher*")
bdh_whitealone_minnesota <- tibble(
  Years = minnesota_data$Years,
  Percentage_women = minnesota_data$`...277`,
  Race = "White Alone"
)

# Mississippi
mississippi_data <- filter(acs_data, Label == "Bachelor's degree or higher*")
bdh_whitealone_mississippi <- tibble(
  Years = mississippi_data$Years,
  Percentage_women = mississippi_data$`...289`,
  Race = "White Alone"
)

# Missouri
missouri_data <- filter(acs_data, Label == "Bachelor's degree or higher*")
bdh_whitealone_missouri <- tibble(
  Years = missouri_data$Years,
  Percentage_women = missouri_data$`...301`,
  Race = "White Alone"
)

# Montana
montana_data <- filter(acs_data, Label == "Bachelor's degree or higher*")
bdh_whitealone_montana <- tibble(
  Years = montana_data$Years,
  Percentage_women = montana_data$`...313`,
  Race = "White Alone"
)

# Nebraska
nebraska_data <- filter(acs_data, Label == "Bachelor's degree or higher*")
bdh_whitealone_nebraska <- tibble(
  Years = nebraska_data$Years,
  Percentage_women = nebraska_data$`...325`,
  Race = "White Alone"
)

# Nevada
nevada_data <- filter(acs_data, Label == "Bachelor's degree or higher*")
bdh_whitealone_nevada <- tibble(
  Years = nevada_data$Years,
  Percentage_women = nevada_data$`...337`,
  Race = "White Alone"
)

# New Hampshire
newhampshire_data <- filter(acs_data, Label == "Bachelor's degree or higher*")
bdh_whitealone_newhampshire <- tibble(
  Years = newhampshire_data$Years,
  Percentage_women = newhampshire_data$`...349`,
  Race = "White Alone"
)

# New Jersey
newjersey_data <- filter(acs_data, Label == "Bachelor's degree or higher*")
bdh_whitealone_newjersey <- tibble(
  Years = newjersey_data$Years,
  Percentage_women = newjersey_data$`...361`,
  Race = "White Alone"
)

# New Mexico
newmexico_data <- filter(acs_data, Label == "Bachelor's degree or higher*")
bdh_whitealone_newmexico <- tibble(
  Years = newmexico_data$Years,
  Percentage_women = newmexico_data$`...373`,
  Race = "White Alone"
)

# New York
newyork_data <- filter(acs_data, Label == "Bachelor's degree or higher*")
bdh_whitealone_newyork <- tibble(
  Years = newyork_data$Years,
  Percentage_women = newyork_data$`...385`,
  Race = "White Alone"
)

# North Carolina
northcarolina_data <- filter(acs_data, Label == "Bachelor's degree or higher*")
bdh_whitealone_northcarolina <- tibble(
  Years = northcarolina_data$Years,
  Percentage_women = northcarolina_data$`...397`,
  Race = "White Alone"
)

# North Dakota
northdakota_data <- filter(acs_data, Label == "Bachelor's degree or higher*")
bdh_whitealone_northdakota <- tibble(
  Years = northdakota_data$Years,
  Percentage_women = northdakota_data$`...409`,
  Race = "White Alone"
)

# Ohio
ohio_data <- filter(acs_data, Label == "Bachelor's degree or higher*")
bdh_whitealone_ohio <- tibble(
  Years = ohio_data$Years,
  Percentage_women = ohio_data$`...421`,
  Race = "White Alone"
)

# Oklahoma
oklahoma_data <- filter(acs_data, Label == "Bachelor's degree or higher*")
bdh_whitealone_oklahoma <- tibble(
  Years = oklahoma_data$Years,
  Percentage_women = oklahoma_data$`...433`,
  Race = "White Alone"
)

# Oregon
oregon_data <- filter(acs_data, Label == "Bachelor's degree or higher*")
bdh_whitealone_oregon <- tibble(
  Years = oregon_data$Years,
  Percentage_women = oregon_data$`...445`,
  Race = "White Alone"
)

# Pennsylvania
pennsylvania_data <- filter(acs_data, Label == "Bachelor's degree or higher*")
bdh_whitealone_pennsylvania <- tibble(
  Years = pennsylvania_data$Years,
  Percentage_women = pennsylvania_data$`...457`,
  Race = "White Alone"
)

# Rhode Island
rhodeisland_data <- filter(acs_data, Label == "Bachelor's degree or higher*")
bdh_whitealone_rhodeisland <- tibble(
  Years = rhodeisland_data$Years,
  Percentage_women = rhodeisland_data$`...469`,
  Race = "White Alone"
)

# South Carolina
southcarolina_data <- filter(acs_data, Label == "Bachelor's degree or higher*")
bdh_whitealone_southcarolina <- tibble(
  Years = southcarolina_data$Years,
  Percentage_women = southcarolina_data$`...481`,
  Race = "White Alone"
)

# South Dakota
southdakota_data <- filter(acs_data, Label == "Bachelor's degree or higher*")
bdh_whitealone_southdakota <- tibble(
  Years = southdakota_data$Years,
  Percentage_women = southdakota_data$`...493`,
  Race = "White Alone"
)

# Tennessee
tennessee_data <- filter(acs_data, Label == "Bachelor's degree or higher*")
bdh_whitealone_tennessee <- tibble(
  Years = tennessee_data$Years,
  Percentage_women = tennessee_data$`...505`,
  Race = "White Alone"
)

# Texas
texas_data <- filter(acs_data, Label == "Bachelor's degree or higher*")
bdh_whitealone_texas <- tibble(
  Years = texas_data$Years,
  Percentage_women = texas_data$`...517`,
  Race = "White Alone"
)

# Utah
utah_data <- filter(acs_data, Label == "Bachelor's degree or higher*")
bdh_whitealone_utah <- tibble(
  Years = utah_data$Years,
  Percentage_women = utah_data$`...529`,
  Race = "White Alone"
)

# Vermont
vermont_data <- filter(acs_data, Label == "Bachelor's degree or higher*")
bdh_whitealone_vermont <- tibble(
  Years = vermont_data$Years,
  Percentage_women = vermont_data$`...541`,
  Race = "White Alone"
)

# Virginia
virginia_data <- filter(acs_data, Label == "Bachelor's degree or higher*")
bdh_whitealone_virginia <- tibble(
  Years = virginia_data$Years,
  Percentage_women = virginia_data$`...553`,
  Race = "White Alone"
)

# Washington
washington_data <- filter(acs_data, Label == "Bachelor's degree or higher*")
bdh_whitealone_washington <- tibble(
  Years = washington_data$Years,
  Percentage_women = washington_data$`...565`,
  Race = "White Alone"
)

# West Virginia
westvirginia_data <- filter(acs_data, Label == "Bachelor's degree or higher*")
bdh_whitealone_westvirginia <- tibble(
  Years = westvirginia_data$Years,
  Percentage_women = westvirginia_data$`...577`,
  Race = "White Alone"
)

# Wisconsin
wisconsin_data <- filter(acs_data, Label == "Bachelor's degree or higher*")
bdh_whitealone_wisconsin <- tibble(
  Years = wisconsin_data$Years,
  Percentage_women = wisconsin_data$`...589`,
 

 Race = "White Alone"
)

# Wyoming
wyoming_data <- filter(acs_data, Label == "Bachelor's degree or higher*")
bdh_whitealone_wyoming <- tibble(
  Years = wyoming_data$Years,
  Percentage_women = wyoming_data$`...601`,
  Race = "White Alone"
)

# Puerto Rico
puertorico_data <- filter(acs_data, Label == "Bachelor's degree or higher*")
bdh_whitealone_puertorico <- tibble(
  Years = puertorico_data$Years,
  Percentage_women = puertorico_data$`...601`,
  Race = "White Alone"
)

# Combine all tibbles into one
combined_data_femalewhitealone <- bind_rows(
  bdh_whitealone_alabama,
  bdh_whitealone_alaska,
  bdh_whitealone_arizona,
  bdh_whitealone_arkansas,
  bdh_whitealone_california,
  bdh_whitealone_colorado,
  bdh_whitealone_connecticut,
  bdh_whitealone_delaware,
  bdh_whitealone_florida,
  bdh_whitealone_georgia,
  bdh_whitealone_hawaii,
  bdh_whitealone_idaho,
  bdh_whitealone_illinois,
  bdh_whitealone_indiana,
  bdh_whitealone_iowa,
  bdh_whitealone_kansas,
  bdh_whitealone_kentucky,
  bdh_whitealone_louisiana,
  bdh_whitealone_maine,
  bdh_whitealone_maryland,
  bdh_whitealone_massachusetts,
  bdh_whitealone_michigan,
  bdh_whitealone_minnesota,
  bdh_whitealone_mississippi,
  bdh_whitealone_missouri,
  bdh_whitealone_montana,
  bdh_whitealone_nebraska,
  bdh_whitealone_nevada,
  bdh_whitealone_newhampshire,
  bdh_whitealone_newjersey,
  bdh_whitealone_newmexico,
  bdh_whitealone_newyork,
  bdh_whitealone_northcarolina,
  bdh_whitealone_northdakota,
  bdh_whitealone_ohio,
  bdh_whitealone_oklahoma,
  bdh_whitealone_oregon,
  bdh_whitealone_pennsylvania,
  bdh_whitealone_rhodeisland,
  bdh_whitealone_southcarolina,
  bdh_whitealone_southdakota,
  bdh_whitealone_tennessee,
  bdh_whitealone_texas,
  bdh_whitealone_utah,
  bdh_whitealone_vermont,
  bdh_whitealone_virginia,
  bdh_whitealone_washington,
  bdh_whitealone_westvirginia,
  bdh_whitealone_wisconsin,
  bdh_whitealone_wyoming,
  bdh_whitealone_puertorico
)

print(combined_data_femalewhitealone)

```

Female, Black-alone, Across all U.S. States + Puerto Rico (Status: Cleaned)

```{r}

library(readxl)
library(dplyr)
library(tibble)

acs_data <- read_excel("dataset/acsfinale.xlsx")

# Alabama
alabama_data <- filter(acs_data, Label == "Bachelor's degree or higher***")
bdh_blackalone_alabama <- tibble(
  Years = alabama_data$Years,
  Percentage_black_women = alabama_data$`Alabama...13`,
  Race = "Black Alone"
)

# Alaska
alaska_data_black <- filter(acs_data, Label == "Bachelor's degree or higher***")
bdh_blackalone_alaska <- tibble(
  Years = alaska_data_black$Years,
  Percentage_black_women = alaska_data_black$`...25`,
  Race = "Black Alone"
)

# Arizona
arizona_data <- filter(acs_data, Label == "Bachelor's degree or higher***")
bdh_blackalone_arizona <- tibble(
  Years = arizona_data$Years,
  Percentage_black_women = arizona_data$`...37`,
  Race = "Black Alone"
)

# Arkansas
arkansas_data <- filter(acs_data, Label == "Bachelor's degree or higher***")
bdh_blackalone_arkansas <- tibble(
  Years = arkansas_data$Years,
  Percentage_black_women = arkansas_data$`...49`,
  Race = "Black Alone"
)

# California
california_data <- filter(acs_data, Label == "Bachelor's degree or higher***")
bdh_blackalone_california <- tibble(
  Years = california_data$Years,
  Percentage_black_women = california_data$`...61`,
  Race = "Black Alone"
)

# Colorado
colorado_data <- filter(acs_data, Label == "Bachelor's degree or higher***")
bdh_blackalone_colorado <- tibble(
  Years = colorado_data$Years,
  Percentage_black_women = colorado_data$`...73`,
  Race = "Black Alone"
)

# Connecticut
connecticut_data <- filter(acs_data, Label == "Bachelor's degree or higher***")
bdh_blackalone_connecticut <- tibble(
  Years = connecticut_data$Years,
  Percentage_black_women = connecticut_data$`...85`,
  Race = "Black Alone"
)

# Delaware
delaware_data <- filter(acs_data, Label == "Bachelor's degree or higher***")
bdh_blackalone_delaware <- tibble(
  Years = delaware_data$Years,
  Percentage_black_women = delaware_data$`...97`,
  Race = "Black Alone"
)

# Florida
florida_data <- filter(acs_data, Label == "Bachelor's degree or higher***")
bdh_blackalone_florida <- tibble(
  Years = florida_data$Years,
  Percentage_black_women = florida_data$`...109`,
  Race = "Black Alone"
)

# Georgia
georgia_data <- filter(acs_data, Label == "Bachelor's degree or higher***")
bdh_blackalone_georgia <- tibble(
  Years = georgia_data$Years,
  Percentage_black_women = georgia_data$`...121`,
  Race = "Black Alone"
)

# Hawaii
hawaii_data <- filter(acs_data, Label == "Bachelor's degree or higher***")
bdh_blackalone_hawaii <- tibble(
  Years = hawaii_data$Years,
  Percentage_black_women = hawaii_data$`...133`,
  Race = "Black Alone"
)

# Idaho
idaho_data <- filter(acs_data, Label == "Bachelor's degree or higher***")
bdh_blackalone_idaho <- tibble(
  Years = idaho_data$Years,
  Percentage_black_women = idaho_data$`...145`,
  Race = "Black Alone"
)

# Illinois
illinois_data <- filter(acs_data, Label == "Bachelor's degree or higher***")
bdh_blackalone_illinois <- tibble(
  Years = illinois_data$Years,
  Percentage_black_women = illinois_data$`...157`,
  Race = "Black Alone"
)

# Indiana
indiana_data <- filter(acs_data, Label == "Bachelor's degree or higher***")
bdh_blackalone_indiana <- tibble(
  Years = indiana_data$Years,
  Percentage_black_women = indiana_data$`...169`,
  Race = "Black Alone"
)

# Iowa
iowa_data <- filter(acs_data, Label == "Bachelor's degree or higher***")
bdh_blackalone_iowa <- tibble(
  Years = iowa_data$Years,
  Percentage_black_women = iowa_data$`...181`,
  Race = "Black Alone"
)

# Kansas
kansas_data <- filter(acs_data, Label == "Bachelor's degree or higher***")
bdh_blackalone_kansas <- tibble(
  Years = kansas_data$Years,
  Percentage_black_women = kansas_data$`...193`,
  Race = "Black Alone"
)

# Kentucky
kentucky_data <- filter(acs_data, Label == "Bachelor's degree or higher***")
bdh_blackalone_kentucky <- tibble(
  Years = kentucky_data$Years,
  Percentage_black_women = kentucky_data$`...205`,
  Race = "Black Alone"
)

# Louisiana
louisiana_data <- filter(acs_data, Label == "Bachelor's degree or higher***")
bdh_blackalone_louisiana <- tibble(
  Years = louisiana_data$Years,
  Percentage_black_women = louisiana_data$`...217`,
  Race = "Black Alone"
)

# Maine
maine_data <- filter(acs_data, Label == "Bachelor's degree or higher***")
bdh_blackalone_maine <- tibble(
  Years = maine_data$Years,
  Percentage_black_women = maine_data$`...229`,
  Race = "Black Alone"
)

# Maryland
maryland_data <- filter(acs_data, Label == "Bachelor's degree or higher***")
bdh_blackalone_maryland <- tibble(
  Years = maryland_data$Years,
  Percentage_black_women = maryland_data$`...241`,
  Race = "Black Alone"
)

# Massachusetts
massachusetts_data <- filter(acs_data, Label == "Bachelor's degree or higher***")
bdh_blackalone_massachusetts <- tibble(
  Years = massachusetts_data$Years,
  Percentage_black_women = massachusetts_data$`...253`,
  Race = "Black Alone"
)

# Michigan
michigan_data <- filter(acs_data, Label == "Bachelor's degree or higher***")
bdh_blackalone_michigan <- tibble(
  Years = michigan_data$Years,
  Percentage_black_women = michigan_data$`...265`,
  Race = "Black Alone"
)

# Minnesota
minnesota_data <- filter(acs_data, Label == "Bachelor's degree or higher***")
bdh_blackalone_minnesota <- tibble(
  Years = minnesota_data$Years,
  Percentage_black_women = minnesota_data$`...277`,
  Race = "Black Alone"
)

# Mississippi
mississippi_data <- filter(acs_data, Label == "Bachelor's degree or higher***")
bdh_blackalone_mississippi <- tibble(
  Years = mississippi_data$Years,
  Percentage_black_women = mississippi_data$`...289`,
  Race = "Black Alone"
)

# Missouri
missouri_data <- filter(acs_data, Label == "Bachelor's degree or higher***")
bdh_blackalone_missouri <- tibble(
  Years = missouri_data$Years,
  Percentage_black_women = missouri_data$`...301`,
  Race = "Black Alone"
)

# Montana
montana_data <- filter(acs_data, Label == "Bachelor's degree or higher***")
bdh_blackalone_montana <- tibble(
  Years = montana_data$Years,
  Percentage_black_women = montana_data$`...313`,
  Race = "Black Alone"
)

# Nebraska
nebraska_data <- filter(acs_data, Label == "Bachelor's degree or higher***")
bdh_blackalone_nebraska <- tibble(
  Years = nebraska_data$Years,
  Percentage_black_women = nebraska_data$`...325`,
  Race = "Black Alone"
)

# Nevada
nevada_data <- filter(acs_data, Label == "Bachelor's degree or higher***")
bdh_blackalone_nevada <- tibble(
  Years = nevada_data$Years,
  Percentage_black_women = nevada_data$`...337`,
  Race = "Black Alone"
)

# New Hampshire
newhampshire_data <- filter(acs_data, Label == "Bachelor's degree or higher***")
bdh_blackalone_newhampshire <- tibble(
  Years = newhampshire_data$Years,
  Percentage_black_women = newhampshire_data$`...349`,
  Race = "Black Alone"
)

# New Jersey
newjersey_data <- filter(acs_data, Label == "Bachelor's degree or higher***")
bdh_blackalone_newjersey <- tibble(
  Years = newjersey_data$Years,
  Percentage_black_women = newjersey_data$`...361`,
  Race = "Black Alone"
)

# New Mexico
newmexico_data <- filter(acs_data, Label == "Bachelor's degree or higher***")
bdh_blackalone_newmexico <- tibble(
  Years = newmexico_data$Years,
  Percentage_black_women = newmexico_data$`...373`,
  Race = "Black Alone"
)

# New York
newyork_data <- filter(acs_data, Label == "Bachelor's degree or higher***")
bdh_blackalone_newyork <- tibble(
  Years = newyork_data$Years,
  Percentage_black_women = newyork_data$`...385`,
  Race = "Black Alone"
)

# North Carolina
northcarolina_data <- filter(acs_data, Label == "Bachelor's degree or higher***")
bdh_blackalone_northcarolina <- tibble(
  Years = northcarolina_data$Years,
  Percentage_black_women = northcarolina_data$`...397`,
  Race = "Black Alone"
)

# North Dakota
northdakota_data <- filter(acs_data, Label == "Bachelor's degree or higher***")
bdh_blackalone_northdakota <- tibble(
  Years = northdakota_data$Years,
  Percentage_black_women = northdakota_data$`...409`,
  Race = "Black Alone"
)

# Ohio
ohio_data <- filter(acs_data, Label == "Bachelor's degree or higher***")
bdh_blackalone_ohio <- tibble(
  Years = ohio_data$Years,
  Percentage_black_women = ohio_data$`...421`,
  Race = "Black Alone"
)

# Oklahoma
oklahoma_data <- filter(acs_data, Label == "Bachelor's degree or higher***")
bdh_blackalone_oklahoma <- tibble(
  Years = oklahoma_data$Years,
  Percentage_black_women = oklahoma_data$`...433`,
  Race = "Black Alone"
)

# Oregon
oregon_data <- filter(acs_data, Label == "Bachelor's degree or higher***")
bdh_blackalone_oregon <- tibble(
  Years = oregon_data$Years,
  Percentage_black_women = oregon_data$`...445`,
  Race = "Black Alone"
)

# Pennsylvania
pennsylvania_data <- filter(acs_data, Label == "Bachelor's degree or higher***")
bdh_blackalone_pennsylvania <- tibble(
  Years = pennsylvania_data$Years,
  Percentage_black_women = pennsylvania_data$`...457`,
  Race = "Black Alone"
)

# Rhode Island
rhodeisland_data <- filter(acs_data, Label == "Bachelor's degree or higher***")
bdh_blackalone_rhodeisland <- tibble(
  Years = rhodeisland_data$Years,
  Percentage_black_women = rhodeisland_data$`...469`,
  Race = "Black Alone"
)

# South Carolina
southcarolina_data <- filter(acs_data, Label == "Bachelor's degree or higher***")
bdh_blackalone_southcarolina <- tibble(
  Years = southcarolina_data$Years,
  Percentage_black_women = southcarolina_data$`...481`,
  Race = "Black Alone"
)

# South Dakota
southdakota_data <- filter(acs_data, Label == "Bachelor's degree or higher***")
bdh_blackalone_southdakota <- tibble(
  Years = southdakota_data$Years,
  Percentage_black_women = southdakota_data$`...493`,
  Race = "Black Alone"
)

# Tennessee
tennessee_data <- filter(acs_data, Label == "Bachelor's degree or higher***")
bdh_blackalone_tennessee <- tibble(
  Years = tennessee_data$Years,
  Percentage_black_women = tennessee_data$`...505`,
  Race = "Black Alone"
)

# Texas
texas_data <- filter(acs_data, Label == "Bachelor's degree or higher***")
bdh_blackalone_texas <- tibble(
  Years = texas_data$Years,
  Percentage_black_women = texas_data$`...517`,
  Race = "Black Alone"
)

# Utah
utah_data <- filter(acs_data, Label == "Bachelor's degree or higher***")
bdh_blackalone_utah <- tibble(
  Years = utah_data$Years,
  Percentage_black_women = utah_data$`...529`,
  Race = "Black Alone"
)

# Vermont
vermont_data <- filter(acs_data, Label == "Bachelor's degree or higher***")
bdh_blackalone_vermont <- tibble(
  Years = vermont_data$Years,
  Percentage_black_women = vermont_data$`...541`,
  Race = "Black Alone"
)

# Virginia
virginia_data <- filter(acs_data, Label == "Bachelor's degree or higher***")
bdh_blackalone_virginia <- tibble(
  Years = virginia_data$Years,
  Percentage_black_women = virginia_data$`...553`,
  Race = "Black Alone"
)

# Washington
washington_data <- filter(acs_data, Label == "Bachelor's degree or higher***")
bdh_blackalone_washington <- tibble(
  Years = washington_data$Years,
  Percentage_black_women = washington_data$`...565`,
  Race = "Black Alone"
)

# West Virginia
westvirginia_data <- filter(acs_data, Label == "Bachelor's degree or higher***")
bdh_blackalone_westvirginia <- tibble(
  Years = westvirginia_data$Years,
  Percentage_black_women = westvirginia_data$`...577`,
  Race = "Black Alone"
)

# Wisconsin
wisconsin_data <- filter(acs_data, Label == "Bachelor's degree or higher***")
bdh_blackalone_wisconsin <- tibble(
  Years = wisconsin_data$Years,
  Percentage_black_women = wisconsin_data$`...589`,
  Race = "Black Alone"
)

# Wyoming
wyoming_data <- filter(acs_data, Label == "Bachelor's degree or higher***")
bdh_blackalone_wyoming <- tibble(
  Years = wyoming_data$Years,
  Percentage_black_women = wyoming_data$`...601`,
  Race = "Black Alone"
)

# Puerto Rico
puertorico_data <- filter(acs_data, Label == "Bachelor's degree or higher***")
bdh_blackalone_puertorico <- tibble(
  Years = puertorico_data$Years,
  Percentage_black_women = puertorico_data$`...613`,
  Race = "Black Alone"
)

combined_data_blackalone <- bind_rows(
  bdh_blackalone_alabama,
  bdh_blackalone_alaska,
  bdh_blackalone_arizona,
  bdh_blackalone_arkansas,
  bdh_blackalone_california,
  bdh_blackalone_colorado,
  bdh_blackalone_connecticut,
  bdh_blackalone_delaware,
  bdh_blackalone_florida,
  bdh_blackalone_georgia,
  bdh_blackalone_hawaii,
  bdh_blackalone_idaho,
  bdh_blackalone_illinois,
  bdh_blackalone_indiana,
  bdh_blackalone_iowa,
  bdh_blackalone_kansas,
  bdh_blackalone_kentucky,
  bdh_blackalone_louisiana,
  bdh_blackalone_maine,
  bdh_blackalone_maryland,
  bdh_blackalone_massachusetts,
  bdh_blackalone_michigan,
  bdh_blackalone_minnesota,
  bdh_blackalone_mississippi,
  bdh_blackalone_missouri,
  bdh_blackalone_montana,
  bdh_blackalone_nebraska,
  bdh_blackalone_nevada,
  bdh_blackalone_newhampshire,
  bdh_blackalone_newjersey,
  bdh_blackalone_newmexico,
  bdh_blackalone_newyork,
  bdh_blackalone_northcarolina,
  bdh_blackalone_northdakota,
  bdh_blackalone_ohio,
  bdh_blackalone_oklahoma,
  bdh_blackalone_oregon,
  bdh_blackalone_pennsylvania,
  bdh_blackalone_rhodeisland,
  bdh_blackalone_southcarolina,
  bdh_blackalone_southdakota,
  bdh_blackalone_tennessee,
  bdh_blackalone_texas,
  bdh_blackalone_utah,
  bdh_blackalone_vermont,
  bdh_blackalone_virginia,
  bdh_blackalone_washington,
  bdh_blackalone_westvirginia,
  bdh_blackalone_wisconsin,
  bdh_blackalone_wyoming,
  bdh_blackalone_puertorico
)

print(combined_data_blackalone)


```

Female, American Indian or Alaska Native Alone, Across all U.S. States + Puerto Rico (Status: Not yet cleaned)

```         
```

Female, Native Hawaiian and Other Pacific Islander Alone, Across all U.S. States + Puerto Rico (Status: Not yet cleaned)

```         
```

Female, Hispanic or Latino Origin Alone, Across all U.S. States + Puerto Rico (Status: Not yet cleaned)

```         
```

Comments:
