---
title: "Female Data Cleaning"
editor: visual
---

Guys, please read the analysis approach before continuing.

```{r}
# Analysis Approach:
# Dependent Variables:
# Percentage of Bachelor’s degrees earned by women of different racial backgrounds (White, Black, Asian, etc.)
# Independent Variable:
# Year

# Data Granularity:
# State-level data
# Segmented by female race. There are 9 classifications, listed below:
  # 'White Alone'
  # 'White Alone, not Hispanic or Latino'
  # 'Black Alone'
  # 'American Indian or Alaska Native Alone'
  # 'Asian Alone' 
  # 'Native Hawaiian and Other Pacific Islander Alone' 
  # 'Some other race alone'
  # 'Two or more races' 
  # 'Hispanic or Latino Origin'

# Hypothesis:
# The percentage of Bachelor's degrees earned by women of different racial backgrounds has changed over time, influenced by various factors. 

```

1.  **Female, White-alone, Across all U.S. States + Puerto Rico (Status: Cleaned)**

```{r}
## Separating data for Female, White-alone, Across all U.S. States + Puerto Rico (Status: Cleaned) 

library(readxl)
library(dplyr)
library(tibble)

acs_data <- read_excel("dataset/acsfinale.xlsx")

# Alabama
us_whitealone_data <- filter(acs_data, Label == "Bachelor's degree or higher*")
bdh_whitealone_alabama <- tibble(
  Years = us_whitealone_data$Years,
  Percentage_women = us_whitealone_data$`Alabama...13`,
  Race = "White Alone"
)

# Alaska

bdh_whitealone_alaska <- tibble(
  Years = us_whitealone_data$Years,
  Percentage_women = us_whitealone_data$`...25`,
  Race = "White Alone"
)


# Arizona

bdh_whitealone_arizona <- tibble(
  Years = us_whitealone_data$Years,
  Percentage_women = us_whitealone_data$`...37`,
  Race = "White Alone"
)

# Arkansas

bdh_whitealone_arkansas <- tibble(
  Years = us_whitealone_data$Years,
  Percentage_women = us_whitealone_data$`...49`,
  Race = "White Alone"
)

# California

bdh_whitealone_california <- tibble(
  Years = us_whitealone_data$Years,
  Percentage_women = us_whitealone_data$`...61`,
  Race = "White Alone"
)

# Colorado

bdh_whitealone_colorado <- tibble(
  Years = us_whitealone_data$Years,
  Percentage_women = us_whitealone_data$`...73`,
  Race = "White Alone"
)

# Connecticut
connecticut_data <- filter(acs_data, Label == "Bachelor's degree or higher*")
bdh_whitealone_connecticut <- tibble(
  Years = connecticut_data$Years,
  Percentage_women = us_whitealone_data$`...85`,
  Race = "White Alone"
)

# Delaware

bdh_whitealone_delaware <- tibble(
  Years = us_whitealone_data$Years,
  Percentage_women = us_whitealone_data$`...97`,
  Race = "White Alone"
)

# Florida
florida_data <- filter(acs_data, Label == "Bachelor's degree or higher*")
bdh_whitealone_florida <- tibble(
  Years = florida_data$Years,
  Percentage_women = us_whitealone_data$`...109`,
  Race = "White Alone"
)

# Georgia
georgia_data <- filter(acs_data, Label == "Bachelor's degree or higher*")
bdh_whitealone_georgia <- tibble(
  Years = georgia_data$Years,
  Percentage_women = us_whitealone_data$`...121`,
  Race = "White Alone"
)

# Hawaii
hawaii_data <- filter(acs_data, Label == "Bachelor's degree or higher*")
bdh_whitealone_hawaii <- tibble(
  Years = hawaii_data$Years,
  Percentage_women = us_whitealone_data$`...133`,
  Race = "White Alone"
)

# Idaho
idaho_data <- filter(acs_data, Label == "Bachelor's degree or higher*")
bdh_whitealone_idaho <- tibble(
  Years = idaho_data$Years,
  Percentage_women = us_whitealone_data$`...145`,
  Race = "White Alone"
)

# Illinois
illinois_data <- filter(acs_data, Label == "Bachelor's degree or higher*")
bdh_whitealone_illinois <- tibble(
  Years = illinois_data$Years,
  Percentage_women = us_whitealone_data$`...157`,
  Race = "White Alone"
)

# Indiana
indiana_data <- filter(acs_data, Label == "Bachelor's degree or higher*")
bdh_whitealone_indiana <- tibble(
  Years = indiana_data$Years,
  Percentage_women = us_whitealone_data$`...169`,
  Race = "White Alone"
)

# Iowa
iowa_data <- filter(acs_data, Label == "Bachelor's degree or higher*")
bdh_whitealone_iowa <- tibble(
  Years = iowa_data$Years,
  Percentage_women = us_whitealone_data$`...181`,
  Race = "White Alone"
)

# Kansas
kansas_data <- filter(acs_data, Label == "Bachelor's degree or higher*")
bdh_whitealone_kansas <- tibble(
  Years = kansas_data$Years,
  Percentage_women = us_whitealone_data$`...193`,
  Race = "White Alone"
)

# Kentucky
kentucky_data <- filter(acs_data, Label == "Bachelor's degree or higher*")
bdh_whitealone_kentucky <- tibble(
  Years = kentucky_data$Years,
  Percentage_women = us_whitealone_data$`...205`,
  Race = "White Alone"
)

# Louisiana
louisiana_data <- filter(acs_data, Label == "Bachelor's degree or higher*")
bdh_whitealone_louisiana <- tibble(
  Years = louisiana_data$Years,
  Percentage_women = us_whitealone_data$`...217`,
  Race = "White Alone"
)

# Maine
maine_data <- filter(acs_data, Label == "Bachelor's degree or higher*")
bdh_whitealone_maine <- tibble(
  Years = maine_data$Years,
  Percentage_women = us_whitealone_data$`...229`,
  Race = "White Alone"
)

# Maryland
maryland_data <- filter(acs_data, Label == "Bachelor's degree or higher*")
bdh_whitealone_maryland <- tibble(
  Years = maryland_data$Years,
  Percentage_women = us_whitealone_data$`...241`,
  Race = "White Alone"
)

# Massachusetts
massachusetts_data <- filter(acs_data, Label == "Bachelor's degree or higher*")
bdh_whitealone_massachusetts <- tibble(
  Years = massachusetts_data$Years,
  Percentage_women = us_whitealone_data$`...253`,
  Race = "White Alone"
)

# Michigan
michigan_data <- filter(acs_data, Label == "Bachelor's degree or higher*")
bdh_whitealone_michigan <- tibble(
  Years = michigan_data$Years,
  Percentage_women = us_whitealone_data$`...265`,
  Race = "White Alone"
)

# Minnesota
minnesota_data <- filter(acs_data, Label == "Bachelor's degree or higher*")
bdh_whitealone_minnesota <- tibble(
  Years = minnesota_data$Years,
  Percentage_women = us_whitealone_data$`...277`,
  Race = "White Alone"
)

# Mississippi
mississippi_data <- filter(acs_data, Label == "Bachelor's degree or higher*")
bdh_whitealone_mississippi <- tibble(
  Years = mississippi_data$Years,
  Percentage_women = us_whitealone_data$`...289`,
  Race = "White Alone"
)

# Missouri
missouri_data <- filter(acs_data, Label == "Bachelor's degree or higher*")
bdh_whitealone_missouri <- tibble(
  Years = missouri_data$Years,
  Percentage_women = us_whitealone_data$`...301`,
  Race = "White Alone"
)

# Montana
montana_data <- filter(acs_data, Label == "Bachelor's degree or higher*")
bdh_whitealone_montana <- tibble(
  Years = montana_data$Years,
  Percentage_women = us_whitealone_data$`...313`,
  Race = "White Alone"
)

# Nebraska
nebraska_data <- filter(acs_data, Label == "Bachelor's degree or higher*")
bdh_whitealone_nebraska <- tibble(
  Years = nebraska_data$Years,
  Percentage_women = us_whitealone_data$`...325`,
  Race = "White Alone"
)

# Nevada
nevada_data <- filter(acs_data, Label == "Bachelor's degree or higher*")
bdh_whitealone_nevada <- tibble(
  Years = nevada_data$Years,
  Percentage_women = us_whitealone_data$`...337`,
  Race = "White Alone"
)

# New Hampshire
newhampshire_data <- filter(acs_data, Label == "Bachelor's degree or higher*")
bdh_whitealone_newhampshire <- tibble(
  Years = newhampshire_data$Years,
  Percentage_women = us_whitealone_data$`...349`,
  Race = "White Alone"
)

# New Jersey
newjersey_data <- filter(acs_data, Label == "Bachelor's degree or higher*")
bdh_whitealone_newjersey <- tibble(
  Years = newjersey_data$Years,
  Percentage_women = newjersey_data$`...361`,
  Race = "White Alone"
)

# New Mexico
newmexico_data <- filter(acs_data, Label == "Bachelor's degree or higher*")
bdh_whitealone_newmexico <- tibble(
  Years = newmexico_data$Years,
  Percentage_women = newmexico_data$`...373`,
  Race = "White Alone"
)

# New York
newyork_data <- filter(acs_data, Label == "Bachelor's degree or higher*")
bdh_whitealone_newyork <- tibble(
  Years = newyork_data$Years,
  Percentage_women = newyork_data$`...385`,
  Race = "White Alone"
)

# North Carolina
northcarolina_data <- filter(acs_data, Label == "Bachelor's degree or higher*")
bdh_whitealone_northcarolina <- tibble(
  Years = northcarolina_data$Years,
  Percentage_women = northcarolina_data$`...397`,
  Race = "White Alone"
)

# North Dakota
northdakota_data <- filter(acs_data, Label == "Bachelor's degree or higher*")
bdh_whitealone_northdakota <- tibble(
  Years = northdakota_data$Years,
  Percentage_women = northdakota_data$`...409`,
  Race = "White Alone"
)

# Ohio
ohio_data <- filter(acs_data, Label == "Bachelor's degree or higher*")
bdh_whitealone_ohio <- tibble(
  Years = ohio_data$Years,
  Percentage_women = ohio_data$`...421`,
  Race = "White Alone"
)

# Oklahoma
oklahoma_data <- filter(acs_data, Label == "Bachelor's degree or higher*")
bdh_whitealone_oklahoma <- tibble(
  Years = oklahoma_data$Years,
  Percentage_women = oklahoma_data$`...433`,
  Race = "White Alone"
)

# Oregon
oregon_data <- filter(acs_data, Label == "Bachelor's degree or higher*")
bdh_whitealone_oregon <- tibble(
  Years = oregon_data$Years,
  Percentage_women = oregon_data$`...445`,
  Race = "White Alone"
)

# Pennsylvania
pennsylvania_data <- filter(acs_data, Label == "Bachelor's degree or higher*")
bdh_whitealone_pennsylvania <- tibble(
  Years = pennsylvania_data$Years,
  Percentage_women = pennsylvania_data$`...457`,
  Race = "White Alone"
)

# Rhode Island
rhodeisland_data <- filter(acs_data, Label == "Bachelor's degree or higher*")
bdh_whitealone_rhodeisland <- tibble(
  Years = rhodeisland_data$Years,
  Percentage_women = rhodeisland_data$`...469`,
  Race = "White Alone"
)

# South Carolina
southcarolina_data <- filter(acs_data, Label == "Bachelor's degree or higher*")
bdh_whitealone_southcarolina <- tibble(
  Years = southcarolina_data$Years,
  Percentage_women = southcarolina_data$`...481`,
  Race = "White Alone"
)

# South Dakota
southdakota_data <- filter(acs_data, Label == "Bachelor's degree or higher*")
bdh_whitealone_southdakota <- tibble(
  Years = southdakota_data$Years,
  Percentage_women = southdakota_data$`...493`,
  Race = "White Alone"
)

# Tennessee
tennessee_data <- filter(acs_data, Label == "Bachelor's degree or higher*")
bdh_whitealone_tennessee <- tibble(
  Years = tennessee_data$Years,
  Percentage_women = tennessee_data$`...505`,
  Race = "White Alone"
)

# Texas
texas_data <- filter(acs_data, Label == "Bachelor's degree or higher*")
bdh_whitealone_texas <- tibble(
  Years = texas_data$Years,
  Percentage_women = texas_data$`...517`,
  Race = "White Alone"
)

# Utah
utah_data <- filter(acs_data, Label == "Bachelor's degree or higher*")
bdh_whitealone_utah <- tibble(
  Years = utah_data$Years,
  Percentage_women = utah_data$`...529`,
  Race = "White Alone"
)

# Vermont
vermont_data <- filter(acs_data, Label == "Bachelor's degree or higher*")
bdh_whitealone_vermont <- tibble(
  Years = vermont_data$Years,
  Percentage_women = vermont_data$`...541`,
  Race = "White Alone"
)

# Virginia
virginia_data <- filter(acs_data, Label == "Bachelor's degree or higher*")
bdh_whitealone_virginia <- tibble(
  Years = virginia_data$Years,
  Percentage_women = virginia_data$`...553`,
  Race = "White Alone"
)

# Washington
washington_data <- filter(acs_data, Label == "Bachelor's degree or higher*")
bdh_whitealone_washington <- tibble(
  Years = washington_data$Years,
  Percentage_women = washington_data$`...565`,
  Race = "White Alone"
)

# West Virginia
westvirginia_data <- filter(acs_data, Label == "Bachelor's degree or higher*")
bdh_whitealone_westvirginia <- tibble(
  Years = westvirginia_data$Years,
  Percentage_women = westvirginia_data$`...577`,
  Race = "White Alone"
)

# Wisconsin
wisconsin_data <- filter(acs_data, Label == "Bachelor's degree or higher*")
bdh_whitealone_wisconsin <- tibble(
  Years = wisconsin_data$Years,
  Percentage_women = wisconsin_data$`...589`,
 

 Race = "White Alone"
)

# Wyoming
wyoming_data <- filter(acs_data, Label == "Bachelor's degree or higher*")
bdh_whitealone_wyoming <- tibble(
  Years = wyoming_data$Years,
  Percentage_women = wyoming_data$`...601`,
  Race = "White Alone"
)

# Puerto Rico
puertorico_data <- filter(acs_data, Label == "Bachelor's degree or higher*")
bdh_whitealone_puertorico <- tibble(
  Years = puertorico_data$Years,
  Percentage_women = puertorico_data$`...601`,
  Race = "White Alone"
)

# Combine all tibbles into one
combined_data_femalewhitealone <- bind_rows(
  bdh_whitealone_alabama,
  bdh_whitealone_alaska,
  bdh_whitealone_arizona,
  bdh_whitealone_arkansas,
  bdh_whitealone_california,
  bdh_whitealone_colorado,
  bdh_whitealone_connecticut,
  bdh_whitealone_delaware,
  bdh_whitealone_florida,
  bdh_whitealone_georgia,
  bdh_whitealone_hawaii,
  bdh_whitealone_idaho,
  bdh_whitealone_illinois,
  bdh_whitealone_indiana,
  bdh_whitealone_iowa,
  bdh_whitealone_kansas,
  bdh_whitealone_kentucky,
  bdh_whitealone_louisiana,
  bdh_whitealone_maine,
  bdh_whitealone_maryland,
  bdh_whitealone_massachusetts,
  bdh_whitealone_michigan,
  bdh_whitealone_minnesota,
  bdh_whitealone_mississippi,
  bdh_whitealone_missouri,
  bdh_whitealone_montana,
  bdh_whitealone_nebraska,
  bdh_whitealone_nevada,
  bdh_whitealone_newhampshire,
  bdh_whitealone_newjersey,
  bdh_whitealone_newmexico,
  bdh_whitealone_newyork,
  bdh_whitealone_northcarolina,
  bdh_whitealone_northdakota,
  bdh_whitealone_ohio,
  bdh_whitealone_oklahoma,
  bdh_whitealone_oregon,
  bdh_whitealone_pennsylvania,
  bdh_whitealone_rhodeisland,
  bdh_whitealone_southcarolina,
  bdh_whitealone_southdakota,
  bdh_whitealone_tennessee,
  bdh_whitealone_texas,
  bdh_whitealone_utah,
  bdh_whitealone_vermont,
  bdh_whitealone_virginia,
  bdh_whitealone_washington,
  bdh_whitealone_westvirginia,
  bdh_whitealone_wisconsin,
  bdh_whitealone_wyoming,
  bdh_whitealone_puertorico
)

print(combined_data_femalewhitealone)

```

2.  **Female, White-alone, not Hispanic or Latino, Across all U.S. States + Puerto Rico (Status: Cleaned)**

```{r}
library(tidyverse)
library(dplyr)
library(tibble)

acs_data <- read_excel("dataset/acsfinale.xlsx")

# Alabama
alabama_data <- filter(acs_data, Label == "Bachelor's degree or higher**")
bdh_wnhp_alabama <- tibble(
  Years = alabama_data$Years,
  Percentage_wnhp_women = alabama_data$`...13`,
  Race = "White alone, not Hispanic or Latino"
)

# Alaska
alaska_data <- filter(acs_data, Label == "Bachelor's degree or higher**")
bdh_wnhp_alaska <- tibble(
  Years = alaska_data$Years,
  Percentage_wnhp_women = alaska_data$`...25`,
  Race = "White alone, not Hispanic or Latino"
)

# Arizona
arizona_data <- filter(acs_data, Label == "Bachelor's degree or higher**")
bdh_wnhp_arizona <- tibble(
  Years = arizona_data$Years,
  Percentage_wnhp_women = arizona_data$`...37`,
  Race = "White alone, not Hispanic or Latino"
)

# Arkansas
arkansas_data <- filter(acs_data, Label == "Bachelor's degree or higher**")
bdh_wnhp_arkansas <- tibble(
  Years = arkansas_data$Years,
  Percentage_wnhp_women = arkansas_data$`...49`,
  Race = "White alone, not Hispanic or Latino"
)

# California
california_data <- filter(acs_data, Label == "Bachelor's degree or higher**")
bdh_wnhp_california <- tibble(
  Years = california_data$Years,
  Percentage_wnhp_women = california_data$`...57`,
  Race = "White alone, not Hispanic or Latino"
)

# Colorado
colorado_data <- filter(acs_data, Label == "Bachelor's degree or higher**")
bdh_wnhp_colorado <- tibble(
  Years = colorado_data$Years,
  Percentage_wnhp_women = colorado_data$`...69`,
  Race = "White alone, not Hispanic or Latino"
)

# Connecticut
connecticut_data <- filter(acs_data, Label == "Bachelor's degree or higher**")
bdh_wnhp_connecticut <- tibble(
  Years = connecticut_data$Years,
  Percentage_wnhp_women = connecticut_data$`...81`,
  Race = "White alone, not Hispanic or Latino"
)

# Delaware
delaware_data <- filter(acs_data, Label == "Bachelor's degree or higher**")
bdh_wnhp_delaware <- tibble(
  Years = delaware_data$Years,
  Percentage_wnhp_women = delaware_data$`...93`,
  Race = "White alone, not Hispanic or Latino"
)

# Florida
florida_data <- filter(acs_data, Label == "Bachelor's degree or higher**")
bdh_wnhp_florida <- tibble(
  Years = florida_data$Years,
  Percentage_wnhp_women = florida_data$`...105`,
  Race = "White alone, not Hispanic or Latino"
)

# Georgia
georgia_data <- filter(acs_data, Label == "Bachelor's degree or higher**")
bdh_wnhp_georgia <- tibble(
  Years = georgia_data$Years,
  Percentage_wnhp_women = georgia_data$`...117`,
  Race = "White alone, not Hispanic or Latino"
)

# Hawaii
hawaii_data <- filter(acs_data, Label == "Bachelor's degree or higher**")
bdh_wnhp_hawaii <- tibble(
  Years = hawaii_data$Years,
  Percentage_wnhp_women = hawaii_data$`...129`,
  Race = "White alone, not Hispanic or Latino"
)

# Idaho
idaho_data <- filter(acs_data, Label == "Bachelor's degree or higher**")
bdh_wnhp_idaho <- tibble(
  Years = idaho_data$Years,
  Percentage_wnhp_women = idaho_data$`...141`,
  Race = "White alone, not Hispanic or Latino"
)

# Illinois
illinois_data <- filter(acs_data, Label == "Bachelor's degree or higher**")
bdh_wnhp_illinois <- tibble(
  Years = illinois_data$Years,
  Percentage_wnhp_women = illinois_data$`...153`,
  Race = "White alone, not Hispanic or Latino"
)

# Indiana
indiana_data <- filter(acs_data, Label == "Bachelor's degree or higher**")
bdh_wnhp_indiana <- tibble(
  Years = indiana_data$Years,
  Percentage_wnhp_women = indiana_data$`...165`,
  Race = "White alone, not Hispanic or Latino"
)

# Iowa
iowa_data <- filter(acs_data, Label == "Bachelor's degree or higher**")
bdh_wnhp_iowa <- tibble(
  Years = iowa_data$Years,
  Percentage_wnhp_women = iowa_data$`...177`,
  Race = "White alone, not Hispanic or Latino"
)

# Kansas
kansas_data <- filter(acs_data, Label == "Bachelor's degree or higher**")
bdh_wnhp_kansas <- tibble(
  Years = kansas_data$Years,
  Percentage_wnhp_women = kansas_data$`...189`,
  Race = "White alone, not Hispanic or Latino"
)

# Kentucky
kentucky_data <- filter(acs_data, Label == "Bachelor's degree or higher**")
bdh_wnhp_kentucky <- tibble(
  Years = kentucky_data$Years,
  Percentage_wnhp_women = kentucky_data$`...201`,
  Race = "White alone, not Hispanic or Latino"
)

# Louisiana
louisiana_data <- filter(acs_data, Label == "Bachelor's degree or higher**")
bdh_wnhp_louisiana <- tibble(
  Years = louisiana_data$Years,
  Percentage_wnhp_women = louisiana_data$`...213`,
  Race = "White alone, not Hispanic or Latino"
)

# Maine
maine_data <- filter(acs_data, Label == "Bachelor's degree or higher**")
bdh_wnhp_maine <- tibble(
  Years = maine_data$Years,
  Percentage_wnhp_women = maine_data$`...225`,
  Race = "White alone, not Hispanic or Latino"
)

# Maryland
maryland_data <- filter(acs_data, Label == "Bachelor's degree or higher**")
bdh_wnhp_maryland <- tibble(
  Years = maryland_data$Years,
  Percentage_wnhp_women = maryland_data$`...237`,
  Race = "White alone, not Hispanic or Latino"
)

# Massachusetts
massachusetts_data <- filter(acs_data, Label == "Bachelor's degree or higher**")
bdh_wnhp_massachusetts <- tibble(
  Years = massachusetts_data$Years,
  Percentage_wnhp_women = massachusetts_data$`...249`,
  Race = "White alone, not Hispanic or Latino"
)

# Michigan
michigan_data <- filter(acs_data, Label == "Bachelor's degree or higher**")
bdh_wnhp_michigan <- tibble(
  Years = michigan_data$Years,
  Percentage_wnhp_women = michigan_data$`...261`,
  Race = "White alone, not Hispanic or Latino"
)

# Minnesota
minnesota_data <- filter(acs_data, Label == "Bachelor's degree or higher**")
bdh_wnhp_minnesota <- tibble(
  Years = minnesota_data$Years,
  Percentage_wnhp_women = minnesota_data$`...273`,
  Race = "White alone, not Hispanic or Latino"
)

# Mississippi
mississippi_data <- filter(acs_data, Label == "Bachelor's degree or higher**")
bdh_wnhp_mississippi <- tibble(
  Years = mississippi_data$Years,
  Percentage_wnhp_women = mississippi_data$`...285`,
  Race = "White alone, not Hispanic or Latino"
)

# Missouri
missouri_data <- filter(acs_data, Label == "Bachelor's degree or higher**")
bdh_wnhp_missouri <- tibble(
  Years = missouri_data$Years,
  Percentage_wnhp_women = missouri_data$`...297`,
  Race = "White alone, not Hispanic or Latino"
)

# Montana
montana_data <- filter(acs_data, Label == "Bachelor's degree or higher**")
bdh_wnhp_montana <- tibble(
  Years = montana_data$Years,
  Percentage_wnhp_women = montana_data$`...309`,
  Race = "White alone, not Hispanic or Latino"
)

# Nebraska
nebraska_data <- filter(acs_data, Label == "Bachelor's degree or higher**")
bdh_wnhp_nebraska <- tibble(
  Years = nebraska_data$Years,
  Percentage_wnhp_women = nebraska_data$`...321`,
  Race = "White alone, not Hispanic or Latino"
)

# Nevada
nevada_data <- filter(acs_data, Label == "Bachelor's degree or higher**")
bdh_wnhp_nevada <- tibble(
  Years = nevada_data$Years,
  Percentage_wnhp_women = nevada_data$`...333`,
  Race = "White alone, not Hispanic or Latino"
)

# New Hampshire
newhampshire_data <- filter(acs_data, Label == "Bachelor's degree or higher**")
bdh_wnhp_newhampshire <- tibble(
  Years = newhampshire_data$Years,
  Percentage_wnhp_women = newhampshire_data$`...345`,
  Race = "White alone, not Hispanic or Latino"
)

# New Jersey
newjersey_data <- filter(acs_data, Label == "Bachelor's degree or higher**")
bdh_wnhp_newjersey <- tibble(
  Years = newjersey_data$Years,
  Percentage_wnhp_women = newjersey_data$`...357`,
  Race = "White alone, not Hispanic or Latino"
)

# New Mexico
newmexico_data <- filter(acs_data, Label == "Bachelor's degree or higher**")
bdh_wnhp_newmexico <- tibble(
  Years = newmexico_data$Years,
  Percentage_wnhp_women = newmexico_data$`...369`,
  Race = "White alone, not Hispanic or Latino"
)

# New York
newyork_data <- filter(acs_data, Label == "Bachelor's degree or higher**")
bdh_wnhp_newyork <- tibble(
  Years = newyork_data$Years,
  Percentage_wnhp_women = newyork_data$`...381`,
  Race = "White alone, not Hispanic or Latino"
)

# North Carolina
northcarolina_data <- filter(acs_data, Label == "Bachelor's degree or higher**")
bdh_wnhp_northcarolina <- tibble(
  Years = northcarolina_data$Years,
  Percentage_wnhp_women = northcarolina_data$`...393`,
  Race = "White alone, not Hispanic or Latino"
)

# North Dakota
northdakota_data <- filter(acs_data, Label == "Bachelor's degree or higher**")
bdh_wnhp_northdakota <- tibble(
  Years = northdakota_data$Years,
  Percentage_wnhp_women = northdakota_data$`...405`,
  Race = "White alone, not Hispanic or Latino"
)

# Ohio
ohio_data <- filter(acs_data, Label == "Bachelor's degree or higher**")
bdh_wnhp_ohio <- tibble(
  Years = ohio_data$Years,
  Percentage_wnhp_women = ohio_data$`...417`,
  Race = "White alone, not Hispanic or Latino"
)

# Oklahoma
oklahoma_data <- filter(acs_data, Label == "Bachelor's degree or higher**")
bdh_wnhp_oklahoma <- tibble(
  Years = oklahoma_data$Years,
  Percentage_wnhp_women = oklahoma_data$`...429`,
  Race = "White alone, not Hispanic or Latino"
)

# Oregon
oregon_data <- filter(acs_data, Label == "Bachelor's degree or higher**")
bdh_wnhp_oregon <- tibble(
  Years = oregon_data$Years,
  Percentage_wnhp_women = oregon_data$`...441`,
  Race = "White alone, not Hispanic or Latino"
)

# Pennsylvania
pennsylvania_data <- filter(acs_data, Label == "Bachelor's degree or higher**")
bdh_wnhp_pennsylvania <- tibble(
  Years = pennsylvania_data$Years,
  Percentage_wnhp_women = pennsylvania_data$`...453`,
  Race = "White alone, not Hispanic or Latino"
)

# Rhode Island
rhodeisland_data <- filter(acs_data, Label == "Bachelor's degree or higher**")
bdh_wnhp_rhodeisland <- tibble(
  Years = rhodeisland_data$Years,
  Percentage_wnhp_women = rhodeisland_data$`...465`,
  Race = "White alone, not Hispanic or Latino"
)

# South Carolina
southcarolina_data <- filter(acs_data, Label == "Bachelor's degree or higher**")
bdh_wnhp_southcarolina <- tibble(
  Years = southcarolina_data$Years,
  Percentage_wnhp_women = southcarolina_data$`...477`,
  Race = "White alone, not Hispanic or Latino"
)

# South Dakota
southdakota_data <- filter(acs_data, Label == "Bachelor's degree or higher**")
bdh_wnhp_southdakota <- tibble(
  Years = southdakota_data$Years,
  Percentage_wnhp_women = southdakota_data$`...489`,
  Race = "White alone, not Hispanic or Latino"
)

# Tennessee
tennessee_data <- filter(acs_data, Label == "Bachelor's degree or higher**")
bdh_wnhp_tennessee <- tibble(
  Years = tennessee_data$Years,
  Percentage_wnhp_women = tennessee_data$`...501`,
  Race = "White alone, not Hispanic or Latino"
)

# Texas
texas_data <- filter(acs_data, Label == "Bachelor's degree or higher**")
bdh_wnhp_texas <- tibble(
  Years = texas_data$Years,
  Percentage_wnhp_women = texas_data$`...513`,
  Race = "White alone, not Hispanic or Latino"
)

# Utah
utah_data <- filter(acs_data, Label == "Bachelor's degree or higher**")
bdh_wnhp_utah <- tibble(
  Years = utah_data$Years,
  Percentage_wnhp_women = utah_data$`...525`,
  Race = "White alone, not Hispanic or Latino"
)

# Vermont
vermont_data <- filter(acs_data, Label == "Bachelor's degree or higher**")
bdh_wnhp_vermont <- tibble(
  Years = vermont_data$Years,
  Percentage_wnhp_women = vermont_data$`...537`,
  Race = "White alone, not Hispanic or Latino"
)

# Virginia
virginia_data <- filter(acs_data, Label == "Bachelor's degree or higher**")
bdh_wnhp_virginia <- tibble(
  Years = virginia_data$Years,
  Percentage_wnhp_women = virginia_data$`...549`,
  Race = "White alone, not Hispanic or Latino"
)

# Washington
washington_data <- filter(acs_data, Label == "Bachelor's degree or higher**")
bdh_wnhp_washington <- tibble(
  Years = washington_data$Years,
  Percentage_wnhp_women = washington_data$`...561`,
  Race = "White alone, not Hispanic or Latino"
)

# West Virginia
westvirginia_data <- filter(acs_data, Label == "Bachelor's degree or higher**")
bdh_wnhp_westvirginia <- tibble(
  Years = westvirginia_data$Years,
  Percentage_wnhp_women = westvirginia_data$`...573`,
  Race = "White alone, not Hispanic or Latino"
)

# Wisconsin
wisconsin_data <- filter(acs_data, Label == "Bachelor's degree or higher**")
bdh_wnhp_wisconsin <- tibble(
  Years = wisconsin_data$Years,
  Percentage_wnhp_women = wisconsin_data$`...585`,
  Race = "White alone, not Hispanic or Latino"
)

# Wyoming
wyoming_data <- filter(acs_data, Label == "Bachelor's degree or higher**")
bdh_wnhp_wyoming <- tibble(
  Years = wyoming_data$Years,
  Percentage_wnhp_women = wyoming_data$`...597`,
  Race = "White alone, not Hispanic or Latino"
)

# Puerto Rico
puertorico_data <- filter(acs_data, Label == "Bachelor's degree or higher**")
bdh_wnhp_puertorico <- tibble(
  Years = puertorico_data$Years,
  Percentage_wnhp_women = puertorico_data$`...609`,
  Race = "White alone, not Hispanic or Latino"
)

# Combine all states
combined_data_wnhp <- bind_rows(
  bdh_wnhp_alabama,
  bdh_wnhp_alaska,
  bdh_wnhp_arizona,
  bdh_wnhp_arkansas,
  bdh_wnhp_california,
  bdh_wnhp_colorado,
  bdh_wnhp_connecticut,
  bdh_wnhp_delaware,
  bdh_wnhp_florida,
  bdh_wnhp_georgia,
  bdh_wnhp_hawaii,
  bdh_wnhp_idaho,
  bdh_wnhp_illinois,
  bdh_wnhp_indiana,
  bdh_wnhp_iowa,
  bdh_wnhp_kansas,
  bdh_wnhp_kentucky,
  bdh_wnhp_louisiana,
  bdh_wnhp_maine,
  bdh_wnhp_maryland,
  bdh_wnhp_massachusetts,
  bdh_wnhp_michigan,
  bdh_wnhp_minnesota,
  bdh_wnhp_mississippi,
  bdh_wnhp_missouri,
  bdh_wnhp_montana,
  bdh_wnhp_nebraska,
  bdh_wnhp_nevada,
  bdh_wnhp_newhampshire,
  bdh_wnhp_newjersey,
  bdh_wnhp_newmexico,
  bdh_wnhp_newyork,
  bdh_wnhp_northcarolina,
  bdh_wnhp_northdakota,
  bdh_wnhp_ohio,
  bdh_wnhp_oklahoma,
  bdh_wnhp_oregon,
  bdh_wnhp_pennsylvania,
  bdh_wnhp_rhodeisland,
  bdh_wnhp_southcarolina,
  bdh_wnhp_southdakota,
  bdh_wnhp_tennessee,
  bdh_wnhp_texas,
  bdh_wnhp_utah,
  bdh_wnhp_vermont,
  bdh_wnhp_virginia,
  bdh_wnhp_washington,
  bdh_wnhp_westvirginia,
  bdh_wnhp_wisconsin,
  bdh_wnhp_wyoming,
  bdh_wnhp_puertorico
)

print(combined_data_wnhp)

```

3.  **Female, Black Alone, Across all U.S. States + Puerto Rico (Status: Cleaned)**

```{r}
library(readxl)
library(dplyr)
library(tibble)

acs_data <- read_excel("dataset/acsfinale.xlsx")

# Alabama
us_blackalone_data <- filter(acs_data, Label == "Bachelor's degree or higher*")
bdh_blackalone_alabama <- tibble(
  Years = us_blackalone_data$Years,
  Percentage_black_women = us_blackalone_data$`Alabama...13`,
  Race = "Black Alone"
)

# Alaska
bdh_blackalone_alaska <- tibble(
  Years = us_blackalone_data$Years,
  Percentage_black_women = us_blackalone_data$`...25`,
  Race = "Black Alone"
)

# Arizona
bdh_blackalone_arizona <- tibble(
  Years = us_blackalone_data$Years,
  Percentage_black_women = us_blackalone_data$`...37`,
  Race = "Black Alone"
)

# Arkansas
bdh_blackalone_arkansas <- tibble(
  Years = us_blackalone_data$Years,
  Percentage_black_women = us_blackalone_data$`...49`,
  Race = "Black Alone"
)

# California
bdh_blackalone_california <- tibble(
  Years = us_blackalone_data$Years,
  Percentage_black_women = us_blackalone_data$`...61`,
  Race = "Black Alone"
)

# Colorado
bdh_blackalone_colorado <- tibble(
  Years = us_blackalone_data$Years,
  Percentage_black_women = us_blackalone_data$`...73`,
  Race = "Black Alone"
)

# Connecticut
bdh_blackalone_connecticut <- tibble(
  Years = us_blackalone_data$Years,
  Percentage_black_women = us_blackalone_data$`...85`,
  Race = "Black Alone"
)

# Delaware
bdh_blackalone_delaware <- tibble(
  Years = us_blackalone_data$Years,
  Percentage_black_women = us_blackalone_data$`...97`,
  Race = "Black Alone"
)

# Florida
bdh_blackalone_florida <- tibble(
  Years = us_blackalone_data$Years,
  Percentage_black_women = us_blackalone_data$`...109`,
  Race = "Black Alone"
)

# Georgia
bdh_blackalone_georgia <- tibble(
  Years = us_blackalone_data$Years,
  Percentage_black_women = us_blackalone_data$`...121`,
  Race = "Black Alone"
)

# Hawaii
bdh_blackalone_hawaii <- tibble(
  Years = us_blackalone_data$Years,
  Percentage_black_women = us_blackalone_data$`...133`,
  Race = "Black Alone"
)

# Idaho
bdh_blackalone_idaho <- tibble(
  Years = us_blackalone_data$Years,
  Percentage_black_women = us_blackalone_data$`...145`,
  Race = "Black Alone"
)

# Illinois
bdh_blackalone_illinois <- tibble(
  Years = us_blackalone_data$Years,
  Percentage_black_women = us_blackalone_data$`...157`,
  Race = "Black Alone"
)

# Indiana
bdh_blackalone_indiana <- tibble(
  Years = us_blackalone_data$Years,
  Percentage_black_women = us_blackalone_data$`...169`,
  Race = "Black Alone"
)

# Iowa
bdh_blackalone_iowa <- tibble(
  Years = us_blackalone_data$Years,
  Percentage_black_women = us_blackalone_data$`...181`,
  Race = "Black Alone"
)

# Kansas
bdh_blackalone_kansas <- tibble(
  Years = us_blackalone_data$Years,
  Percentage_black_women = us_blackalone_data$`...193`,
  Race = "Black Alone"
)

# Kentucky
bdh_blackalone_kentucky <- tibble(
  Years = us_blackalone_data$Years,
  Percentage_black_women = us_blackalone_data$`...205`,
  Race = "Black Alone"
)

# Louisiana
bdh_blackalone_louisiana <- tibble(
  Years = us_blackalone_data$Years,
  Percentage_black_women = us_blackalone_data$`...217`,
  Race = "Black Alone"
)

# Maine
bdh_blackalone_maine <- tibble(
  Years = us_blackalone_data$Years,
  Percentage_black_women = us_blackalone_data$`...229`,
  Race = "Black Alone"
)

# Maryland
bdh_blackalone_maryland <- tibble(
  Years = us_blackalone_data$Years,
  Percentage_black_women = us_blackalone_data$`...241`,
  Race = "Black Alone"
)

# Massachusetts
bdh_blackalone_massachusetts <- tibble(
  Years = us_blackalone_data$Years,
  Percentage_black_women = us_blackalone_data$`...253`,
  Race = "Black Alone"
)

# Michigan
bdh_blackalone_michigan <- tibble(
  Years = us_blackalone_data$Years,
  Percentage_black_women = us_blackalone_data$`...265`,
  Race = "Black Alone"
)

# Minnesota
bdh_blackalone_minnesota <- tibble(
  Years = us_blackalone_data$Years,
  Percentage_black_women = us_blackalone_data$`...277`,
  Race = "Black Alone"
)

# Mississippi
bdh_blackalone_mississippi <- tibble(
  Years = us_blackalone_data$Years,
  Percentage_black_women = us_blackalone_data$`...289`,
  Race = "Black Alone"
)

# Missouri
bdh_blackalone_missouri <- tibble(
  Years = us_blackalone_data$Years,
  Percentage_black_women = us_blackalone_data$`...301`,
  Race = "Black Alone"
)

# Montana
bdh_blackalone_montana <- tibble(
  Years = us_blackalone_data$Years,
  Percentage_black_women = us_blackalone_data$`...313`,
  Race = "Black Alone"
)

# Nebraska
bdh_blackalone_nebraska <- tibble(
  Years = us_blackalone_data$Years,
  Percentage_black_women = us_blackalone_data$`...325`,
  Race = "Black Alone"
)

# Nevada
bdh_blackalone_nevada <- tibble(
  Years = us_blackalone_data$Years,
  Percentage_black_women = us_blackalone_data$`...337`,
  Race = "Black Alone"
)

# New Hampshire
bdh_blackalone_newhampshire <- tibble(
  Years = us_blackalone_data$Years,
  Percentage_black_women = us_blackalone_data$`...349`,
  Race = "Black Alone"
)

# New Jersey
bdh_blackalone_newjersey <- tibble(
  Years = us_blackalone_data$Years,
  Percentage_black_women = us_blackalone_data$`...361`,
  Race = "Black Alone"
)

# New Mexico
bdh_blackalone_newmexico <- tibble(
  Years = us_blackalone_data$Years,
  Percentage_black_women = us_blackalone_data$`...373`,
  Race = "Black Alone"
)

# New York
bdh_blackalone_newyork <- tibble(
  Years = us_blackalone_data$Years,
  Percentage_black_women = us_blackalone_data$`...385`,
  Race = "Black Alone"
)

# North Carolina
bdh_blackalone_northcarolina <- tibble(
  Years = us_blackalone_data$Years,
  Percentage_black_women = us_blackalone_data$`...397`,
  Race = "Black Alone"
)

# North Dakota
bdh_blackalone_northdakota <- tibble(
  Years = us_blackalone_data$Years,
  Percentage_black_women = us_blackalone_data$`...409`,
  Race = "Black Alone"
)

# Ohio
bdh_blackalone_ohio <- tibble(
  Years = us_blackalone_data$Years,
  Percentage_black_women = us_blackalone_data$`...421`,
  Race = "Black Alone"
)

# Oklahoma
bdh_blackalone_oklahoma <- tibble(
  Years = us_blackalone_data$Years,
  Percentage_black_women = us_blackalone_data$`...433`,
  Race = "Black Alone"
)

# Oregon
bdh_blackalone_oregon <- tibble(
  Years = us_blackalone_data$Years,
  Percentage_black_women = us_blackalone_data$`...445`,
  Race = "Black Alone"
)

# Pennsylvania
bdh_blackalone_pennsylvania <- tibble(
  Years = us_blackalone_data$Years,
  Percentage_black_women = us_blackalone_data$`...457`,
  Race = "Black Alone"
)

# Rhode Island
bdh_blackalone_rhodeisland <- tibble(
  Years = us_blackalone_data$Years,
  Percentage_black_women = us_blackalone_data$`...469`,
  Race = "Black Alone"
)

# South Carolina
bdh_blackalone_southcarolina <- tibble(
  Years = us_blackalone_data$Years,
  Percentage_black_women = us_blackalone_data$`...481`,
  Race = "Black Alone"
)

# South Dakota
bdh_blackalone_southdakota <- tibble(
  Years = us_blackalone_data$Years,
  Percentage_black_women = us_blackalone_data$`...493`,
  Race = "Black Alone"
)

# Tennessee
bdh_blackalone_tennessee <- tibble(
  Years = us_blackalone_data$Years,
  Percentage_black_women = us_blackalone_data$`...505`,
  Race = "Black Alone"
)

# Texas
bdh_blackalone_texas <- tibble(
  Years = us_blackalone_data$Years,
  Percentage_black_women = us_blackalone_data$`...517`,
  Race = "Black Alone"
)

# Utah
bdh_blackalone_utah <- tibble(
  Years = us_blackalone_data$Years,
  Percentage_black_women = us_blackalone_data$`...529`,
  Race = "Black Alone"
)

# Vermont
bdh_blackalone_vermont <- tibble(
  Years = us_blackalone_data$Years,
  Percentage_black_women = us_blackalone_data$`...541`,
  Race = "Black Alone"
)

# Virginia
bdh_blackalone_virginia <- tibble(
  Years = us_blackalone_data$Years,
  Percentage_black_women = us_blackalone_data$`...553`,
  Race = "Black Alone"
)

# Washington
bdh_blackalone_washington <- tibble(
  Years = us_blackalone_data$Years,
  Percentage_black_women = us_blackalone_data$`...565`,
  Race = "Black Alone"
)

# West Virginia
bdh_blackalone_westvirginia <- tibble(
  Years = us_blackalone_data$Years,
  Percentage_black_women = us_blackalone_data$`...577`,
  Race = "Black Alone"
)

# Wisconsin
bdh_blackalone_wisconsin <- tibble(
  Years = us_blackalone_data$Years,
  Percentage_black_women = us_blackalone_data$`...589`,
  Race = "Black Alone"
)

# Wyoming
bdh_blackalone_wyoming <- tibble(
  Years = us_blackalone_data$Years,
  Percentage_black_women = us_blackalone_data$`...601`,
  Race = "Black Alone"
)

# Puerto Rico
bdh_blackalone_puertorico <- tibble(
  Years = us_blackalone_data$Years,
  Percentage_black_women = us_blackalone_data$`...613`,
  Race = "Black Alone"
)

combined_data_blackalone <- bind_rows(
  bdh_blackalone_alabama,
  bdh_blackalone_alaska,
  bdh_blackalone_arizona,
  bdh_blackalone_arkansas,
  bdh_blackalone_california,
  bdh_blackalone_colorado,
  bdh_blackalone_connecticut,
  bdh_blackalone_delaware,
  bdh_blackalone_florida,
  bdh_blackalone_georgia,
  bdh_blackalone_hawaii,
  bdh_blackalone_idaho,
  bdh_blackalone_illinois,
  bdh_blackalone_indiana,
  bdh_blackalone_iowa,
  bdh_blackalone_kansas,
  bdh_blackalone_kentucky,
  bdh_blackalone_louisiana,
  bdh_blackalone_maine,
  bdh_blackalone_maryland,
  bdh_blackalone_massachusetts,
  bdh_blackalone_michigan,
  bdh_blackalone_minnesota,
  bdh_blackalone_mississippi,
  bdh_blackalone_missouri,
  bdh_blackalone_montana,
  bdh_blackalone_nebraska,
  bdh_blackalone_nevada,
  bdh_blackalone_newhampshire,
  bdh_blackalone_newjersey,
  bdh_blackalone_newmexico,
  bdh_blackalone_newyork,
  bdh_blackalone_northcarolina,
  bdh_blackalone_northdakota,
  bdh_blackalone_ohio,
  bdh_blackalone_oklahoma,
  bdh_blackalone_oregon,
  bdh_blackalone_pennsylvania,
  bdh_blackalone_rhodeisland,
  bdh_blackalone_southcarolina,
  bdh_blackalone_southdakota,
  bdh_blackalone_tennessee,
  bdh_blackalone_texas,
  bdh_blackalone_utah,
  bdh_blackalone_vermont,
  bdh_blackalone_virginia,
  bdh_blackalone_washington,
  bdh_blackalone_westvirginia,
  bdh_blackalone_wisconsin,
  bdh_blackalone_wyoming,
  bdh_blackalone_puertorico
)

print(combined_data_blackalone)


```

4.  **Female, American Indian or Alaska Native Alone, Across all U.S. States + Puerto Rico (Status: Cleaned)**

```{r}
library(readxl)
library(dplyr)
library(tibble)


acs_data <- read_excel("dataset/acsfinale.xlsx")

# Alabama
alabama_data <- filter(acs_data, Label == "Bachelor's degree or higher****")
bdh_aianalone_alabama <- tibble(
  Years = alabama_data$Years,
  Percentage_aiap_women = alabama_data$`Alabama...13`,
  Race = "American Indian or Alaska Native Alone"
)

# Alaska
alaska_data <- filter(acs_data, Label == "Bachelor's degree or higher****")
bdh_aianalone_alaska <- tibble(
  Years = alaska_data$Years,
  Percentage_aiap_women = alaska_data$`...25`,
  Race = "American Indian or Alaska Native Alone"
)

# Arizona
arizona_data <- filter(acs_data, Label == "Bachelor's degree or higher****")
bdh_aianalone_arizona <- tibble(
  Years = arizona_data$Years,
  Percentage_aiap_women = arizona_data$`...37`,
  Race = "American Indian or Alaska Native Alone"
)

# Arkansas
arkansas_data <- filter(acs_data, Label == "Bachelor's degree or higher****")
bdh_aianalone_arkansas <- tibble(
  Years = arkansas_data$Years,
  Percentage_aiap_women = arkansas_data$`...49`,
  Race = "American Indian or Alaska Native Alone"
)

# California
california_data <- filter(acs_data, Label == "Bachelor's degree or higher****")
bdh_aianalone_california <- tibble(
  Years = california_data$Years,
  Percentage_aiap_women = california_data$`...61`,
  Race = "American Indian or Alaska Native Alone"
)

# Colorado
colorado_data <- filter(acs_data, Label == "Bachelor's degree or higher****")
bdh_aianalone_colorado <- tibble(
  Years = colorado_data$Years,
  Percentage_aiap_women = colorado_data$`...73`,
  Race = "American Indian or Alaska Native Alone"
)

# Connecticut
connecticut_data <- filter(acs_data, Label == "Bachelor's degree or higher****")
bdh_aianalone_connecticut <- tibble(
  Years = connecticut_data$Years,
  Percentage_aiap_women = connecticut_data$`...85`,
  Race = "American Indian or Alaska Native Alone"
)

# Delaware
delaware_data <- filter(acs_data, Label == "Bachelor's degree or higher****")
bdh_aianalone_delaware <- tibble(
  Years = delaware_data$Years,
  Percentage_aiap_women = delaware_data$`...97`,
  Race = "American Indian or Alaska Native Alone"
)

# Florida
florida_data <- filter(acs_data, Label == "Bachelor's degree or higher****")
bdh_aianalone_florida <- tibble(
  Years = florida_data$Years,
  Percentage_aiap_women = florida_data$`...109`,
  Race = "American Indian or Alaska Native Alone"
)

# Georgia
georgia_data <- filter(acs_data, Label == "Bachelor's degree or higher****")
bdh_aianalone_georgia <- tibble(
  Years = georgia_data$Years,
  Percentage_aiap_women = georgia_data$`...121`,
  Race = "American Indian or Alaska Native Alone"
)

# Hawaii
hawaii_data <- filter(acs_data, Label == "Bachelor's degree or higher****")
bdh_aianalone_hawaii <- tibble(
  Years = hawaii_data$Years,
  Percentage_aiap_women = hawaii_data$`...133`,
  Race = "American Indian or Alaska Native Alone"
)

# Idaho
idaho_data <- filter(acs_data, Label == "Bachelor's degree or higher****")
bdh_aianalone_idaho <- tibble(
  Years = idaho_data$Years,
  Percentage_aiap_women = idaho_data$`...145`,
  Race = "American Indian or Alaska Native Alone"
)

# Illinois
illinois_data <- filter(acs_data, Label == "Bachelor's degree or higher****")
bdh_aianalone_illinois <- tibble(
  Years = illinois_data$Years,
  Percentage_aiap_women = illinois_data$`...157`,
  Race = "American Indian or Alaska Native Alone"
)

# Indiana
indiana_data <- filter(acs_data, Label == "Bachelor's degree or higher****")
bdh_aianalone_indiana <- tibble(
  Years = indiana_data$Years,
  Percentage_aiap_women = indiana_data$`...169`,
  Race = "American Indian or Alaska Native Alone"
)

# Iowa
iowa_data <- filter(acs_data, Label == "Bachelor's degree or higher****")
bdh_aianalone_iowa <- tibble(
  Years = iowa_data$Years,
  Percentage_aiap_women = iowa_data$`...181`,
  Race = "American Indian or Alaska Native Alone"
)

# Kansas
kansas_data <- filter(acs_data, Label == "Bachelor's degree or higher****")
bdh_aianalone_kansas <- tibble(
  Years = kansas_data$Years,
  Percentage_aiap_women = kansas_data$`...193`,
  Race = "American Indian or Alaska Native Alone"
)

# Kentucky
kentucky_data <- filter(acs_data, Label == "Bachelor's degree or higher****")
bdh_aianalone_kentucky <- tibble(
  Years = kentucky_data$Years,
  Percentage_aiap_women = kentucky_data$`...205`,
  Race = "American Indian or Alaska Native Alone"
)

# Louisiana
louisiana_data <- filter(acs_data, Label == "Bachelor's degree or higher****")
bdh_aianalone_louisiana <- tibble(
  Years = louisiana_data$Years,
  Percentage_aiap_women = louisiana_data$`...217`,
  Race = "American Indian or Alaska Native Alone"
)

# Maine
maine_data <- filter(acs_data, Label == "Bachelor's degree or higher****")
bdh_aianalone_maine <- tibble(
  Years = maine_data$Years,
  Percentage_aiap_women = maine_data$`...229`,
  Race = "American Indian or Alaska Native Alone"
)

# Maryland
maryland_data <- filter(acs_data, Label == "Bachelor's degree or higher****")
bdh_aianalone_maryland <- tibble(
  Years = maryland_data$Years,
  Percentage_aiap_women = maryland_data$`...241`,
  Race = "American Indian or Alaska Native Alone"
)

# Massachusetts
massachusetts_data <- filter(acs_data, Label == "Bachelor's degree or higher****")
bdh_aianalone_massachusetts <- tibble(
  Years = massachusetts_data$Years,
  Percentage_aiap_women = massachusetts_data$`...253`,
  Race = "American Indian or Alaska Native Alone"
)

# Michigan
michigan_data <- filter(acs_data, Label == "Bachelor's degree or higher****")
bdh_aianalone_michigan <- tibble(
  Years = michigan_data$Years,
  Percentage_aiap_women = michigan_data$`...265`,
  Race = "American Indian or Alaska Native Alone"
)

# Minnesota
minnesota_data <- filter(acs_data, Label == "Bachelor's degree or higher****")
bdh_aianalone_minnesota <- tibble(
  Years = minnesota_data$Years,
  Percentage_aiap_women = minnesota_data$`...277`,
  Race = "American Indian or Alaska Native Alone"
)

# Mississippi
mississippi_data <- filter(acs_data, Label == "Bachelor's degree or higher****")
bdh_aianalone_mississippi <- tibble(
  Years = mississippi_data$Years,
  Percentage_aiap_women = mississippi_data$`...289`,
  Race = "American Indian or Alaska Native Alone"
)

# Missouri
missouri_data <- filter(acs_data, Label == "Bachelor's degree or higher****")
bdh_aianalone_missouri <- tibble(
  Years = missouri_data$Years,
  Percentage_aiap_women = missouri_data$`...301`,
  Race = "American Indian or Alaska Native Alone"
)

# Montana
montana_data <- filter(acs_data, Label == "Bachelor's degree or higher****")
bdh_aianalone_montana <- tibble(
  Years = montana_data$Years,
  Percentage_aiap_women = montana_data$`...313`,
  Race = "American Indian or Alaska Native Alone"
)

# Nebraska
nebraska_data <- filter(acs_data, Label == "Bachelor's degree or higher****")
bdh_aianalone_nebraska <- tibble(
  Years = nebraska_data$Years,
  Percentage_aiap_women = nebraska_data$`...325`,
  Race = "American Indian or Alaska Native Alone"
)

# Nevada
nevada_data <- filter(acs_data, Label == "Bachelor's degree or higher****")
bdh_aianalone_nevada <- tibble(
  Years = nevada_data$Years,
  Percentage_aiap_women = nevada_data$`...337`,
  Race = "American Indian or Alaska Native Alone"
)

# New Hampshire
newhampshire_data <- filter(acs_data, Label == "Bachelor's degree or higher****")
bdh_aianalone_newhampshire <- tibble(
  Years = newhampshire_data$Years,
  Percentage_aiap_women = newhampshire_data$`...349`,
  Race = "American Indian or Alaska Native Alone"
)

# New Jersey
newjersey_data <- filter(acs_data, Label == "Bachelor's degree or higher****")
bdh_aianalone_newjersey <- tibble(
  Years = newjersey_data$Years,
  Percentage_aiap_women = newjersey_data$`...361`,
  Race = "American Indian or Alaska Native Alone"
)

# New Mexico
newmexico_data <- filter(acs_data, Label == "Bachelor's degree or higher****")
bdh_aianalone_newmexico <- tibble(
  Years = newmexico_data$Years,
  Percentage_aiap_women = newmexico_data$`...373`,
  Race = "American Indian or Alaska Native Alone"
)

# New York
newyork_data <- filter(acs_data, Label == "Bachelor's degree or higher****")
bdh_aianalone_newyork <- tibble(
  Years = newyork_data$Years,
  Percentage_aiap_women = newyork_data$`...385`,
  Race = "American Indian or Alaska Native Alone"
)

# North Carolina
northcarolina_data <- filter(acs_data, Label == "Bachelor's degree or higher****")
bdh_aianalone_northcarolina <- tibble(
  Years = northcarolina_data$Years,
  Percentage_aiap_women = northcarolina_data$`...397`,
  Race = "American Indian or Alaska Native Alone"
)

# North Dakota
northdakota_data <- filter(acs_data, Label == "Bachelor's degree or higher****")
bdh_aianalone_northdakota <- tibble(
  Years = northdakota_data$Years,
  Percentage_aiap_women = northdakota_data$`...409`,
  Race = "American Indian or Alaska Native Alone"
)

# Ohio
ohio_data <- filter(acs_data, Label == "Bachelor's degree or higher****")
bdh_aianalone_ohio <- tibble(
  Years = ohio_data$Years,
  Percentage_aiap_women = ohio_data$`...421`,
  Race = "American Indian or Alaska Native Alone"
)

# Oklahoma
oklahoma_data <- filter(acs_data, Label == "Bachelor's degree or higher****")
bdh_aianalone_oklahoma <- tibble(
  Years = oklahoma_data$Years,
  Percentage_aiap_women = oklahoma_data$`...433`,
  Race = "American Indian or Alaska Native Alone"
)

# Oregon
oregon_data <- filter(acs_data, Label == "Bachelor's degree or higher****")
bdh_aianalone_oregon <- tibble(
  Years = oregon_data$Years,
  Percentage_aiap_women = oregon_data$`...445`,
  Race = "American Indian or Alaska Native Alone"
)

# Pennsylvania
pennsylvania_data <- filter(acs_data, Label == "Bachelor's degree or higher****")
bdh_aianalone_pennsylvania <- tibble(
  Years = pennsylvania_data$Years,
  Percentage_aiap_women = pennsylvania_data$`...457`,
  Race = "American Indian or Alaska Native Alone"
)

# Rhode Island
rhodeisland_data <- filter(acs_data, Label == "Bachelor's degree or higher****")
bdh_aianalone_rhodeisland <- tibble(
  Years = rhodeisland_data$Years,
  Percentage_aiap_women = rhodeisland_data$`...469`,
  Race = "American Indian or Alaska Native Alone"
)

# South Carolina
southcarolina_data <- filter(acs_data, Label == "Bachelor's degree or higher****")
bdh_aianalone_southcarolina <- tibble(
  Years = southcarolina_data$Years,
  Percentage_aiap_women = southcarolina_data$`...481`,
  Race = "American Indian or Alaska Native Alone"
)

# South Dakota
southdakota_data <- filter(acs_data, Label == "Bachelor's degree or higher****")
bdh_aianalone_southdakota <- tibble(
  Years = southdakota_data$Years,
  Percentage_aiap_women = southdakota_data$`...493`,
  Race = "American Indian or Alaska Native Alone"
)

# Tennessee
tennessee_data <- filter(acs_data, Label == "Bachelor's degree or higher****")
bdh_aianalone_tennessee <- tibble(
  Years = tennessee_data$Years,
  Percentage_aiap_women = tennessee_data$`...505`,
  Race = "American Indian or Alaska Native Alone"
)

# Texas
texas_data <- filter(acs_data, Label == "Bachelor's degree or higher****")
bdh_aianalone_texas <- tibble(
  Years = texas_data$Years,
  Percentage_aiap_women = texas_data$`...517`,
  Race = "American Indian or Alaska Native Alone"
)

# Utah
utah_data <- filter(acs_data, Label == "Bachelor's degree or higher****")
bdh_aianalone_utah <- tibble(
  Years = utah_data$Years,
  Percentage_aiap_women = utah_data$`...529`,
  Race = "American Indian or Alaska Native Alone"
)

# Vermont
vermont_data <- filter(acs_data, Label == "Bachelor's degree or higher****")
bdh_aianalone_vermont <- tibble(
  Years = vermont_data$Years,
  Percentage_aiap_women = vermont_data$`...541`,
  Race = "American Indian or Alaska Native Alone"
)

# Virginia
virginia_data <- filter(acs_data, Label == "Bachelor's degree or higher****")
bdh_aianalone_virginia <- tibble(
  Years = virginia_data$Years,
  Percentage_aiap_women = virginia_data$`...553`,
  Race = "American Indian or Alaska Native Alone"
)

# Washington
washington_data <- filter(acs_data, Label == "Bachelor's degree or higher****")
bdh_aianalone_washington <- tibble(
  Years = washington_data$Years,
  Percentage_aiap_women = washington_data$`...565`,
  Race = "American Indian or Alaska Native Alone"
)

# West Virginia
westvirginia_data <- filter(acs_data, Label == "Bachelor's degree or higher****")
bdh_aianalone_westvirginia <- tibble(
  Years = westvirginia_data$Years,
  Percentage_aiap_women = westvirginia_data$`...577`,
  Race = "American Indian or Alaska Native Alone"
)

# Wisconsin
wisconsin_data <- filter(acs_data, Label == "Bachelor's degree or higher****")
bdh_aianalone_wisconsin <- tibble(
  Years = wisconsin_data$Years,
  Percentage_aiap_women = wisconsin_data$`...589`,
  Race = "American Indian or Alaska Native Alone"
)

# Wyoming
wyoming_data <- filter(acs_data, Label == "Bachelor's degree or higher****")
bdh_aianalone_wyoming <- tibble(
  Years = wyoming_data$Years,
  Percentage_aiap_women = wyoming_data$`...601`,
  Race = "American Indian or Alaska Native Alone"
)

# Puerto Rico
puertorico_data <- filter(acs_data, Label == "Bachelor's degree or higher****")
bdh_aianalone_puertorico <- tibble(
  Years = puertorico_data$Years,
  Percentage_aiap_women = puertorico_data$`...613`,
  Race = "American Indian or Alaska Native Alone"
)


combined_data_aianalone <- bind_rows(
  bdh_aianalone_alabama,
  bdh_aianalone_alaska,
  bdh_aianalone_arizona,
  bdh_aianalone_arkansas,
  bdh_aianalone_california,
  bdh_aianalone_colorado,
  bdh_aianalone_connecticut,
  bdh_aianalone_delaware,
  bdh_aianalone_florida,
  bdh_aianalone_georgia,
  bdh_aianalone_hawaii,
  bdh_aianalone_idaho,
  bdh_aianalone_illinois,
  bdh_aianalone_indiana,
  bdh_aianalone_iowa,
  bdh_aianalone_kansas,
  bdh_aianalone_kentucky,
  bdh_aianalone_louisiana,
  bdh_aianalone_maine,
  bdh_aianalone_maryland,
  bdh_aianalone_massachusetts,
  bdh_aianalone_michigan,
  bdh_aianalone_minnesota,
  bdh_aianalone_mississippi,
  bdh_aianalone_missouri,
  bdh_aianalone_montana,
  bdh_aianalone_nebraska,
  bdh_aianalone_nevada,
  bdh_aianalone_newhampshire,
  bdh_aianalone_newjersey,
  bdh_aianalone_newmexico,
  bdh_aianalone_newyork,
  bdh_aianalone_northcarolina,
  bdh_aianalone_northdakota,
  bdh_aianalone_ohio,
  bdh_aianalone_oklahoma,
  bdh_aianalone_oregon,
  bdh_aianalone_pennsylvania,
  bdh_aianalone_rhodeisland,
  bdh_aianalone_southcarolina,
  bdh_aianalone_southdakota,
  bdh_aianalone_tennessee,
  bdh_aianalone_texas,
  bdh_aianalone_utah,
  bdh_aianalone_vermont,
  bdh_aianalone_virginia,
  bdh_aianalone_washington,
  bdh_aianalone_westvirginia,
  bdh_aianalone_wisconsin,
  bdh_aianalone_wyoming,
  bdh_aianalone_puertorico
)

print(combined_data_aianalone)


```

5.  **Female, Asian Alone, Across all U.S. States + Puerto Rico (Status: Cleaned)**

```{r}
library(readxl)
library(dplyr)
library(tibble)

acs_data <- read_excel("dataset/acsfinale.xlsx")

# Alabama
alabama_data <- filter(acs_data, Label == "Bachelor's degree or higher*****")
bdh_asianalone_alabama <- tibble(
  Years = alabama_data$Years,
  Percentage_asian_women = alabama_data$`Alabama...13`,
  Race = "Asian Alone"
)

# Alaska
alaska_data <- filter(acs_data, Label == "Bachelor's degree or higher*****")
bdh_asianalone_alaska <- tibble(
  Years = alaska_data$Years,
  Percentage_asian_women = alaska_data$`...25`,
  Race = "Asian Alone"
)

# Arizona
arizona_data <- filter(acs_data, Label == "Bachelor's degree or higher*****")
bdh_asianalone_arizona <- tibble(
  Years = arizona_data$Years,
  Percentage_asian_women = arizona_data$`...37`,
  Race = "Asian Alone"
)

# Arkansas
arkansas_data <- filter(acs_data, Label == "Bachelor's degree or higher*****")
bdh_asianalone_arkansas <- tibble(
  Years = arkansas_data$Years,
  Percentage_asian_women = arkansas_data$`...49`,
  Race = "Asian Alone"
)

# California
california_data <- filter(acs_data, Label == "Bachelor's degree or higher*****")
bdh_asianalone_california <- tibble(
  Years = california_data$Years,
  Percentage_asian_women = california_data$`...61`,
  Race = "Asian Alone"
)

# Colorado
colorado_data <- filter(acs_data, Label == "Bachelor's degree or higher*****")
bdh_asianalone_colorado <- tibble(
  Years = colorado_data$Years,
  Percentage_asian_women = colorado_data$`...73`,
  Race = "Asian Alone"
)

# Connecticut
connecticut_data <- filter(acs_data, Label == "Bachelor's degree or higher*****")
bdh_asianalone_connecticut <- tibble(
  Years = connecticut_data$Years,
  Percentage_asian_women = connecticut_data$`...85`,
  Race = "Asian Alone"
)

# Delaware
delaware_data <- filter(acs_data, Label == "Bachelor's degree or higher*****")
bdh_asianalone_delaware <- tibble(
  Years = delaware_data$Years,
  Percentage_asian_women = delaware_data$`...97`,
  Race = "Asian Alone"
)

# Florida
florida_data <- filter(acs_data, Label == "Bachelor's degree or higher*****")
bdh_asianalone_florida <- tibble(
  Years = florida_data$Years,
  Percentage_asian_women = florida_data$`...109`,
  Race = "Asian Alone"
)

# Georgia
georgia_data <- filter(acs_data, Label == "Bachelor's degree or higher*****")
bdh_asianalone_georgia <- tibble(
  Years = georgia_data$Years,
  Percentage_asian_women = georgia_data$`...121`,
  Race = "Asian Alone"
)

# Hawaii
hawaii_data <- filter(acs_data, Label == "Bachelor's degree or higher*****")
bdh_asianalone_hawaii <- tibble(
  Years = hawaii_data$Years,
  Percentage_asian_women = hawaii_data$`...133`,
  Race = "Asian Alone"
)

# Idaho
idaho_data <- filter(acs_data, Label == "Bachelor's degree or higher*****")
bdh_asianalone_idaho <- tibble(
  Years = idaho_data$Years,
  Percentage_asian_women = idaho_data$`...145`,
  Race = "Asian Alone"
)

# Illinois
illinois_data <- filter(acs_data, Label == "Bachelor's degree or higher*****")
bdh_asianalone_illinois <- tibble(
  Years = illinois_data$Years,
  Percentage_asian_women = illinois_data$`...157`,
  Race = "Asian Alone"
)

# Indiana
indiana_data <- filter(acs_data, Label == "Bachelor's degree or higher*****")
bdh_asianalone_indiana <- tibble(
  Years = indiana_data$Years,
  Percentage_asian_women = indiana_data$`...169`,
  Race = "Asian Alone"
)

# Iowa
iowa_data <- filter(acs_data, Label == "Bachelor's degree or higher*****")
bdh_asianalone_iowa <- tibble(
  Years = iowa_data$Years,
  Percentage_asian_women = iowa_data$`...181`,
  Race = "Asian Alone"
)

# Kansas
kansas_data <- filter(acs_data, Label == "Bachelor's degree or higher*****")
bdh_asianalone_kansas <- tibble(
  Years = kansas_data$Years,
  Percentage_asian_women = kansas_data$`...193`,
  Race = "Asian Alone"
)

# Kentucky
kentucky_data <- filter(acs_data, Label == "Bachelor's degree or higher*****")
bdh_asianalone_kentucky <- tibble(
  Years = kentucky_data$Years,
  Percentage_asian_women = kentucky_data$`...205`,
  Race = "Asian Alone"
)

# Louisiana
louisiana_data <- filter(acs_data, Label == "Bachelor's degree or higher*****")
bdh_asianalone_louisiana <- tibble(
  Years = louisiana_data$Years,
  Percentage_asian_women = louisiana_data$`...217`,
  Race = "Asian Alone"
)

# Maine
maine_data <- filter(acs_data, Label == "Bachelor's degree or higher*****")
bdh_asianalone_maine <- tibble(
  Years = maine_data$Years,
  Percentage_asian_women = maine_data$`...229`,
  Race = "Asian Alone"
)

# Maryland
maryland_data <- filter(acs_data, Label == "Bachelor's degree or higher*****")
bdh_asianalone_maryland <- tibble(
  Years = maryland_data$Years,
  Percentage_asian_women = maryland_data$`...241`,
  Race = "Asian Alone"
)

# Massachusetts
massachusetts_data <- filter(acs_data, Label == "Bachelor's degree or higher*****")
bdh_asianalone_massachusetts <- tibble(
  Years = massachusetts_data$Years,
  Percentage_asian_women = massachusetts_data$`...253`,
  Race = "Asian Alone"
)

# Michigan
michigan_data <- filter(acs_data, Label == "Bachelor's degree or higher*****")
bdh_asianalone_michigan <- tibble(
  Years = michigan_data$Years,
  Percentage_asian_women = michigan_data$`...265`,
  Race = "Asian Alone"
)

# Minnesota
minnesota_data <- filter(acs_data, Label == "Bachelor's degree or higher*****")
bdh_asianalone_minnesota <- tibble(
  Years = minnesota_data$Years,
  Percentage_asian_women = minnesota_data$`...277`,
  Race = "Asian Alone"
)

# Mississippi
mississippi_data <- filter(acs_data, Label == "Bachelor's degree or higher*****")
bdh_asianalone_mississippi <- tibble(
  Years = mississippi_data$Years,
  Percentage_asian_women = mississippi_data$`...289`,
  Race = "Asian Alone"
)

# Missouri
missouri_data <- filter(acs_data, Label == "Bachelor's degree or higher*****")
bdh_asianalone_missouri <- tibble(
  Years = missouri_data$Years,
  Percentage_asian_women = missouri_data$`...301`,
  Race = "Asian Alone"
)

# Montana
montana_data <- filter(acs_data, Label == "Bachelor's degree or higher*****")
bdh_asianalone_montana <- tibble(
  Years = montana_data$Years,
  Percentage_asian_women = montana_data$`...313`,
  Race = "Asian Alone"
)

# Nebraska
nebraska_data <- filter(acs_data, Label == "Bachelor's degree or higher*****")
bdh_asianalone_nebraska <- tibble(
  Years = nebraska_data$Years,
  Percentage_asian_women = nebraska_data$`...325`,
  Race = "Asian Alone"
)

# Nevada
nevada_data <- filter(acs_data, Label == "Bachelor's degree or higher*****")
bdh_asianalone_nevada <- tibble(
  Years = nevada_data$Years,
  Percentage_asian_women = nevada_data$`...337`,
  Race = "Asian Alone"
)

# New Hampshire
newhampshire_data <- filter(acs_data, Label == "Bachelor's degree or higher*****")
bdh_asianalone_newhampshire <- tibble(
  Years = newhampshire_data$Years,
  Percentage_asian_women = newhampshire_data$`...349`,
  Race = "Asian Alone"
)

# New Jersey
newjersey_data <- filter(acs_data, Label == "Bachelor's degree or higher*****")
bdh_asianalone_newjersey <- tibble(
  Years = newjersey_data$Years,
  Percentage_asian_women = newjersey_data$`...361`,
  Race = "Asian Alone"
)

# New Mexico
newmexico_data <- filter(acs_data, Label == "Bachelor's degree or higher*****")
bdh_asianalone_newmexico <- tibble(
  Years = newmexico_data$Years,
  Percentage_asian_women = newmexico_data$`...373`,
  Race = "Asian Alone"
)

# New York
newyork_data <- filter(acs_data, Label == "Bachelor's degree or higher*****")
bdh_asianalone_newyork <- tibble(
  Years = newyork_data$Years,
  Percentage_asian_women = newyork_data$`...385`,
  Race = "Asian Alone"
)

# North Carolina
northcarolina_data <- filter(acs_data, Label == "Bachelor's degree or higher*****")
bdh_asianalone_northcarolina <- tibble(
  Years = northcarolina_data$Years,
  Percentage_asian_women = northcarolina_data$`...397`,
  Race = "Asian Alone"
)

# North Dakota
northdakota_data <- filter(acs_data, Label == "Bachelor's degree or higher*****")
bdh_asianalone_northdakota <- tibble(
  Years = northdakota_data$Years,
  Percentage_asian_women = northdakota_data$`...409`,
  Race = "Asian Alone"
)

# Ohio
ohio_data <- filter(acs_data, Label == "Bachelor's degree or higher*****")
bdh_asianalone_ohio <- tibble(
  Years = ohio_data$Years,
  Percentage_asian_women = ohio_data$`...421`,
  Race = "Asian Alone"
)

# Oklahoma
oklahoma_data <- filter(acs_data, Label == "Bachelor's degree or higher*****")
bdh_asianalone_oklahoma <- tibble(
  Years = oklahoma_data$Years,
  Percentage_asian_women = oklahoma_data$`...433`,
  Race = "Asian Alone"
)

# Oregon
oregon_data <- filter(acs_data, Label == "Bachelor's degree or higher*****")
bdh_asianalone_oregon <- tibble(
  Years = oregon_data$Years,
  Percentage_asian_women = oregon_data$`...445`,
  Race = "Asian Alone"
)

# Pennsylvania
pennsylvania_data <- filter(acs_data, Label == "Bachelor's degree or higher*****")
bdh_asianalone_pennsylvania <- tibble(
  Years = pennsylvania_data$Years,
  Percentage_asian_women = pennsylvania_data$`...457`,
  Race = "Asian Alone"
)

# Rhode Island
rhodeisland_data <- filter(acs_data, Label == "Bachelor's degree or higher*****")
bdh_asianalone_rhodeisland <- tibble(
  Years = rhodeisland_data$Years,
  Percentage_asian_women = rhodeisland_data$`...469`,
  Race = "Asian Alone"
)

# South Carolina
southcarolina_data <- filter(acs_data, Label == "Bachelor's degree or higher*****")
bdh_asianalone_southcarolina <- tibble(
  Years = southcarolina_data$Years,
  Percentage_asian_women = southcarolina_data$`...481`,
  Race = "Asian Alone"
)

# South Dakota
southdakota_data <- filter(acs_data, Label == "Bachelor's degree or higher*****")
bdh_asianalone_southdakota <- tibble(
  Years = southdakota_data$Years,
  Percentage_asian_women = southdakota_data$`...493`,
  Race = "Asian Alone"
)

# Tennessee
tennessee_data <- filter(acs_data, Label == "Bachelor's degree or higher*****")
bdh_asianalone_tennessee <- tibble(
  Years = tennessee_data$Years,
  Percentage_asian_women = tennessee_data$`...505`,
  Race = "Asian Alone"
)

# Texas
texas_data <- filter(acs_data, Label == "Bachelor's degree or higher*****")
bdh_asianalone_texas <- tibble(
  Years = texas_data$Years,
  Percentage_asian_women = texas_data$`...517`,
  Race = "Asian Alone"
)

# Utah
utah_data <- filter(acs_data, Label == "Bachelor's degree or higher*****")
bdh_asianalone_utah <- tibble(
  Years = utah_data$Years,
  Percentage_asian_women = utah_data$`...529`,
  Race = "Asian Alone"
)

# Vermont
vermont_data <- filter(acs_data, Label == "Bachelor's degree or higher*****")
bdh_asianalone_vermont <- tibble(
  Years = vermont_data$Years,
  Percentage_asian_women = vermont_data$`...541`,
  Race = "Asian Alone"
)

# Virginia
virginia_data <- filter(acs_data, Label == "Bachelor's degree or higher*****")
bdh_asianalone_virginia <- tibble(
  Years = virginia_data$Years,
  Percentage_asian_women = virginia_data$`...553`,
  Race = "Asian Alone"
)

# Washington
washington_data <- filter(acs_data, Label == "Bachelor's degree or higher*****")
bdh_asianalone_washington <- tibble(
  Years = washington_data$Years,
  Percentage_asian_women = washington_data$`...565`,
  Race = "Asian Alone"
)

# West Virginia
westvirginia_data <- filter(acs_data, Label == "Bachelor's degree or higher*****")
bdh_asianalone_westvirginia <- tibble(
  Years = westvirginia_data$Years,
  Percentage_asian_women = westvirginia_data$`...577`,
  Race = "Asian Alone"
)

# Wisconsin
wisconsin_data <- filter(acs_data, Label == "Bachelor's degree or higher*****")
bdh_asianalone_wisconsin <- tibble(
  Years = wisconsin_data$Years,
  Percentage_asian_women = wisconsin_data$`...589`,
  Race = "Asian Alone"
)

# Wyoming
wyoming_data <- filter(acs_data, Label == "Bachelor's degree or higher*****")
bdh_asianalone_wyoming <- tibble(
  Years = wyoming_data$Years,
  Percentage_asian_women = wyoming_data$`...601`,
  Race = "Asian Alone"
)

# Puerto Rico
puertorico_data <- filter(acs_data, Label == "Bachelor's degree or higher*****")
bdh_asianalone_puertorico <- tibble(
  Years = puertorico_data$Years,
  Percentage_asian_women = puertorico_data$`Puerto Rico...613`,
  Race = "Asian Alone"
)

# Combining all the dataframes
combined_data_asianalone <- bind_rows(
  bdh_asianalone_alabama,
  bdh_asianalone_alaska,
  bdh_asianalone_arizona,
  bdh_asianalone_arkansas,
  bdh_asianalone_california,
  bdh_asianalone_colorado,
  bdh_asianalone_connecticut,
  bdh_asianalone_delaware,
  bdh_asianalone_florida,
  bdh_asianalone_georgia,
  bdh_asianalone_hawaii,
  bdh_asianalone_idaho,
  bdh_asianalone_illinois,
  bdh_asianalone_indiana,
  bdh_asianalone_iowa,
  bdh_asianalone_kansas,
  bdh_asianalone_kentucky,
  bdh_asianalone_louisiana,
  bdh_asianalone_maine,
  bdh_asianalone_maryland,
  bdh_asianalone_massachusetts,
  bdh_asianalone_michigan,
  bdh_asianalone_minnesota,
  bdh_asianalone_mississippi,
  bdh_asianalone_missouri,
  bdh_asianalone_montana,
  bdh_asianalone_nebraska,
  bdh_asianalone_nevada,
  bdh_asianalone_newhampshire,
  bdh_asianalone_newjersey,
  bdh_asianalone_newmexico,
  bdh_asianalone_newyork,
  bdh_asianalone_northcarolina,
  bdh_asianalone_northdakota,
  bdh_asianalone_ohio,
  bdh_asianalone_oklahoma,
  bdh_asianalone_oregon,
  bdh_asianalone_pennsylvania,
  bdh_asianalone_rhodeisland,
  bdh_asianalone_southcarolina,
  bdh_asianalone_southdakota,
  bdh_asianalone_tennessee,
  bdh_asianalone_texas,
  bdh_asianalone_utah,
  bdh_asianalone_vermont,
  bdh_asianalone_virginia,
  bdh_asianalone_washington,
  bdh_asianalone_westvirginia,
  bdh_asianalone_wisconsin,
  bdh_asianalone_wyoming,
  bdh_asianalone_puertorico
)


print(combined_data_asianalone)


```

6.  **Female, Native Hawaiian and Other Pacific Islander Alone, Across all U.S. States + Puerto Rico (Status: Cleaned)**

```{r}
library(readxl)
library(dplyr)
library(tibble)


acs_data <- read_excel("dataset/acsfinale.xlsx")

# Alabama
alabama_data <- filter(acs_data, Label == "Bachelor's degree or higher******")
bdh_nhopalone_alabama <- tibble(
  Years = alabama_data$Years,
  Percentage_nhop_women = alabama_data$`Alabama...13`,
  Race = "Native Hawaiian and Other Pacific Islander Alone"
)

# Alaska
alaska_data <- filter(acs_data, Label == "Bachelor's degree or higher******")
bdh_nhopalone_alaska <- tibble(
  Years = alaska_data$Years,
  Percentage_nhop_women = alaska_data$`...25`,
  Race = "Native Hawaiian and Other Pacific Islander Alone"
)

# Arizona
arizona_data <- filter(acs_data, Label == "Bachelor's degree or higher******")
bdh_nhopalone_arizona <- tibble(
  Years = arizona_data$Years,
  Percentage_nhop_women = arizona_data$`...37`,
  Race = "Native Hawaiian and Other Pacific Islander Alone"
)

# Arkansas
arkansas_data <- filter(acs_data, Label == "Bachelor's degree or higher******")
bdh_nhopalone_arkansas <- tibble(
  Years = arkansas_data$Years,
  Percentage_nhop_women = arkansas_data$`...49`,
  Race = "Native Hawaiian and Other Pacific Islander Alone"
)

# California
california_data <- filter(acs_data, Label == "Bachelor's degree or higher******")
bdh_nhopalone_california <- tibble(
  Years = california_data$Years,
  Percentage_nhop_women = california_data$`...61`,
  Race = "Native Hawaiian and Other Pacific Islander Alone"
)

# Colorado
colorado_data <- filter(acs_data, Label == "Bachelor's degree or higher******")
bdh_nhopalone_colorado <- tibble(
  Years = colorado_data$Years,
  Percentage_nhop_women = colorado_data$`...73`,
  Race = "Native Hawaiian and Other Pacific Islander Alone"
)

# Connecticut
connecticut_data <- filter(acs_data, Label == "Bachelor's degree or higher******")
bdh_nhopalone_connecticut <- tibble(
  Years = connecticut_data$Years,
  Percentage_nhop_women = connecticut_data$`...85`,
  Race = "Native Hawaiian and Other Pacific Islander Alone"
)

# Delaware
delaware_data <- filter(acs_data, Label == "Bachelor's degree or higher******")
bdh_nhopalone_delaware <- tibble(
  Years = delaware_data$Years,
  Percentage_nhop_women = delaware_data$`...97`,
  Race = "Native Hawaiian and Other Pacific Islander Alone"
)

# Florida
florida_data <- filter(acs_data, Label == "Bachelor's degree or higher******")
bdh_nhopalone_florida <- tibble(
  Years = florida_data$Years,
  Percentage_nhop_women = florida_data$`...109`,
  Race = "Native Hawaiian and Other Pacific Islander Alone"
)

# Georgia
georgia_data <- filter(acs_data, Label == "Bachelor's degree or higher******")
bdh_nhopalone_georgia <- tibble(
  Years = georgia_data$Years,
  Percentage_nhop_women = georgia_data$`...121`,
  Race = "Native Hawaiian and Other Pacific Islander Alone"
)

# Hawaii
hawaii_data <- filter(acs_data, Label == "Bachelor's degree or higher******")
bdh_nhopalone_hawaii <- tibble(
  Years = hawaii_data$Years,
  Percentage_nhop_women = hawaii_data$`...133`,
  Race = "Native Hawaiian and Other Pacific Islander Alone"
)

# Idaho
idaho_data <- filter(acs_data, Label == "Bachelor's degree or higher******")
bdh_nhopalone_idaho <- tibble(
  Years = idaho_data$Years,
  Percentage_nhop_women = idaho_data$`...145`,
  Race = "Native Hawaiian and Other Pacific Islander Alone"
)

# Illinois
illinois_data <- filter(acs_data, Label == "Bachelor's degree or higher******")
bdh_nhopalone_illinois <- tibble(
  Years = illinois_data$Years,
  Percentage_nhop_women = illinois_data$`...157`,
  Race = "Native Hawaiian and Other Pacific Islander Alone"
)

# Indiana
indiana_data <- filter(acs_data, Label == "Bachelor's degree or higher******")
bdh_nhopalone_indiana <- tibble(
  Years = indiana_data$Years,
  Percentage_nhop_women = indiana_data$`...169`,
  Race = "Native Hawaiian and Other Pacific Islander Alone"
)

# Iowa
iowa_data <- filter(acs_data, Label == "Bachelor's degree or higher******")
bdh_nhopalone_iowa <- tibble(
  Years = iowa_data$Years,
  Percentage_nhop_women = iowa_data$`...181`,
  Race = "Native Hawaiian and Other Pacific Islander Alone"
)

# Kansas
kansas_data <- filter(acs_data, Label == "Bachelor's degree or higher******")
bdh_nhopalone_kansas <- tibble(
  Years = kansas_data$Years,
  Percentage_nhop_women = kansas_data$`...193`,
  Race = "Native Hawaiian and Other Pacific Islander Alone"
)

# Kentucky
kentucky_data <- filter(acs_data, Label == "Bachelor's degree or higher******")
bdh_nhopalone_kentucky <- tibble(
  Years = kentucky_data$Years,
  Percentage_nhop_women = kentucky_data$`...205`,
  Race = "Native Hawaiian and Other Pacific Islander Alone"
)

# Louisiana
louisiana_data <- filter(acs_data, Label == "Bachelor's degree or higher******")
bdh_nhopalone_louisiana <- tibble(
  Years = louisiana_data$Years,
  Percentage_nhop_women = louisiana_data$`...217`,
  Race = "Native Hawaiian and Other Pacific Islander Alone"
)

# Maine
maine_data <- filter(acs_data, Label == "Bachelor's degree or higher******")
bdh_nhopalone_maine <- tibble(
  Years = maine_data$Years,
  Percentage_nhop_women = maine_data$`...229`,
  Race = "Native Hawaiian and Other Pacific Islander Alone"
)

# Maryland
maryland_data <- filter(acs_data, Label == "Bachelor's degree or higher******")
bdh_nhopalone_maryland <- tibble(
  Years = maryland_data$Years,
  Percentage_nhop_women = maryland_data$`...241`,
  Race = "Native Hawaiian and Other Pacific Islander Alone"
)

# Massachusetts
massachusetts_data <- filter(acs_data, Label == "Bachelor's degree or higher******")
bdh_nhopalone_massachusetts <- tibble(
  Years = massachusetts_data$Years,
  Percentage_nhop_women = massachusetts_data$`...253`,
  Race = "Native Hawaiian and Other Pacific Islander Alone"
)

# Michigan
michigan_data <- filter(acs_data, Label == "Bachelor's degree or higher******")
bdh_nhopalone_michigan <- tibble(
  Years = michigan_data$Years,
  Percentage_nhop_women = michigan_data$`...265`,
  Race = "Native Hawaiian and Other Pacific Islander Alone"
)

# Minnesota
minnesota_data <- filter(acs_data, Label == "Bachelor's degree or higher******")
bdh_nhopalone_minnesota <- tibble(
  Years = minnesota_data$Years,
  Percentage_nhop_women = minnesota_data$`...277`,
  Race = "Native Hawaiian and Other Pacific Islander Alone"
)

# Mississippi
mississippi_data <- filter(acs_data, Label == "Bachelor's degree or higher******")
bdh_nhopalone_mississippi <- tibble(
  Years = mississippi_data$Years,
  Percentage_nhop_women = mississippi_data$`...289`,
  Race = "Native Hawaiian and Other Pacific Islander Alone"
)

# Missouri
missouri_data <- filter(acs_data, Label == "Bachelor's degree or higher******")
bdh_nhopalone_missouri <- tibble(
  Years = missouri_data$Years,
  Percentage_nhop_women = missouri_data$`...301`,
  Race = "Native Hawaiian and Other Pacific Islander Alone"
)

# Montana
montana_data <- filter(acs_data, Label == "Bachelor's degree or higher******")
bdh_nhopalone_montana <- tibble(
  Years = montana_data$Years,
  Percentage_nhop_women = montana_data$`...313`,
  Race = "Native Hawaiian and Other Pacific Islander Alone"
)

# Nebraska
nebraska_data <- filter(acs_data, Label == "Bachelor's degree or higher******")
bdh_nhopalone_nebraska <- tibble(
  Years = nebraska_data$Years,
  Percentage_nhop_women = nebraska_data$`...325`,
  Race = "Native Hawaiian and Other Pacific Islander Alone"
)

# Nevada
nevada_data <- filter(acs_data, Label == "Bachelor's degree or higher******")
bdh_nhopalone_nevada <- tibble(
  Years = nevada_data$Years,
  Percentage_nhop_women = nevada_data$`...337`,
  Race = "Native Hawaiian and Other Pacific Islander Alone"
)

# New Hampshire
newhampshire_data <- filter(acs_data, Label == "Bachelor's degree or higher******")
bdh_nhopalone_newhampshire <- tibble(
  Years = newhampshire_data$Years,
  Percentage_nhop_women = newhampshire_data$`...349`,
  Race = "Native Hawaiian and Other Pacific Islander Alone"
)

# New Jersey
newjersey_data <- filter(acs_data, Label == "Bachelor's degree or higher******")
bdh_nhopalone_newjersey <- tibble(
  Years = newjersey_data$Years,
  Percentage_nhop_women = newjersey_data$`...361`,
  Race = "Native Hawaiian and Other Pacific Islander Alone"
)

# New Mexico
newmexico_data <- filter(acs_data, Label == "Bachelor's degree or higher******")
bdh_nhopalone_newmexico <- tibble(
  Years = newmexico_data$Years,
  Percentage_nhop_women = newmexico_data$`...373`,
  Race = "Native Hawaiian and Other Pacific Islander Alone"
)

# New York
newyork_data <- filter(acs_data, Label == "Bachelor's degree or higher******")
bdh_nhopalone_newyork <- tibble(
  Years = newyork_data$Years,
  Percentage_nhop_women = newyork_data$`...385`,
  Race = "Native Hawaiian and Other Pacific Islander Alone"
)

# North Carolina
northcarolina_data <- filter(acs_data, Label == "Bachelor's degree or higher******")
bdh_nhopalone_northcarolina <- tibble(
  Years = northcarolina_data$Years,
  Percentage_nhop_women = northcarolina_data$`...397`,
  Race = "Native Hawaiian and Other Pacific Islander Alone"
)

# North Dakota
northdakota_data <- filter(acs_data, Label == "Bachelor's degree or higher******")
bdh_nhopalone_northdakota <- tibble(
  Years = northdakota_data$Years,
  Percentage_nhop_women = northdakota_data$`...409`,
  Race = "Native Hawaiian and Other Pacific Islander Alone"
)

# Ohio
ohio_data <- filter(acs_data, Label == "Bachelor's degree or higher******")
bdh_nhopalone_ohio <- tibble(
  Years = ohio_data$Years,
  Percentage_nhop_women = ohio_data$`...421`,
  Race = "Native Hawaiian and Other Pacific Islander Alone"
)

# Oklahoma
oklahoma_data <- filter(acs_data, Label == "Bachelor's degree or higher******")
bdh_nhopalone_oklahoma <- tibble(
  Years = oklahoma_data$Years,
  Percentage_nhop_women = oklahoma_data$`...433`,
  Race = "Native Hawaiian and Other Pacific Islander Alone"
)

# Oregon
oregon_data <- filter(acs_data, Label == "Bachelor's degree or higher******")
bdh_nhopalone_oregon <- tibble(
  Years = oregon_data$Years,
  Percentage_nhop_women = oregon_data$`...445`,
  Race = "Native Hawaiian and Other Pacific Islander Alone"
)

# Pennsylvania
pennsylvania_data <- filter(acs_data, Label == "Bachelor's degree or higher******")
bdh_nhopalone_pennsylvania <- tibble(
  Years = pennsylvania_data$Years,
  Percentage_nhop_women = pennsylvania_data$`...457`,
  Race = "Native Hawaiian and Other Pacific Islander Alone"
)

# Rhode Island
rhodeisland_data <- filter(acs_data, Label == "Bachelor's degree or higher******")
bdh_nhopalone_rhodeisland <- tibble(
  Years = rhodeisland_data$Years,
  Percentage_nhop_women = rhodeisland_data$`...469`,
  Race = "Native Hawaiian and Other Pacific Islander Alone"
)

# South Carolina
southcarolina_data <- filter(acs_data, Label == "Bachelor's degree or higher******")
bdh_nhopalone_southcarolina <- tibble(
  Years = southcarolina_data$Years,
  Percentage_nhop_women = southcarolina_data$`...481`,
  Race = "Native Hawaiian and Other Pacific Islander Alone"
)

# South Dakota
southdakota_data <- filter(acs_data, Label == "Bachelor's degree or higher******")
bdh_nhopalone_southdakota <- tibble(
  Years = southdakota_data$Years,
  Percentage_nhop_women = southdakota_data$`...493`,
  Race = "Native Hawaiian and Other Pacific Islander Alone"
)

# Tennessee
tennessee_data <- filter(acs_data, Label == "Bachelor's degree or higher******")
bdh_nhopalone_tennessee <- tibble(
  Years = tennessee_data$Years,
  Percentage_nhop_women = tennessee_data$`...505`,
  Race = "Native Hawaiian and Other Pacific Islander Alone"
)

# Texas
texas_data <- filter(acs_data, Label == "Bachelor's degree or higher******")
bdh_nhopalone_texas <- tibble(
  Years = texas_data$Years,
  Percentage_nhop_women = texas_data$`...517`,
  Race = "Native Hawaiian and Other Pacific Islander Alone"
)

# Utah
utah_data <- filter(acs_data, Label == "Bachelor's degree or higher******")
bdh_nhopalone_utah <- tibble(
  Years = utah_data$Years,
  Percentage_nhop_women = utah_data$`...529`,
  Race = "Native Hawaiian and Other Pacific Islander Alone"
)

# Vermont
vermont_data <- filter(acs_data, Label == "Bachelor's degree or higher******")
bdh_nhopalone_vermont <- tibble(
  Years = vermont_data$Years,
  Percentage_nhop_women = vermont_data$`...541`,
  Race = "Native Hawaiian and Other Pacific Islander Alone"
)

# Virginia
virginia_data <- filter(acs_data, Label == "Bachelor's degree or higher******")
bdh_nhopalone_virginia <- tibble(
  Years = virginia_data$Years,
  Percentage_nhop_women = virginia_data$`...553`,
  Race = "Native Hawaiian and Other Pacific Islander Alone"
)

# Washington
washington_data <- filter(acs_data, Label == "Bachelor's degree or higher******")
bdh_nhopalone_washington <- tibble(
  Years = washington_data$Years,
  Percentage_nhop_women = washington_data$`...565`,
  Race = "Native Hawaiian and Other Pacific Islander Alone"
)

# West Virginia
westvirginia_data <- filter(acs_data, Label == "Bachelor's degree or higher******")
bdh_nhopalone_westvirginia <- tibble(
  Years = westvirginia_data$Years,
  Percentage_nhop_women = westvirginia_data$`...577`,
  Race = "Native Hawaiian and Other Pacific Islander Alone"
)

# Wisconsin
wisconsin_data <- filter(acs_data, Label == "Bachelor's degree or higher******")
bdh_nhopalone_wisconsin <- tibble(
  Years = wisconsin_data$Years,
  Percentage_nhop_women = wisconsin_data$`...589`,
  Race = "Native Hawaiian and Other Pacific Islander Alone"
)

# Wyoming
wyoming_data <- filter(acs_data, Label == "Bachelor's degree or higher******")
bdh_nhopalone_wyoming <- tibble(
  Years = wyoming_data$Years,
  Percentage_nhop_women = wyoming_data$`...601`,
  Race = "Native Hawaiian and Other Pacific Islander Alone"
)

# Puerto Rico
puertorico_data <- filter(acs_data, Label == "Bachelor's degree or higher******")
bdh_nhopalone_puertorico <- tibble(
  Years = puertorico_data$Years,
  Percentage_nhop_women = puertorico_data$`Puerto...613`,
  Race = "Native Hawaiian and Other Pacific Islander Alone"
)

# Combine all states
combined_data_nhopalone <- bind_rows(
  bdh_nhopalone_alabama,
  bdh_nhopalone_alaska,
  bdh_nhopalone_arizona,
  bdh_nhopalone_arkansas,
  bdh_nhopalone_california,
  bdh_nhopalone_colorado,
  bdh_nhopalone_connecticut,
  bdh_nhopalone_delaware,
  bdh_nhopalone_florida,
  bdh_nhopalone_georgia,
  bdh_nhopalone_hawaii,
  bdh_nhopalone_idaho,
  bdh_nhopalone_illinois,
  bdh_nhopalone_indiana,
  bdh_nhopalone_iowa,
  bdh_nhopalone_kansas,
  bdh_nhopalone_kentucky,
  bdh_nhopalone_louisiana,
  bdh_nhopalone_maine,
  bdh_nhopalone_maryland,
  bdh_nhopalone_massachusetts,
  bdh_nhopalone_michigan,
  bdh_nhopalone_minnesota,
  bdh_nhopalone_mississippi,
  bdh_nhopalone_missouri,
  bdh_nhopalone_montana,
  bdh_nhopalone_nebraska,
  bdh_nhopalone_nevada,
  bdh_nhopalone_newhampshire,
  bdh_nhopalone_newjersey,
  bdh_nhopalone_newmexico,
  bdh_nhopalone_newyork,
  bdh_nhopalone_northcarolina,
  bdh_nhopalone_northdakota,
  bdh_nhopalone_ohio,
  bdh_nhopalone_oklahoma,
  bdh_nhopalone_oregon,
  bdh_nhopalone_pennsylvania,
  bdh_nhopalone_rhodeisland,
  bdh_nhopalone_southcarolina,
  bdh_nhopalone_southdakota,
  bdh_nhopalone_tennessee,
  bdh_nhopalone_texas,
  bdh_nhopalone_utah,
  bdh_nhopalone_vermont,
  bdh_nhopalone_virginia,
  bdh_nhopalone_washington,
  bdh_nhopalone_westvirginia,
  bdh_nhopalone_wisconsin,
  bdh_nhopalone_wyoming,
  bdh_nhopalone_puertorico
)

print(combined_data_nhopalone)

```

7.  **Female, Some other race Alone, Across all U.S. States + Puerto Rico (Status: Cleaned)**

```{r}


library(dplyr)
library(readr)
library(tibble)


acs_data <- read_excel("dataset/acsfinale.xlsx")



# Alabama
alabama_data <- filter(acs_data, Label == "Bachelor's degree or higher*******")
bdh_sor_alabama <- tibble(
  Years = alabama_data$Years,
  Percentage_sor_women = alabama_data$`...1`,
  Race = "Some other race Alone"
)

# Alaska
alaska_data <- filter(acs_data, Label == "Bachelor's degree or higher*******")
bdh_sor_alaska <- tibble(
  Years = alaska_data$Years,
  Percentage_sor_women = alaska_data$`...13`,
  Race = "Some other race Alone"
)

# Arizona
arizona_data <- filter(acs_data, Label == "Bachelor's degree or higher*******")
bdh_sor_arizona <- tibble(
  Years = arizona_data$Years,
  Percentage_sor_women = arizona_data$`...25`,
  Race = "Some other race Alone"
)

# Arkansas
arkansas_data <- filter(acs_data, Label == "Bachelor's degree or higher*******")
bdh_sor_arkansas <- tibble(
  Years = arkansas_data$Years,
  Percentage_sor_women = arkansas_data$`...37`,
  Race = "Some other race Alone"
)

# California
california_data <- filter(acs_data, Label == "Bachelor's degree or higher*******")
bdh_sor_california <- tibble(
  Years = california_data$Years,
  Percentage_sor_women = california_data$`...49`,
  Race = "Some other race Alone"
)

# Colorado
colorado_data <- filter(acs_data, Label == "Bachelor's degree or higher*******")
bdh_sor_colorado <- tibble(
  Years = colorado_data$Years,
  Percentage_sor_women = colorado_data$`...61`,
  Race = "Some other race Alone"
)

# Connecticut
connecticut_data <- filter(acs_data, Label == "Bachelor's degree or higher*******")
bdh_sor_connecticut <- tibble(
  Years = connecticut_data$Years,
  Percentage_sor_women = connecticut_data$`...73`,
  Race = "Some other race Alone"
)

# Delaware
delaware_data <- filter(acs_data, Label == "Bachelor's degree or higher*******")
bdh_sor_delaware <- tibble(
  Years = delaware_data$Years,
  Percentage_sor_women = delaware_data$`...85`,
  Race = "Some other race Alone"
)

# Florida
florida_data <- filter(acs_data, Label == "Bachelor's degree or higher*******")
bdh_sor_florida <- tibble(
  Years = florida_data$Years,
  Percentage_sor_women = florida_data$`...97`,
  Race = "Some other race Alone"
)

# Georgia
georgia_data <- filter(acs_data, Label == "Bachelor's degree or higher*******")
bdh_sor_georgia <- tibble(
  Years = georgia_data$Years,
  Percentage_sor_women = georgia_data$`...109`,
  Race = "Some other race Alone"
)

# Hawaii
hawaii_data <- filter(acs_data, Label == "Bachelor's degree or higher*******")
bdh_sor_hawaii <- tibble(
  Years = hawaii_data$Years,
  Percentage_sor_women = hawaii_data$`...121`,
  Race = "Some other race Alone"
)

# Idaho
idaho_data <- filter(acs_data, Label == "Bachelor's degree or higher*******")
bdh_sor_idaho <- tibble(
  Years = idaho_data$Years,
  Percentage_sor_women = idaho_data$`...133`,
  Race = "Some other race Alone"
)

# Illinois
illinois_data <- filter(acs_data, Label == "Bachelor's degree or higher*******")
bdh_sor_illinois <- tibble(
  Years = illinois_data$Years,
  Percentage_sor_women = illinois_data$`...145`,
  Race = "Some other race Alone"
)

# Indiana
indiana_data <- filter(acs_data, Label == "Bachelor's degree or higher*******")
bdh_sor_indiana <- tibble(
  Years = indiana_data$Years,
  Percentage_sor_women = indiana_data$`...157`,
  Race = "Some other race Alone"
)

# Iowa
iowa_data <- filter(acs_data, Label == "Bachelor's degree or higher*******")
bdh_sor_iowa <- tibble(
  Years = iowa_data$Years,
  Percentage_sor_women = iowa_data$`...169`,
  Race = "Some other race Alone"
)

# Kansas
kansas_data <- filter(acs_data, Label == "Bachelor's degree or higher*******")
bdh_sor_kansas <- tibble(
  Years = kansas_data$Years,
  Percentage_sor_women = kansas_data$`...181`,
  Race = "Some other race Alone"
)

# Kentucky
kentucky_data <- filter(acs_data, Label == "Bachelor's degree or higher*******")
bdh_sor_kentucky <- tibble(
  Years = kentucky_data$Years,
  Percentage_sor_women = kentucky_data$`...193`,
  Race = "Some other race Alone"
)

# Louisiana
louisiana_data <- filter(acs_data, Label == "Bachelor's degree or higher*******")
bdh_sor_louisiana <- tibble(
  Years = louisiana_data$Years,
  Percentage_sor_women = louisiana_data$`...205`,
  Race = "Some other race Alone"
)

# Maine
maine_data <- filter(acs_data, Label == "Bachelor's degree or higher*******")
bdh_sor_maine <- tibble(
  Years = maine_data$Years,
  Percentage_sor_women = maine_data$`...217`,
  Race = "Some other race Alone"
)

# Maryland
maryland_data <- filter(acs_data, Label == "Bachelor's degree or higher*******")
bdh_sor_maryland <- tibble(
  Years = maryland_data$Years,
  Percentage_sor_women = maryland_data$`...229`,
  Race = "Some other race Alone"
)

# Massachusetts
massachusetts_data <- filter(acs_data, Label == "Bachelor's degree or higher*******")
bdh_sor_massachusetts <- tibble(
  Years = massachusetts_data$Years,
  Percentage_sor_women = massachusetts_data$`...241`,
  Race = "Some other race Alone"
)

# Michigan
michigan_data <- filter(acs_data, Label == "Bachelor's degree or higher*******")
bdh_sor_michigan <- tibble(
  Years = michigan_data$Years,
  Percentage_sor_women = michigan_data$`...253`,
  Race = "Some other race Alone"
)

# Minnesota
minnesota_data <- filter(acs_data, Label == "Bachelor's degree or higher*******")
bdh_sor_minnesota <- tibble(
  Years = minnesota_data$Years,
  Percentage_sor_women = minnesota_data$`...265`,
  Race = "Some other race Alone"
)

# Mississippi
mississippi_data <- filter(acs_data, Label == "Bachelor's degree or higher*******")
bdh_sor_mississippi <- tibble(
  Years = mississippi_data$Years,
  Percentage_sor_women = mississippi_data$`...277`,
  Race = "Some other race Alone"
)

# Missouri
missouri_data <- filter(acs_data, Label == "Bachelor's degree or higher*******")
bdh_sor_missouri <- tibble(
  Years = missouri_data$Years,
  Percentage_sor_women = missouri_data$`...289`,
  Race = "Some other race Alone"
)

# Montana
montana_data <- filter(acs_data, Label == "Bachelor's degree or higher*******")
bdh_sor_montana <- tibble(
  Years = montana_data$Years,
  Percentage_sor_women = montana_data$`...301`,
  Race = "Some other race Alone"
)

# Nebraska
nebraska_data <- filter(acs_data, Label == "Bachelor's degree or higher*******")
bdh_sor_nebraska <- tibble(
  Years = nebraska_data$Years,
  Percentage_sor_women = nebraska_data$`...313`,
  Race = "Some other race Alone"
)

# Nevada
nevada_data <- filter(acs_data, Label == "Bachelor's degree or higher*******")
bdh_sor_nevada <- tibble(
  Years = nevada_data$Years,
  Percentage_sor_women = nevada_data$`...325`,
  Race = "Some other race Alone"
)

# New Hampshire
newhampshire_data <- filter(acs_data, Label == "Bachelor's degree or higher*******")
bdh_sor_newhampshire <- tibble(
  Years = newhampshire_data$Years,
  Percentage_sor_women = newhampshire_data$`...337`,
  Race = "Some other race Alone"
)

# New Jersey
newjersey_data <- filter(acs_data, Label == "Bachelor's degree or higher*******")
bdh_sor_newjersey <- tibble(
  Years = newjersey_data$Years,
  Percentage_sor_women = newjersey_data$`...349`,
  Race = "Some other race Alone"
)

# New Mexico
newmexico_data <- filter(acs_data, Label == "Bachelor's degree or higher*******")
bdh_sor_newmexico <- tibble(
  Years = newmexico_data$Years,
  Percentage_sor_women = newmexico_data$`...361`,
  Race = "Some other race Alone"
)

# New York
newyork_data <- filter(acs_data, Label == "Bachelor's degree or higher*******")
bdh_sor_newyork <- tibble(
  Years = newyork_data$Years,
  Percentage_sor_women = newyork_data$`...373`,
  Race = "Some other race Alone"
)

# North Carolina
northcarolina_data <- filter(acs_data, Label == "Bachelor's degree or higher*******")
bdh_sor_northcarolina <- tibble(
  Years = northcarolina_data$Years,
  Percentage_sor_women = northcarolina_data$`...385`,
  Race = "Some other race Alone"
)

# North Dakota
northdakota_data <- filter(acs_data, Label == "Bachelor's degree or higher*******")
bdh_sor_northdakota <- tibble(
  Years = northdakota_data$Years,
  Percentage_sor_women = northdakota_data$`...397`,
  Race = "Some other race Alone"
)

# Ohio
ohio_data <- filter(acs_data, Label == "Bachelor's degree or higher*******")
bdh_sor_ohio <- tibble(
  Years = ohio_data$Years,
  Percentage_sor_women = ohio_data$`...409`,
  Race = "Some other race Alone"
)

# Oklahoma
oklahoma_data <- filter(acs_data, Label == "Bachelor's degree or higher*******")
bdh_sor_oklahoma <- tibble(
  Years = oklahoma_data$Years,
  Percentage_sor_women = oklahoma_data$`...421`,
  Race = "Some other race Alone"
)

# Oregon
oregon_data <- filter(acs_data, Label == "Bachelor's degree or higher*******")
bdh_sor_oregon <- tibble(
  Years = oregon_data$Years,
  Percentage_sor_women = oregon_data$`...433`,
  Race = "Some other race Alone"
)

# Pennsylvania
pennsylvania_data <- filter(acs_data, Label == "Bachelor's degree or higher*******")
bdh_sor_pennsylvania <- tibble(
  Years = pennsylvania_data$Years,
  Percentage_sor_women = pennsylvania_data$`...445`,
  Race = "Some other race Alone"
)

# Rhode Island
rhodeisland_data <- filter(acs_data, Label == "Bachelor's degree or higher*******")
bdh_sor_rhodeisland <- tibble(
  Years = rhodeisland_data$Years,
  Percentage_sor_women = rhodeisland_data$`...457`,
  Race = "Some other race Alone"
)

# South Carolina
southcarolina_data <- filter(acs_data, Label == "Bachelor's degree or higher*******")
bdh_sor_southcarolina <- tibble(
  Years = southcarolina_data$Years,
  Percentage_sor_women = southcarolina_data$`...469`,
  Race = "Some other race Alone"
)

# South Dakota
southdakota_data <- filter(acs_data, Label == "Bachelor's degree or higher*******")
bdh_sor_southdakota <- tibble(
  Years = southdakota_data$Years,
  Percentage_sor_women = southdakota_data$`...481`,
  Race = "Some other race Alone"
)

# Tennessee
tennessee_data <- filter(acs_data, Label == "Bachelor's degree or higher*******")
bdh_sor_tennessee <- tibble(
  Years = tennessee_data$Years,
  Percentage_sor_women = tennessee_data$`...493`,
  Race = "Some other race Alone"
)

# Texas
texas_data <- filter(acs_data, Label == "Bachelor's degree or higher*******")
bdh_sor_texas <- tibble(
  Years = texas_data$Years,
  Percentage_sor_women = texas_data$`...505`,
  Race = "Some other race Alone"
)

# Utah
utah_data <- filter(acs_data, Label == "Bachelor's degree or higher*******")
bdh_sor_utah <- tibble(
  Years = utah_data$Years,
  Percentage_sor_women = utah_data$`...517`,
  Race = "Some other race Alone"
)

# Vermont
vermont_data <- filter(acs_data, Label == "Bachelor's degree or higher*******")
bdh_sor_vermont <- tibble(
  Years = vermont_data$Years,
  Percentage_sor_women = vermont_data$`...529`,
  Race = "Some other race Alone"
)

# Virginia
virginia_data <- filter(acs_data, Label == "Bachelor's degree or higher*******")
bdh_sor_virginia <- tibble(
  Years = virginia_data$Years,
  Percentage_sor_women = virginia_data$`...541`,
  Race = "Some other race Alone"
)

# Washington
washington_data <- filter(acs_data, Label == "Bachelor's degree or higher*******")
bdh_sor_washington <- tibble(
  Years = washington_data$Years,
  Percentage_sor_women = washington_data$`...553`,
  Race = "Some other race Alone"
)

# West Virginia
westvirginia_data <- filter(acs_data, Label == "Bachelor's degree or higher*******")
bdh_sor_westvirginia <- tibble(
  Years = westvirginia_data$Years,
  Percentage_sor_women = westvirginia_data$`...565`,
  Race = "Some other race Alone"
)

# Wisconsin
wisconsin_data <- filter(acs_data, Label == "Bachelor's degree or higher*******")
bdh_sor_wisconsin <- tibble(
  Years = wisconsin_data$Years,
  Percentage_sor_women = wisconsin_data$`...577`,
  Race = "Some other race Alone"
)

# Wyoming
wyoming_data <- filter(acs_data, Label == "Bachelor's degree or higher*******")
bdh_sor_wyoming <- tibble(
  Years = wyoming_data$Years,
  Percentage_sor_women = wyoming_data$`...589`,
  Race = "Some other race Alone"
)

# Puerto Rico
puertorico_data <- filter(acs_data, Label == "Bachelor's degree or higher*******")
bdh_sor_puertorico <- tibble(
  Years = puertorico_data$Years,
  Percentage_sor_women = puertorico_data$`...601`,
  Race = "Some other race Alone"
)

# Combine all states
combined_data_sor <- bind_rows(
  bdh_sor_alabama,
  bdh_sor_alaska,
  bdh_sor_arizona,
  bdh_sor_arkansas,
  bdh_sor_california,
  bdh_sor_colorado,
  bdh_sor_connecticut,
  bdh_sor_delaware,
  bdh_sor_florida,
  bdh_sor_georgia,
  bdh_sor_hawaii,
  bdh_sor_idaho,
  bdh_sor_illinois,
  bdh_sor_indiana,
  bdh_sor_iowa,
  bdh_sor_kansas,
  bdh_sor_kentucky,
  bdh_sor_louisiana,
  bdh_sor_maine,
  bdh_sor_maryland,
  bdh_sor_massachusetts,
  bdh_sor_michigan,
  bdh_sor_minnesota,
  bdh_sor_mississippi,
  bdh_sor_missouri,
  bdh_sor_montana,
  bdh_sor_nebraska,
  bdh_sor_nevada,
  bdh_sor_newhampshire,
  bdh_sor_newjersey,
  bdh_sor_newmexico,
  bdh_sor_newyork,
  bdh_sor_northcarolina,
  bdh_sor_northdakota,
  bdh_sor_ohio,
  bdh_sor_oklahoma,
  bdh_sor_oregon,
  bdh_sor_pennsylvania,
  bdh_sor_rhodeisland,
  bdh_sor_southcarolina,
  bdh_sor_southdakota,
  bdh_sor_tennessee,
  bdh_sor_texas,
  bdh_sor_utah,
  bdh_sor_vermont,
  bdh_sor_virginia,
  bdh_sor_washington,
  bdh_sor_westvirginia,
  bdh_sor_wisconsin,
  bdh_sor_wyoming,
  bdh_sor_puertorico
)


print(combined_data_sor)


```

8.  **Female, Two or more races, Across all U.S. States + Puerto Rico (Status: Cleaned)**

```{r}
library(readxl)
library(dplyr)
library(tibble)

acs_data <- read_excel("dataset/acsfinale.xlsx")

# Alabama
alabama_data <- filter(acs_data, Label == "Bachelor's degree or higher********")
bdh_tmr_alabama <- tibble(
  Years = alabama_data$Years,
  Percentage_tmr_women = alabama_data$`Alabama...13`,
  Race = "Two or more races"
)

# Alaska
alaska_data <- filter(acs_data, Label == "Bachelor's degree or higher********")
bdh_tmr_alaska <- tibble(
  Years = alaska_data$Years,
  Percentage_tmr_women = alaska_data$`...25`,
  Race = "Two or more races"
)

# Arizona
arizona_data <- filter(acs_data, Label == "Bachelor's degree or higher********")
bdh_tmr_arizona <- tibble(
  Years = arizona_data$Years,
  Percentage_tmr_women = arizona_data$`...37`,
  Race = "Two or more races"
)

# Arkansas
arkansas_data <- filter(acs_data, Label == "Bachelor's degree or higher********")
bdh_tmr_arkansas <- tibble(
  Years = arkansas_data$Years,
  Percentage_tmr_women = arkansas_data$`...49`,
  Race = "Two or more races"
)

# California
california_data <- filter(acs_data, Label == "Bachelor's degree or higher********")
bdh_tmr_california <- tibble(
  Years = california_data$Years,
  Percentage_tmr_women = california_data$`...61`,
  Race = "Two or more races"
)

# Colorado
colorado_data <- filter(acs_data, Label == "Bachelor's degree or higher********")
bdh_tmr_colorado <- tibble(
  Years = colorado_data$Years,
  Percentage_tmr_women = colorado_data$`...73`,
  Race = "Two or more races"
)

# Connecticut
connecticut_data <- filter(acs_data, Label == "Bachelor's degree or higher********")
bdh_tmr_connecticut <- tibble(
  Years = connecticut_data$Years,
  Percentage_tmr_women = connecticut_data$`...85`,
  Race = "Two or more races"
)

# Delaware
delaware_data <- filter(acs_data, Label == "Bachelor's degree or higher********")
bdh_tmr_delaware <- tibble(
  Years = delaware_data$Years,
  Percentage_tmr_women = delaware_data$`...97`,
  Race = "Two or more races"
)

# Florida
florida_data <- filter(acs_data, Label == "Bachelor's degree or higher********")
bdh_tmr_florida <- tibble(
  Years = florida_data$Years,
  Percentage_tmr_women = florida_data$`...109`,
  Race = "Two or more races"
)

# Georgia
georgia_data <- filter(acs_data, Label == "Bachelor's degree or higher********")
bdh_tmr_georgia <- tibble(
  Years = georgia_data$Years,
  Percentage_tmr_women = georgia_data$`...121`,
  Race = "Two or more races"
)

# Hawaii
hawaii_data <- filter(acs_data, Label == "Bachelor's degree or higher********")
bdh_tmr_hawaii <- tibble(
  Years = hawaii_data$Years,
  Percentage_tmr_women = hawaii_data$`...133`,
  Race = "Two or more races"
)

# Idaho
idaho_data <- filter(acs_data, Label == "Bachelor's degree or higher********")
bdh_tmr_idaho <- tibble(
  Years = idaho_data$Years,
  Percentage_tmr_women = idaho_data$`...145`,
  Race = "Two or more races"
)

# Illinois
illinois_data <- filter(acs_data, Label == "Bachelor's degree or higher********")
bdh_tmr_illinois <- tibble(
  Years = illinois_data$Years,
  Percentage_tmr_women = illinois_data$`...157`,
  Race = "Two or more races"
)

# Indiana
indiana_data <- filter(acs_data, Label == "Bachelor's degree or higher********")
bdh_tmr_indiana <- tibble(
  Years = indiana_data$Years,
  Percentage_tmr_women = indiana_data$`...169`,
  Race = "Two or more races"
)

# Iowa
iowa_data <- filter(acs_data, Label == "Bachelor's degree or higher********")
bdh_tmr_iowa <- tibble(
  Years = iowa_data$Years,
  Percentage_tmr_women = iowa_data$`...181`,
  Race = "Two or more races"
)

# Kansas
kansas_data <- filter(acs_data, Label == "Bachelor's degree or higher********")
bdh_tmr_kansas <- tibble(
  Years = kansas_data$Years,
  Percentage_tmr_women = kansas_data$`...193`,
  Race = "Two or more races"
)

# Kentucky
kentucky_data <- filter(acs_data, Label == "Bachelor's degree or higher********")
bdh_tmr_kentucky <- tibble(
  Years = kentucky_data$Years,
  Percentage_tmr_women = kentucky_data$`...205`,
  Race = "Two or more races"
)

# Louisiana
louisiana_data <- filter(acs_data, Label == "Bachelor's degree or higher********")
bdh_tmr_louisiana <- tibble(
  Years = louisiana_data$Years,
  Percentage_tmr_women = louisiana_data$`...217`,
  Race = "Two or more races"
)

# Maine
maine_data <- filter(acs_data, Label == "Bachelor's degree or higher********")
bdh_tmr_maine <- tibble(
  Years = maine_data$Years,
  Percentage_tmr_women = maine_data$`...229`,
  Race = "Two or more races"
)

# Maryland
maryland_data <- filter(acs_data, Label == "Bachelor's degree or higher********")
bdh_tmr_maryland <- tibble(
  Years = maryland_data$Years,
  Percentage_tmr_women = maryland_data$`...241`,
  Race = "Two or more races"
)

# Massachusetts
massachusetts_data <- filter(acs_data, Label == "Bachelor's degree or higher********")
bdh_tmr_massachusetts <- tibble(
  Years = massachusetts_data$Years,
  Percentage_tmr_women = massachusetts_data$`...253`,
  Race = "Two or more races"
)

# Michigan
michigan_data <- filter(acs_data, Label == "Bachelor's degree or higher********")
bdh_tmr_michigan <- tibble(
  Years = michigan_data$Years,
  Percentage_tmr_women = michigan_data$`...265`,
  Race = "Two or more races"
)

# Minnesota
minnesota_data <- filter(acs_data, Label == "Bachelor's degree or higher********")
bdh_tmr_minnesota <- tibble(
  Years = minnesota_data

$Years,
  Percentage_tmr_women = minnesota_data$`...277`,
  Race = "Two or more races"
)

# Mississippi
mississippi_data <- filter(acs_data, Label == "Bachelor's degree or higher********")
bdh_tmr_mississippi <- tibble(
  Years = mississippi_data$Years,
  Percentage_tmr_women = mississippi_data$`...289`,
  Race = "Two or more races"
)

# Missouri
missouri_data <- filter(acs_data, Label == "Bachelor's degree or higher********")
bdh_tmr_missouri <- tibble(
  Years = missouri_data$Years,
  Percentage_tmr_women = missouri_data$`...301`,
  Race = "Two or more races"
)

# Montana
montana_data <- filter(acs_data, Label == "Bachelor's degree or higher********")
bdh_tmr_montana <- tibble(
  Years = montana_data$Years,
  Percentage_tmr_women = montana_data$`...313`,
  Race = "Two or more races"
)

# Nebraska
nebraska_data <- filter(acs_data, Label == "Bachelor's degree or higher********")
bdh_tmr_nebraska <- tibble(
  Years = nebraska_data$Years,
  Percentage_tmr_women = nebraska_data$`...325`,
  Race = "Two or more races"
)

# Nevada
nevada_data <- filter(acs_data, Label == "Bachelor's degree or higher********")
bdh_tmr_nevada <- tibble(
  Years = nevada_data$Years,
  Percentage_tmr_women = nevada_data$`...337`,
  Race = "Two or more races"
)

# New Hampshire
new_hampshire_data <- filter(acs_data, Label == "Bachelor's degree or higher********")
bdh_tmr_new_hampshire <- tibble(
  Years = new_hampshire_data$Years,
  Percentage_tmr_women = new_hampshire_data$`...349`,
  Race = "Two or more races"
)

# New Jersey
new_jersey_data <- filter(acs_data, Label == "Bachelor's degree or higher********")
bdh_tmr_new_jersey <- tibble(
  Years = new_jersey_data$Years,
  Percentage_tmr_women = new_jersey_data$`...361`,
  Race = "Two or more races"
)

# New Mexico
new_mexico_data <- filter(acs_data, Label == "Bachelor's degree or higher********")
bdh_tmr_new_mexico <- tibble(
  Years = new_mexico_data$Years,
  Percentage_tmr_women = new_mexico_data$`...373`,
  Race = "Two or more races"
)

# New York
new_york_data <- filter(acs_data, Label == "Bachelor's degree or higher********")
bdh_tmr_new_york <- tibble(
  Years = new_york_data$Years,
  Percentage_tmr_women = new_york_data$`...385`,
  Race = "Two or more races"
)

# North Carolina
north_carolina_data <- filter(acs_data, Label == "Bachelor's degree or higher********")
bdh_tmr_north_carolina <- tibble(
  Years = north_carolina_data$Years,
  Percentage_tmr_women = north_carolina_data$`...397`,
  Race = "Two or more races"
)

# North Dakota
north_dakota_data <- filter(acs_data, Label == "Bachelor's degree or higher********")
bdh_tmr_north_dakota <- tibble(
  Years = north_dakota_data$Years,
  Percentage_tmr_women = north_dakota_data$`...409`,
  Race = "Two or more races"
)

# Ohio
ohio_data <- filter(acs_data, Label == "Bachelor's degree or higher********")
bdh_tmr_ohio <- tibble(
  Years = ohio_data$Years,
  Percentage_tmr_women = ohio_data$`...421`,
  Race = "Two or more races"
)

# Oklahoma
oklahoma_data <- filter(acs_data, Label == "Bachelor's degree or higher********")
bdh_tmr_oklahoma <- tibble(
  Years = oklahoma_data$Years,
  Percentage_tmr_women = oklahoma_data$`...433`,
  Race = "Two or more races"
)

# Oregon
oregon_data <- filter(acs_data, Label == "Bachelor's degree or higher********")
bdh_tmr_oregon <- tibble(
  Years = oregon_data$Years,
  Percentage_tmr_women = oregon_data$`...445`,
  Race = "Two or more races"
)

# Pennsylvania
pennsylvania_data <- filter(acs_data, Label == "Bachelor's degree or higher********")
bdh_tmr_pennsylvania <- tibble(
  Years = pennsylvania_data$Years,
  Percentage_tmr_women = pennsylvania_data$`...457`,
  Race = "Two or more races"
)

# Rhode Island
rhode_island_data <- filter(acs_data, Label == "Bachelor's degree or higher********")
bdh_tmr_rhode_island <- tibble(
  Years = rhode_island_data$Years,
  Percentage_tmr_women = rhode_island_data$`...469`,
  Race = "Two or more races"
)

# South Carolina
south_carolina_data <- filter(acs_data, Label == "Bachelor's degree or higher********")
bdh_tmr_south_carolina <- tibble(
  Years = south_carolina_data$Years,
  Percentage_tmr_women = south_carolina_data$`...481`,
  Race = "Two or more races"
)

# South Dakota
south_dakota_data <- filter(acs_data, Label == "Bachelor's degree or higher********")
bdh_tmr_south_dakota <- tibble(
  Years = south_dakota_data$Years,
  Percentage_tmr_women = south_dakota_data$`...493`,
  Race = "Two or more races"
)

# Tennessee
tennessee_data <- filter(acs_data, Label == "Bachelor's degree or higher********")
bdh_tmr_tennessee <- tibble(
  Years = tennessee_data$Years,
  Percentage_tmr_women = tennessee_data$`...505`,
  Race = "Two or more races"
)

# Texas
texas_data <- filter(acs_data, Label == "Bachelor's degree or higher********")
bdh_tmr_texas <- tibble(
  Years = texas_data$Years,
  Percentage_tmr_women = texas_data$`...517`,
  Race = "Two or more races"
)

# Utah
utah_data <- filter(acs_data, Label == "Bachelor's degree or higher********")
bdh_tmr_utah <- tibble(
  Years = utah_data$Years,
  Percentage_tmr_women = utah_data$`...529`,
  Race = "Two or more races"
)

# Vermont
vermont_data <- filter(acs_data, Label == "Bachelor's degree or higher********")
bdh_tmr_vermont <- tibble(
  Years = vermont_data$Years,
  Percentage_tmr_women

 = vermont_data$`...541`,
  Race = "Two or more races"
)

# Virginia
virginia_data <- filter(acs_data, Label == "Bachelor's degree or higher********")
bdh_tmr_virginia <- tibble(
  Years = virginia_data$Years,
  Percentage_tmr_women = virginia_data$`...553`,
  Race = "Two or more races"
)

# Washington
washington_data <- filter(acs_data, Label == "Bachelor's degree or higher********")
bdh_tmr_washington <- tibble(
  Years = washington_data$Years,
  Percentage_tmr_women = washington_data$`...565`,
  Race = "Two or more races"
)

# West Virginia
west_virginia_data <- filter(acs_data, Label == "Bachelor's degree or higher********")
bdh_tmr_west_virginia <- tibble(
  Years = west_virginia_data$Years,
  Percentage_tmr_women = west_virginia_data$`...577`,
  Race = "Two or more races"
)

# Wisconsin
wisconsin_data <- filter(acs_data, Label == "Bachelor's degree or higher********")
bdh_tmr_wisconsin <- tibble(
  Years = wisconsin_data$Years,
  Percentage_tmr_women = wisconsin_data$`...589`,
  Race = "Two or more races"
)

# Wyoming
wyoming_data <- filter(acs_data, Label == "Bachelor's degree or higher********")
bdh_tmr_wyoming <- tibble(
  Years = wyoming_data$Years,
  Percentage_tmr_women = wyoming_data$`...601`,
  Race = "Two or more races"
)

# Puerto Rico
puerto_rico_data <- filter(acs_data, Label == "Bachelor's degree or higher********")
bdh_tmr_puerto_rico <- tibble(
  Years = puerto_rico_data$Years,
  Percentage_tmr_women = puerto_rico_data$`...613`,
  Race = "Two or more races"
)


combined_data_tmr <- bind_rows(
  bdh_tmr_alabama,
  bdh_tmr_alaska,
  bdh_tmr_arizona,
  bdh_tmr_arkansas,
  bdh_tmr_california,
  bdh_tmr_colorado,
  bdh_tmr_connecticut,
  bdh_tmr_delaware,
  bdh_tmr_florida,
  bdh_tmr_georgia,
  bdh_tmr_hawaii,
  bdh_tmr_idaho,
  bdh_tmr_illinois,
  bdh_tmr_indiana,
  bdh_tmr_iowa,
  bdh_tmr_kansas,
  bdh_tmr_kentucky,
  bdh_tmr_louisiana,
  bdh_tmr_maine,
  bdh_tmr_maryland,
  bdh_tmr_massachusetts,
  bdh_tmr_michigan,
  bdh_tmr_minnesota,
  bdh_tmr_mississippi,
  bdh_tmr_missouri,
  bdh_tmr_montana,
  bdh_tmr_nebraska,
  bdh_tmr_nevada,
  bdh_tmr_new_hampshire,
  bdh_tmr_new_jersey,
  bdh_tmr_new_mexico,
  bdh_tmr_new_york,
  bdh_tmr_north_carolina,
  bdh_tmr_north_dakota,
  bdh_tmr_ohio,
  bdh_tmr_oklahoma,
  bdh_tmr_oregon,
  bdh_tmr_pennsylvania,
  bdh_tmr_rhode_island,
  bdh_tmr_south_carolina,
  bdh_tmr_south_dakota,
  bdh_tmr_tennessee,
  bdh_tmr_texas,
  bdh_tmr_utah,
  bdh_tmr_vermont,
  bdh_tmr_virginia,
  bdh_tmr_washington,
  bdh_tmr_west_virginia,
  bdh_tmr_wisconsin,
  bdh_tmr_wyoming,
  bdh_tmr_puerto_rico
)


print(combined_data_tmr)

```

9.  **Female, Hispanic or Latino Origin, Across all U.S. States + Puerto Rico (Status: Cleaned)**

```{r}
library(readxl)
library(dplyr)
library(tibble)


acs_data <- read_excel("dataset/acsfinale.xlsx")

#Puerto Rico
puertorico_data <- filter(acs_data, Label == "Bachelor's degree or higher*********")
bdh_hloorigin_puertorico <- tibble(
  Years = puertorico_data$Years,
  Percentage_hloorigin_women = puertorico_data$`Puerto Rico...613`,
  Race = "Hispanic or Latino Origin"
)

# Alabama
alabama_data <- filter(acs_data, Label == "Bachelor's degree or higher*********")
bdh_hloorigin_alabama <- tibble(
  Years = alabama_data$Years,
  Percentage_hloorigin_women = alabama_data$`...5`,
  Race = "Hispanic or Latino Origin"
)

# Alaska
alaska_data <- filter(acs_data, Label == "Bachelor's degree or higher*********")
bdh_hloorigin_alaska <- tibble(
  Years = alaska_data$Years,
  Percentage_hloorigin_women = alaska_data$`...17`,
  Race = "Hispanic or Latino Origin"
)

# Arizona
arizona_data <- filter(acs_data, Label == "Bachelor's degree or higher*********")
bdh_hloorigin_arizona <- tibble(
  Years = arizona_data$Years,
  Percentage_hloorigin_women = arizona_data$`...29`,
  Race = "Hispanic or Latino Origin"
)

# Arkansas
arkansas_data <- filter(acs_data, Label == "Bachelor's degree or higher*********")
bdh_hloorigin_arkansas <- tibble(
  Years = arkansas_data$Years,
  Percentage_hloorigin_women = arkansas_data$`...41`,
  Race = "Hispanic or Latino Origin"
)

# California
california_data <- filter(acs_data, Label == "Bachelor's degree or higher*********")
bdh_hloorigin_california <- tibble(
  Years = california_data$Years,
  Percentage_hloorigin_women = california_data$`...53`,
  Race = "Hispanic or Latino Origin"
)

# Colorado
colorado_data <- filter(acs_data, Label == "Bachelor's degree or higher*********")
bdh_hloorigin_colorado <- tibble(
  Years = colorado_data$Years,
  Percentage_hloorigin_women = colorado_data$`...65`,
  Race = "Hispanic or Latino Origin"
)

# Connecticut
connecticut_data <- filter(acs_data, Label == "Bachelor's degree or higher*********")
bdh_hloorigin_connecticut <- tibble(
  Years = connecticut_data$Years,
  Percentage_hloorigin_women = connecticut_data$`...77`,
  Race = "Hispanic or Latino Origin"
)

# Delaware
delaware_data <- filter(acs_data, Label == "Bachelor's degree or higher*********")
bdh_hloorigin_delaware <- tibble(
  Years = delaware_data$Years,
  Percentage_hloorigin_women = delaware_data$`...89`,
  Race = "Hispanic or Latino Origin"
)

# Florida
florida_data <- filter(acs_data, Label == "Bachelor's degree or higher*********")
bdh_hloorigin_florida <- tibble(
  Years = florida_data$Years,
  Percentage_hloorigin_women = florida_data$`...101`,
  Race = "Hispanic or Latino Origin"
)

# Georgia
georgia_data <- filter(acs_data, Label == "Bachelor's degree or higher*********")
bdh_hloorigin_georgia <- tibble(
  Years = georgia_data$Years,
  Percentage_hloorigin_women = georgia_data$`...113`,
  Race = "Hispanic or Latino Origin"
)

# Hawaii
hawaii_data <- filter(acs_data, Label == "Bachelor's degree or higher*********")
bdh_hloorigin_hawaii <- tibble(
  Years = hawaii_data$Years,
  Percentage_hloorigin_women = hawaii_data$`...125`,
  Race = "Hispanic or Latino Origin"
)

# Idaho
idaho_data <- filter(acs_data, Label == "Bachelor's degree or higher*********")
bdh_hloorigin_idaho <- tibble(
  Years = idaho_data$Years,
  Percentage_hloorigin_women = idaho_data$`...137`,
  Race = "Hispanic or Latino Origin"
)

# Illinois
illinois_data <- filter(acs_data, Label == "Bachelor's degree or higher*********")
bdh_hloorigin_illinois <- tibble(
  Years = illinois_data$Years,
  Percentage_hloorigin_women = illinois_data$`...149`,
  Race = "Hispanic or Latino Origin"
)

# Indiana
indiana_data <- filter(acs_data, Label == "Bachelor's degree or higher*********")
bdh_hloorigin_indiana <- tibble(
  Years = indiana_data$Years,
  Percentage_hloorigin_women = indiana_data$`...161`,
  Race = "Hispanic or Latino Origin"
)

# Iowa
iowa_data <- filter(acs_data, Label == "Bachelor's degree or higher*********")
bdh_hloorigin_iowa <- tibble(
  Years = iowa_data$Years,
  Percentage_hloorigin_women = iowa_data$`...173`,
  Race = "Hispanic or Latino Origin"
)

# Kansas
kansas_data <- filter(acs_data, Label == "Bachelor's degree or higher*********")
bdh_hloorigin_kansas <- tibble(
  Years = kansas_data$Years,
  Percentage_hloorigin_women = kansas_data$`...185`,
  Race = "Hispanic or Latino Origin"
)

# Kentucky
kentucky_data <- filter(acs_data, Label == "Bachelor's degree or higher*********")
bdh_hloorigin_kentucky <- tibble(
  Years = kentucky_data$Years,
  Percentage_hloorigin_women = kentucky_data$`...197`,
  Race = "Hispanic or Latino Origin"
)

# Louisiana
louisiana_data <- filter(acs_data, Label == "Bachelor's degree or higher*********")
bdh_hloorigin_louisiana <- tibble(
  Years = louisiana_data$Years,
  Percentage_hloorigin_women = louisiana_data$`...209`,
  Race = "Hispanic or Latino Origin"
)

# Maine
maine_data <- filter(acs_data, Label == "Bachelor's degree or higher*********")
bdh_hloorigin_maine <- tibble(
  Years = maine_data$Years,
  Percentage_hloorigin_women = maine_data$`...221`,
  Race = "Hispanic or Latino Origin"
)

# Maryland
maryland_data <- filter(acs_data, Label == "Bachelor's degree or higher*********")
bdh_hloorigin_maryland <- tibble(
  Years = maryland_data$Years,
  Percentage_hloorigin_women = maryland_data$`...233`,
  Race = "Hispanic or Latino Origin"
)

# Massachusetts
massachusetts_data <- filter(acs_data, Label == "Bachelor's degree or higher*********")
bdh_hloorigin_massachusetts <- tibble(
  Years = massachusetts_data$Years,
  Percentage_hloorigin_women = massachusetts_data$`...245`,
  Race = "Hispanic or Latino Origin"
)

# Michigan
michigan_data <- filter(acs_data, Label == "Bachelor's degree or higher*********")
bdh_hloorigin_michigan <- tibble(
  Years = michigan_data$Years,
  Percentage_hloorigin_women = michigan_data$`...257`,
  Race = "Hispanic or Latino Origin"
)

# Minnesota
minnesota_data <- filter(acs_data, Label == "Bachelor's degree or higher*********")
bdh_hloorigin_minnesota <- tibble(
  Years = minnesota_data$Years,
  Percentage_hloorigin_women = minnesota_data$`...269`,
  Race = "Hispanic or Latino Origin"
)

# Mississippi
mississippi_data <- filter(acs_data, Label == "Bachelor's degree or higher*********")
bdh_hloorigin_mississippi <- tibble(
  Years = mississippi_data$Years,
  Percentage_hloorigin_women = mississippi_data$`...281`,
  Race = "Hispanic or Latino Origin"
)

# Missouri
missouri_data <- filter(acs_data, Label == "Bachelor's degree or higher*********")
bdh_hloorigin_missouri <- tibble(
  Years = missouri_data$Years,
  Percentage_hloorigin_women = missouri_data$`...293`,
  Race = "Hispanic or Latino Origin"
)

# Montana
montana_data <- filter(acs_data, Label == "Bachelor's degree or higher*********")
bdh_hloorigin_montana <- tibble(
  Years = montana_data$Years,
  Percentage_hloorigin_women = montana_data$`...305`,
  Race = "Hispanic or Latino Origin"
)

# Nebraska
nebraska_data <- filter(acs_data, Label == "Bachelor's degree or higher*********")
bdh_hloorigin_nebraska <- tibble(
  Years = nebraska_data$Years,
  Percentage_hloorigin_women = nebraska_data$`...317`,
  Race = "Hispanic or Latino Origin"
)

# Nevada
nevada_data <- filter(acs_data, Label == "Bachelor's degree or higher*********")
bdh_hloorigin_nevada <- tibble(
  Years = nevada_data$Years,
  Percentage_hloorigin_women = nevada_data$`...329`,
  Race = "Hispanic or Latino Origin"
)

# New Hampshire
newhampshire_data <- filter(acs_data, Label == "Bachelor's degree or higher*********")
bdh_hloorigin_newhampshire <- tibble(
  Years = newhampshire_data$Years,
  Percentage_hloorigin_women = newhampshire_data$`...341`,
  Race = "Hispanic or Latino Origin"
)

# New Jersey
newjersey_data <- filter(acs_data, Label == "Bachelor's degree or higher*********")
bdh_hloorigin_newjersey <- tibble(
  Years = newjersey_data$Years,
  Percentage_hloorigin_women = newjersey_data$`...353`,
  Race = "Hispanic or Latino Origin"
)

# New Mexico
newmexico_data <- filter(acs_data, Label == "Bachelor's degree or higher*********")
bdh_hloorigin_newmexico <- tibble(
  Years = newmexico_data$Years,
  Percentage_hloorigin_women = newmexico_data$`...365`,
  Race = "Hispanic or Latino Origin"
)

# New York
newyork_data <- filter(acs_data, Label == "Bachelor's degree or higher*********")
bdh_hloorigin_newyork <- tibble(
  Years = newyork_data$Years,
  Percentage_hloorigin_women = newyork_data$`...377`,
  Race = "Hispanic or Latino Origin"
)

# North Carolina
northcarolina_data <- filter(acs_data, Label == "Bachelor's degree or higher*********")
bdh_hloorigin_northcarolina <- tibble(
  Years = northcarolina_data$Years,
  Percentage_hloorigin_women = northcarolina_data$`...389`,
  Race = "Hispanic or Latino Origin"
)

# North Dakota
northdakota_data <- filter(acs_data, Label == "Bachelor's degree or higher*********")
bdh_hloorigin_northdakota <- tibble(
  Years = northdakota_data$Years,
  Percentage_hloorigin_women = northdakota_data$`...401`,
  Race = "Hispanic or Latino Origin"
)

# Ohio
ohio_data <- filter(acs_data, Label == "Bachelor's degree or higher*********")
bdh_hloorigin_ohio <- tibble(
  Years = ohio_data$Years,
  Percentage_hloorigin_women = ohio_data$`...413`,
  Race = "Hispanic or Latino Origin"
)

# Oklahoma
oklahoma_data <- filter(acs_data, Label == "Bachelor's degree or higher*********")
bdh_hloorigin_oklahoma <- tibble(
  Years = oklahoma_data$Years,
  Percentage_hloorigin_women = oklahoma_data$`...425`,
  Race = "Hispanic or Latino Origin"
)

# Oregon
oregon_data <- filter(acs_data, Label == "Bachelor's degree or higher*********")
bdh_hloorigin_oregon <- tibble(
  Years = oregon_data$Years,
  Percentage_hloorigin_women = oregon_data$`...437`,
  Race = "Hispanic or Latino Origin"
)

# Pennsylvania
pennsylvania_data <- filter(acs_data, Label == "Bachelor's degree or higher*********")
bdh_hloorigin_pennsylvania <- tibble(
  Years = pennsylvania_data$Years,
  Percentage_hloorigin_women = pennsylvania_data$`...449`,
  Race = "Hispanic or Latino Origin"
)

# Rhode Island
rhodeisland_data <- filter(acs_data, Label == "Bachelor's degree or higher*********")
bdh_hloorigin_rhodeisland <- tibble(
  Years = rhodeisland_data$Years,
  Percentage_hloorigin_women = rhodeisland_data$`...461`,
  Race = "Hispanic or Latino Origin"
)

# South Carolina
southcarolina_data <- filter(acs_data, Label == "Bachelor's degree or higher*********")
bdh_hloorigin_southcarolina <- tibble(
  Years = southcarolina_data$Years,
  Percentage_hloorigin_women = southcarolina_data$`...473`,
  Race = "Hispanic or Latino Origin"
)

# South Dakota
southdakota_data <- filter(acs_data, Label == "Bachelor's degree or higher*********")
bdh_hloorigin_southdakota <- tibble(
  Years = southdakota_data$Years,
  Percentage_hloorigin_women = southdakota_data$`...485`,
  Race = "Hispanic or Latino Origin"
)

# Tennessee
tennessee_data <- filter(acs_data, Label == "Bachelor's degree or higher*********")
bdh_hloorigin_tennessee <- tibble(
  Years = tennessee_data$Years,
  Percentage_hloorigin_women = tennessee_data$`...497`,
  Race = "Hispanic or Latino Origin"
)

# Texas
texas_data <- filter(acs_data, Label == "Bachelor's degree or higher*********")
bdh_hloorigin_texas <- tibble(
  Years = texas_data$Years,
  Percentage_hloorigin_women = texas_data$`...509`,
  Race = "Hispanic or Latino Origin"
)

# Utah
utah_data <- filter(acs_data, Label == "Bachelor's degree or higher*********")
bdh_hloorigin_utah <- tibble(
  Years = utah_data$Years,
  Percentage_hloorigin_women = utah_data$`...521`,
  Race = "Hispanic or Latino Origin"
)

# Vermont
vermont_data <- filter(acs_data, Label == "Bachelor's degree or higher*********")
bdh_hloorigin_vermont <- tibble(
  Years = vermont_data$Years,
  Percentage_hloorigin_women = vermont_data$`...533`,
  Race = "Hispanic or Latino Origin"
)

# Virginia
virginia_data <- filter(acs_data, Label == "Bachelor's degree or higher*********")
bdh_hloorigin_virginia <- tibble(
  Years = virginia_data$Years,
  Percentage_hloorigin_women = virginia_data$`...545`,
  Race = "Hispanic or Latino Origin"
)

# Washington
washington_data <- filter(acs_data, Label == "Bachelor's degree or higher*********")
bdh_hloorigin_washington <- tibble(
  Years = washington_data$Years,
  Percentage_hloorigin_women = washington_data$`...557`,
  Race = "Hispanic or Latino Origin"
)

# West Virginia
westvirginia_data <- filter(acs_data, Label == "Bachelor's degree or higher*********")
bdh_hloorigin_westvirginia <- tibble(
  Years = westvirginia_data$Years,
  Percentage_hloorigin_women = westvirginia_data$`...569`,
  Race = "Hispanic or Latino Origin"
)

# Wisconsin
wisconsin_data <- filter(acs_data, Label == "Bachelor's degree or higher*********")
bdh_hloorigin_wisconsin <- tibble(
  Years = wisconsin_data$Years,
  Percentage_hloorigin_women = wisconsin_data$`...581`,
  Race = "Hispanic or Latino Origin"
)

# Wyoming
wyoming_data <- filter(acs_data, Label == "Bachelor's degree or higher*********")
bdh_hloorigin_wyoming <- tibble(
  Years = wyoming_data$Years,
  Percentage_hloorigin_women = wyoming_data$`...593`,
  Race = "Hispanic or Latino Origin"
)


combined_data_hloorigin <- bind_rows(
  bdh_hloorigin_alabama,
  bdh_hloorigin_alaska,
  bdh_hloorigin_arizona,
  bdh_hloorigin_arkansas,
  bdh_hloorigin_california,
  bdh_hloorigin_colorado,
  bdh_hloorigin_connecticut,
  bdh_hloorigin_delaware,
  bdh_hloorigin_florida,
  bdh_hloorigin_georgia,
  bdh_hloorigin_hawaii,
  bdh_hloorigin_idaho,
  bdh_hloorigin_illinois,
  bdh_hloorigin_indiana,
  bdh_hloorigin_iowa,
  bdh_hloorigin_kansas,
  bdh_hloorigin_kentucky,
  bdh_hloorigin_louisiana,
  bdh_hloorigin_maine,
  bdh_hloorigin_maryland,
  bdh_hloorigin_massachusetts,
  bdh_hloorigin_michigan,
  bdh_hloorigin_minnesota,
  bdh_hloorigin_mississippi,
  bdh_hloorigin_missouri,
  bdh_hloorigin_montana,
  bdh_hloorigin_nebraska,
  bdh_hloorigin_nevada,
  bdh_hloorigin_newhampshire,
  bdh_hloorigin_newjersey,
  bdh_hloorigin_newmexico,
  bdh_hloorigin_newyork,
  bdh_hloorigin_northcarolina,
  bdh_hloorigin_northdakota,
  bdh_hloorigin_ohio,
  bdh_hloorigin_oklahoma,
  bdh_hloorigin_oregon,
  bdh_hloorigin_pennsylvania,
  bdh_hloorigin_rhodeisland,
  bdh_hloorigin_southcarolina,
  bdh_hloorigin_southdakota,
  bdh_hloorigin_tennessee,
  bdh_hloorigin_texas,
  bdh_hloorigin_utah,
  bdh_hloorigin_vermont,
  bdh_hloorigin_virginia,
  bdh_hloorigin_washington,
  bdh_hloorigin_westvirginia,
  bdh_hloorigin_wisconsin,
  bdh_hloorigin_wyoming,
  bdh_hloorigin_puertorico
)

print(combined_data_hloorigin)

```

*Initial Comments:*

-   Guys, note that there are some N/As for American Indian or Alaska Native Alone Data, Some other race Alone, Hispanic/Latino Origin, . Should not be a problem though since we can easily filter them out.
